---
title: "<br><br> `r params$scinamicNum`: Quality Control report includes `r params$cellline`"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  bookdown::html_document2:
    collapsed: true
    fig_width: 8
    highlight: haddock
    keep_md: false
    theme: cerulean
    toc: yes
    toc_float:
      collapsed: yes
params:
  #cellline: "Jurkat"
  scinamicNum: "A-2025-0150-A"
  baseDir: "/fsx/home/crivera/BULK-TRANSCRIPTOMICS/Cell_line_Experiments/PROTEOMICS/ChemoBetter/Results_251112_CHEMOPROTEOMICS/A-2025-0150-A"
  DirPipeline:  "/fsx/home/crivera/BULK-TRANSCRIPTOMICS/Transcriptomics_Pipeline/R/all_reports/main_qc_report"
  Alias_path: "/fsx/home/crivera/BULK-TRANSCRIPTOMICS/Transcriptomics_Pipeline/data/Data_for_pipeline/mol_ids_chemobetter.csv"
  Uniprot_map_db: "/fsx/home/crivera/Data_Bases/UNIPROT_GeneInfo/hgnc_uniprot_mapping.txt"
  Metadata_gr_path: "~/MULTI_OMICS/ChemoBetter_results/Chemoproteomics/2025/A-2025-0150-A/A-2025-0150-A_contrast_metadata.csv"
  Contrast_def_path: "~/MULTI_OMICS/ChemoBetter_results/Chemoproteomics/2025/A-2025-0150-A/A-2025-0150-A_contrast_definitions.csv"
  workstream: "Pisa"
  Extract_Metadata_path: "/fsx/home/crivera/MULTI_OMICS/ChemoBetter_results/Chemoproteomics/2025_Raw/elnid=A-2025-0150-A/Extract Proteomics-20251017052646.xlsx"
  Proteins_protdisc_path: "/fsx/home/crivera/MULTI_OMICS/ChemoBetter_results/Chemoproteomics/2025_Raw/elnid=A-2025-0150-A/20251003_A150_A_f_Proteins.txt"               
  Contrast_groups_path: "/fsx/home/crivera/MULTI_OMICS/ChemoBetter_results/Chemoproteomics/2025/A-2025-0150-A/A-2025-0150-A_contrast_groups.csv"     
  PSM_path: "/fsx/home/crivera/MULTI_OMICS/ChemoBetter_results/Chemoproteomics/2025_Raw/elnid=A-2025-0150-A/20251003_A150_A_f_PSMs.txt"
  
     
  
---




```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, error=TRUE, fig.align="left",  dev="png", fig.height=6, fig.width=9, message=F, warning=F)

# load packages
library(tidyverse)
library(DT)
library(biomaRt)
library(plotly)
#library(EnhancedVolcano)
library(knitr)
#library(kableExtra)
library(glue)
library(devtools)
library(msigdbr)
library(ggthemes)
#library(DESeq2)
library(patchwork)
library(pheatmap)
library(metafolio)
library("rio")
library("janitor")
library(patchwork)

# Save parameters to a JSON file
library(jsonlite)


# deal with namespace clashes
library(conflicted)
conflicts_prefer(
  dplyr::select,
  dplyr::select,
  dplyr::filter,
  dplyr::rename,
  dplyr::mutate,
  base::intersect
)

theme_set(theme_bw(base_size = 14))

library(jsonlite)
write_json(params, file.path(params$baseDir,"params_QC.json"))

# color blind friendly palette
cbPalette <- c("#999999", "#E69F00", "#56B4E9", "#009E73", "#F0E442", "#0072B2", "#D55E00", "#CC79A7")
```

```{r functions }
# load custom functions
source(file.path(params$DirPipeline, "../cleaned_functions.R"))

```



-------------------

# Description QC Report


### **2. Boxplot for QC ** {.unnumbered}

Boxplot from abundance matrix across all samples before normalization. These plots are utilized to assess whether the protein abundance distribution varies significantly between different biological conditions and to identify any anomalies in individual samples.

### **3. Coefficient of Variation of Biological groups ** {.unnumbered}

Histograms showing the distribution of the coefficient of variation percentage (CV %) for each biological group. The CV % is calculated as the standard deviation divided by the mean, multiplied by 100. A lower CV % indicates less variability within the group, while a higher CV % suggests greater variability.

### **4. Number of quantified proteins ** {.unnumbered}

The total number of proteins quantified with High FDR confidence (combined) is displayed here

### **5. Principal Components Analysis (Abundances) ** {.unnumbered}

PCA plot across all samples using the abundance matrix before normalization.

### **6. Principal Components Analysis (Normalized abundances) ** {.unnumbered}

PCA plot across all samples using the normalized abundance matrix. This plot gives an overview of how well samples of the same biological condition are clustering.

### **7. Number of Peptide Spectrum Matches ** {.unnumbered}

The total number of PSMs identified

### **8. Average Reporter S/N ** {.unnumbered}

Histogram showing the average Signal to Noise ratio across all PSMs identified. A higher S/N ratio indicates that the signal (i.e., the reporter ion's intensity) is significantly above the noise level, suggesting more reliable quantification.

### **8. Number of missed cleavages ** {.unnumbered}

Histogram showing the distribution of the number of missed cleavages across all PSMs identified. Missed cleavages occur when the protease used for digestion does not cleave at all expected sites, leading to longer peptides. A lower number of missed cleavages generally indicates more efficient digestion and better sample preparation.




```{r ReportContrast,eval = TRUE}

library(tidyverse)
uniprot_map <- readr::read_tsv(params$Uniprot_map_db)
colnames(uniprot_map) <- c("gene", "Uniprot.ID")

# Download mapping between molid and alias name
Alias_map <- read.csv(params$Alias_path)

# Download metadata of the groups
Metadata_gr_def = read.csv(file.path(params$Metadata_gr_path))
Contrasts_def = read.csv(file.path(params$Contrast_def_path))
#Data_df = read.csv(file.path(params$Data_df_path))

Metadata_gr_def_new <- Metadata_gr_def  %>% pivot_wider(names_from = Factor, values_from = Value)
colnames(Metadata_gr_def_new) <- gsub(" ", "_", colnames(Metadata_gr_def_new))

if(params$workstream == "Pisa"){
# Comment once metadata is fixed
Metadata_gr_def_new$Compound_Treatment_Time = 0.5
Metadata_gr_def_new$Cotreatment_Batch = "NONE"
Metadata_gr_def_new =Metadata_gr_def_new %>% dplyr::rename(Cellline = Celllines)
Metadata_gr_def_new =Metadata_gr_def_new %>% dplyr::rename(Compound_Concentration = Compound_Concentration_uM)
}else if (params$workstream == "Proteomics"){

 Metadata_gr_def_new =Metadata_gr_def_new %>% dplyr::rename(Compound_Treatment_Time = `Compound_Treatment_Time_(h)`)
 
}else if(params$workstream == "PAL"){
 
    Metadata_gr_def_new$Compound_Treatment_Time = 1
    Metadata_gr_def_new$Cotreatment_Batch = "COT-00000027-001"
    Metadata_gr_def_new =Metadata_gr_def_new %>% dplyr::rename(Cellline = Celllines)
    Metadata_gr_def_new =Metadata_gr_def_new %>% dplyr::rename(Compound_Concentration = Compound_Concentration_uM)
    
    
}
Metadata_gr_def_new$alias_name <- ifelse(is.na(match(Metadata_gr_def_new$Compound_Batch, Alias_map$MolID)),
  # If Compound_Batch is not found, use itself as the alias name
  Metadata_gr_def_new$Compound_Batch,
  # If found, use the Treatment from the Alias_map
  Alias_map$Treatment[match(Metadata_gr_def_new$Compound_Batch, Alias_map$MolID)]
)
Metadata_gr_def_new$alias_cotreat <- ifelse(is.na(match(Metadata_gr_def_new$Cotreatment_Batch, Alias_map$MolID)),
  # If Compound_Batch is not found, use itself as the alias name
  Metadata_gr_def_new$Cotreatment_Batch,
  # If found, use the Treatment from the Alias_map
  Alias_map$Treatment[match(Metadata_gr_def_new$Cotreatment_Batch, Alias_map$MolID)]
)


Metadata_gr_def_new$coarse_cond = paste(Metadata_gr_def_new$Cellline, Metadata_gr_def_new$alias_name, Metadata_gr_def_new$Compound_Concentration, Metadata_gr_def_new$Compound_Treatment_Time, Metadata_gr_def_new$alias_cotreat, sep = "_")

Drugs = Metadata_gr_def_new$alias_name[!Metadata_gr_def_new$alias_name %in% "DMSO"]
Groups_drugs = Metadata_gr_def_new %>% dplyr::filter(alias_name %in% Drugs) %>% pull(Group_ID)

Contrasts_def_new <- Contrasts_def %>% pivot_wider(
    names_from = Numerator_or_Denomenator,
    values_from = Group_ID
  ) 
Contrasts_def_new$treat = Metadata_gr_def_new$coarse_cond[match(Contrasts_def_new$Numerator, Metadata_gr_def_new$Group_ID)]
Contrasts_def_new$untreat = Metadata_gr_def_new$coarse_cond[match(Contrasts_def_new$Denomenator, Metadata_gr_def_new$Group_ID)]
Contrasts_def_new$cell_line = Metadata_gr_def_new$Cellline[match(Contrasts_def_new$Numerator, Metadata_gr_def_new$Group_ID)]
Contrasts_def_new$drug = Metadata_gr_def_new$alias_name[match(Contrasts_def_new$Numerator, Metadata_gr_def_new$Group_ID)]
Contrasts_def_new$stimulation = Metadata_gr_def_new$alias_cotreat[match(Contrasts_def_new$Numerator, Metadata_gr_def_new$Group_ID)]

# Lets create a list for comparisons against DMSO first
Contrasts_DMSO_list = c()
for(gr in Groups_drugs){
    
    Stim = unique(Metadata_gr_def_new %>% dplyr::filter(Group_ID == gr) %>% pull("Cotreatment_Batch"))
    DMSO_group = Metadata_gr_def_new %>% dplyr::filter(alias_name == "DMSO" , Cotreatment_Batch ==  Stim  ) %>% pull(Group_ID)  
    Contrasts_def_case = Contrasts_def %>% dplyr::filter(Group_ID %in% gr, Numerator_or_Denomenator == "Numerator")
    Contrasts_def_control = Contrasts_def %>% dplyr::filter(Group_ID %in% DMSO_group, Numerator_or_Denomenator == "Denomenator")
    Cont_sel = base::intersect(Contrasts_def_case$Contrast_ID, Contrasts_def_control$Contrast_ID)
    Contrasts_DMSO_list = c(Contrasts_DMSO_list,Cont_sel)
}

# Add the stim vs NoStim 
dmso_stims_list = c()
for(st in unique(Metadata_gr_def_new$Cotreatment_Batch)){
    
    NoStim_group = Metadata_gr_def_new %>% dplyr::filter(alias_name == "DMSO" , Cotreatment_Batch ==  "NONE"  ) %>% pull(Group_ID)  
    Stim_group = Metadata_gr_def_new %>% dplyr::filter(alias_name == "DMSO" , Cotreatment_Batch ==  st  ) %>% pull(Group_ID)  
    Contrasts_def_case = Contrasts_def %>% dplyr::filter(Group_ID %in% Stim_group, Numerator_or_Denomenator == "Numerator")
    Contrasts_def_control = Contrasts_def %>% dplyr::filter(Group_ID %in% NoStim_group, Numerator_or_Denomenator == "Denomenator")
    Cont_sel = base::intersect(Contrasts_def_case$Contrast_ID, Contrasts_def_control$Contrast_ID)
    dmso_stims_list = c(dmso_stims_list,Cont_sel)
}

first_report = c(Contrasts_DMSO_list, dmso_stims_list)
combined <- c(first_report, base::setdiff(unique(Contrasts_def_new$Contrast_ID), first_report))

# Function to split into chunks of 10
split_into_chunks <- function(vec, chunk_size) {
  split(vec, ceiling(seq_along(vec) / chunk_size))
}

chunks <- split_into_chunks(combined, 8)

report_num_df <- data.frame(
  Element = unlist(chunks),
  ReporNum = rep(seq_along(chunks), sapply(chunks, length))
)

Contrasts_def_new$reportNum = report_num_df$ReporNum[match(Contrasts_def_new$Contrast_ID, report_num_df$Element)]
Contrasts_def_new = Contrasts_def_new[match(report_num_df$Element, Contrasts_def_new$Contrast_ID), ]
 

# Save Contrast file with report numbers in a folder names Contrast
#Output_file_path = params$baseDir



# Save metadata and count formatted data frames
dir.create(file.path( params$baseDir, "CONTRAST_FILE_GEN"))
#save contrast file as .csv
write.csv(Contrasts_def_new, file.path(params$baseDir, "CONTRAST_FILE_GEN", paste(params$scinamicNum, "constrasts.csv", sep = "_")), row.names = FALSE)
#setwd("..")


```


```{r, echo=FALSE, results='asis', fig.show='hide'}
library(openxlsx)

dir.create(file.path( params$baseDir, "QC_Plots"))
# Build metadata and unnormalized unscaled abundances and normalized abundances matrices
# Read contrast group assignments
Contrast_groups_map = read.csv(params$Contrast_groups_path)
Contrast_groups_map$coarse_cond = Metadata_gr_def_new$coarse_cond[match(Contrast_groups_map$Group_ID, Metadata_gr_def_new$Group_ID)]

Metadata_features = c("ID", "Isobaric.Tag.Channel", "Isobaric.Tag")
# Read Extract metadata and group class and alias group
Metadata_Extract <- read.xlsx(params$Extract_Metadata_path, sheet = 1) %>% dplyr::select(all_of(Metadata_features))
 
# Add groups and alias_group to Metadata Extract
Metadata_Extract <- left_join(Metadata_Extract, Contrast_groups_map, by = c("ID" = "Proteomics_Extract_ID"))
 
 # Define Samples Names
 Metadata_Extract$Sample_name = paste(Metadata_Extract$coarse_cond, Metadata_Extract$ID, sep = "_")
 Metadata_Extract$Biological_condition = Metadata_Extract$coarse_cond
 
 # Read Proteome discover outcome containing everything
 Proteins_prot_dic <- read.table(params$Proteins_protdisc_path, header = TRUE, sep = "\t")
 # Grab columns for un-nomalized, unscaled abundances
 Col_abundances = colnames(Proteins_prot_dic)[grep("Abundance..F", colnames(Proteins_prot_dic))]
 Col_Nom_abundances = colnames(Proteins_prot_dic)[grep("Abundances..Normalized", colnames(Proteins_prot_dic))]
 #Col_scl_abundances = colnames(Proteins_prot_dic)[grep("Abundances..Scaled", colnames(Proteins_prot_dic))]
 
 # ABUNDANCE MATRIX
 Data_df_abundances = Proteins_prot_dic %>% dplyr::select(Accession, all_of(Col_abundances))
 Data_df_abundances = Data_df_abundances %>% column_to_rownames("Accession")
 colnames(Data_df_abundances) = unlist(sapply(colnames(Data_df_abundances),function(x){sub(".*F1\\.\\.(.*?)\\.\\.Sample.*", "\\1", x)}))
 Colnames_abund = Metadata_Extract$Sample_name[match(colnames(Data_df_abundances),Metadata_Extract$Isobaric.Tag.Channel)]
 colnames(Data_df_abundances) = Colnames_abund
 #Data_df_abundances[is.na(Data_df_abundances)] <- 0
 
 # NORMALIZED ABUNDANCE MATRIX
 
 Data_df_abundances_norm = Proteins_prot_dic %>% dplyr::select(Accession, all_of(Col_Nom_abundances))
 Data_df_abundances_norm = Data_df_abundances_norm %>% column_to_rownames("Accession")
 colnames(Data_df_abundances_norm) = unlist(sapply(colnames(Data_df_abundances_norm),function(x){sub(".*F1\\.\\.(.*?)\\.\\.Sample.*", "\\1", x)}))
 Colnames_abund_norm = Metadata_Extract$Sample_name[match(colnames(Data_df_abundances_norm),Metadata_Extract$Isobaric.Tag.Channel)]
 colnames(Data_df_abundances_norm) = Colnames_abund_norm
 #Data_df_abundances_norm[is.na(Data_df_abundances_norm)] <- 0
 
 # Save Metadata and abndace matrices
 
 Df_list = list("Abundances" = Data_df_abundances %>% rownames_to_column("Uniprot"),
                "Norm_Abundances" = Data_df_abundances_norm %>% rownames_to_column("Uniprot"),
                "Metadata" = Metadata_Extract)
 wb <- createWorkbook()
 for (sheet_name in names(Df_list)) {
  # Add a new sheet
  addWorksheet(wb, sheet_name)
  
  # Write the data frame to the sheet
  writeData(wb, sheet = sheet_name, Df_list[[sheet_name]])
}

# Save the workbook to a file
saveWorkbook(wb, file.path(params$baseDir, "QC_Plots","Dfs_abund_metadata.xlsx"), overwrite = TRUE)
 
         
```

# Boxplots for QC (Abundances) - All samples - All samples

In these boxplot the middle represents the median and the box the interquartile range (IQR), which spans from 25th percentile (first quartile, Q1) to the 75th percentile (third quartile, Q3). The whiskers extend to 1.5 times the IQR. Points outside this range are considered outliers.

```{r, echo=FALSE, results='asis'}


Data_df_abundances_long = Data_df_abundances %>% rownames_to_column("Uniprot") %>% pivot_longer(!Uniprot, names_to = "Sample_name", values_to = "abundance")
Data_df_abundances_long = left_join(Data_df_abundances_long, Metadata_Extract, by="Sample_name")
Data_df_abundances_long$Biological_condition = as.factor(Data_df_abundances_long$Biological_condition)
pl = ggplot(Data_df_abundances_long, aes(x=Sample_name, y = log10(abundance), fill=Biological_condition)) +
  geom_boxplot(outlier.size = 0.5) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1, size=6)) +
  xlab("Samples") +
  ylab("Log10(Abundance)") +
  ggtitle("Protein abundance across samples")




ggplotly(pl)

ggsave(
  filename = file.path( params$baseDir, "QC_Plots", "Boxplot_Abundances.png"),
  plot = pl,
  width = 10,         # in inches
  height = 7,        # in inches
  dpi = 300          # good quality
)

```         

# Coefficient of Variation of Biological groups (Normalized abundances) {.tabset}



```{r, echo=FALSE, results='asis', eval. = FALSE}

Coarse_conds = unique(Data_df_abundances_long$Biological_condition)
# We use the normalized abundance matrix for this. 
Data_df_abundances_norm_long = Data_df_abundances_norm %>% rownames_to_column("Uniprot") %>% pivot_longer(!Uniprot, names_to = "Sample_name", values_to = "abundance")
Data_df_abundances_norm_long = left_join(Data_df_abundances_norm_long, Metadata_Extract, by="Sample_name")


Data_for_CV = Data_df_abundances_norm_long
result <- lapply(Coarse_conds, function(coarse) {
   knitr::knit_child(file.path(params$DirPipeline, "child_reports","Child_CV_hist.Rmd"),
                    envir = environment(),
                    quiet = TRUE,
                    options = list(
                      cache = FALSE
                    )
   )
  })

cat(unlist(result), sep="\n")

```         


# Number of quantified proteins


```{r, echo=FALSE, results='asis'}
library(openxlsx)


cat(paste("Number of quantified proteins (Proteins with High value on the <i>Protein FDR Confidence: Combined </i> ) is ", nrow(Proteins_prot_dic), sep=""))
         
```


# Principal Components Analysis (Abundances) - All samples{.tabset}

We use PCA plots like these to give us an overall view of the samples.

```{r, echo=FALSE, results='asis', fig.show='hide'}
library(openxlsx)
dir.create(file.path( params$baseDir, "PCAs"))

has_valid_variance <- apply(Data_df_abundances, 1, function(x) {
  # Calculate variance but handle NA cases
  v <- var(x, na.rm = TRUE)
  !is.na(v) && v > 0
})

 Data_df_abundances_pca = Data_df_abundances[has_valid_variance , ]
 
 pca <- prcomp(t(as.matrix(Data_df_abundances_pca)), scale. = TRUE, center = TRUE)
 pca_res <- left_join(Metadata_Extract,
                     as.data.frame(pca$x) %>% rownames_to_column("Sample_name"),
                     by="Sample_name")
 pca_var <-pca$sdev^2/sum(pca$sdev^2)
 

covariates = c("Biological_condition", Metadata_features)

result <- lapply(covariates, function(covar) {
   knitr::knit_child(file.path(params$DirPipeline, "child_reports","Child_PCA.Rmd"),
                    envir = environment(),
                    quiet = TRUE,
                    options = list(
                      cache = FALSE
                    )
   )
  })


cat(unlist(result), sep="\n")
# Save just the PCA colored by the biological sample condition
pl = pcaplot(df = pca_res,pca_var, covar = "Biological_condition", pc1 = "PC1", pc2 = "PC2")

ggsave(
  filename = file.path( params$baseDir, "PCAs", "PCA_unnormalized.png"),
  plot = pl,
  width = 10,         # in inches
  height = 7,        # in inches
  dpi = 300          # good quality
)


         
```


# Principal Components Analysis (Normalized abundances) - All samples{.tabset}

We use PCA plots like these to give us an overall view of the samples.

```{r, echo=FALSE, results='asis', fig.show='hide'}
library(openxlsx)

dir.create(file.path( params$baseDir, "PCAs"))

 has_valid_variance <- apply(Data_df_abundances_norm, 1, function(x) {
  # Calculate variance but handle NA cases
  v <- var(x, na.rm = TRUE)
  !is.na(v) && v > 0
})
 
 Data_df_abundances_norm_pca = Data_df_abundances_norm[has_valid_variance, ]
 
 pca_norm <- prcomp(t(as.matrix(Data_df_abundances_norm_pca)), scale. = TRUE, center = TRUE)
 pca_res <- left_join(Metadata_Extract,
                     as.data.frame(pca_norm$x) %>% rownames_to_column("Sample_name"),
                     by="Sample_name")
 pca_var <-pca_norm$sdev^2/sum(pca_norm$sdev^2)
 

covariates = c("Biological_condition", Metadata_features)

result <- lapply(covariates, function(covar) {
   knitr::knit_child(file.path(params$DirPipeline, "child_reports","Child_PCA.Rmd"),
                    envir = environment(),
                    quiet = TRUE,
                    options = list(
                      cache = FALSE
                    )
   )
  })
cat(unlist(result), sep="\n")
# Save just the PCA colored by the biological sample condition

pl2 = pcaplot(df = pca_res,pca_var, covar = "Biological_condition", pc1 = "PC1", pc2 = "PC2")

ggsave(
  filename = file.path( params$baseDir, "PCAs", "PCA_normalized.png"),
  plot = pl2,
  width = 10,         # in inches
  height = 7,        # in inches
  dpi = 300          # good quality
)

         
```


# Number of PSMs


```{r, echo=FALSE, results='asis'}
library(openxlsx)


 PSMs_df = read.table(params$PSM_path, header = TRUE, sep = "\t")

 cat(paste("Number of PSMs is ", nrow(PSMs_df), sep=""))
         
```


# Average Reporter Signal to Noise ratio

Histogram showing the average Signal to Noise ratio across all PSMs identified. A higher S/N ratio indicates that the signal (i.e., the reporter ion's intensity) is significantly above the noise level, suggesting more reliable quantification.


```{r, echo=FALSE, results='asis'}


percentiles <- quantile(PSMs_df$Average.Reporter.S.N, probs = c(0.50, 0.8), na.rm = TRUE)
annotations <- data.frame(
  x = percentiles,
  labels = c("Median", "80th Percentile")
)

Max = PSMs_df$Average.Reporter.S.N[which.max(PSMs_df$Average.Reporter.S.N)]
ggplot(PSMs_df, aes(x = Average.Reporter.S.N)) +
  geom_histogram(bins = 40,  # You can change the binwidth to refine the histogram
                 fill = "cyan3", color = "black", 
                 boundary = 0, closed = "left") +
  geom_vline(data = annotations, aes(xintercept = x, color = labels), 
             linetype = "dashed", size = 1, show.legend = TRUE) +
  scale_color_manual(name = "Percentiles", values = c("Median" = "red", "80th Percentile" = "blue")) +     
  scale_x_continuous(name = "Average Reporter S/N", limits = c(0, Max)) +
  scale_y_continuous(name = "Frequency") 

ggplot(PSMs_df, aes(x = Average.Reporter.S.N)) +
  geom_histogram(bins = 40,  # You can change the binwidth to refine the histogram
                 fill = "cyan3", color = "black", 
                 boundary = 0, closed = "left") +
  geom_vline(data = annotations, aes(xintercept = x, color = labels), 
             linetype = "dashed", size = 1, show.legend = TRUE) +
  scale_color_manual(name = "Percentiles", values = c("Median" = "red", "80th Percentile" = "blue")) +     
  scale_x_continuous(name = "Average Reporter S/N", limits = c(0, percentiles[2])) +
  scale_y_continuous(name = "Frequency") 
  

  


         
```

# Number of missed cleavages
Histogram showing the distribution of the number of missed cleavages across all PSMs identified. Missed cleavages occur when the protease used for digestion does not cleave at all expected sites, leading to longer peptides. A lower number of missed cleavages generally indicates more efficient digestion and better sample preparation.

```{r, echo=FALSE, results='asis'}
PSMs_df$Number_missed_cleavages_perc = PSMs_df[["X..Missed.Cleavages"]] 

ggplot(PSMs_df, aes(x = Number_missed_cleavages_perc)) +
  geom_histogram(aes(y = after_stat((count / sum(count)) * 100)), binwidth = 1,fill = "cyan3", color = "black") +
  xlab("Number of missed cleavages") +
  ylab("Percent count") +
  scale_y_continuous(breaks = seq(0, 100, by = 10)) +
  ggtitle("") +
  theme_minimal()+
  theme(axis.text.x = element_text(size = 14),
        axis.title.x = element_text(size = 16),
        axis.text.y = element_text(size = 14),
        axis.title.y = element_text(size = 16))    
         
```




# R session info
This section includes technical details about the R code used to produce this analysis. Most readers can safely ignore it. 

<button class="btn btn-rcode" data-toggle="collapse" data-target="#BlockName"> Show/Hide R Session Details </button>  
<div id="BlockName" class="collapse">  

```{r session info}
sess <- devtools::session_info()
sess$platform
knitr::kable(as.data.frame(sess$packages), caption="Package versions")
```





