---
title: "<br><br> `r params$scinamicNum`: Differential gene expression and enrichment analysis of bulk-RNAseq data for `r params$drug` treated samples in `r params$cell_line` with `r params$stimulation` stimulation"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  bookdown::html_document2:
    collapsed: true
    fig_width: 8
    highlight: haddock
    keep_md: false
    theme: cerulean
    toc: yes
    toc_float:
      collapsed: yes
params:
  drug: "M2065_M2580_M277_SB525334"
  cell_line: "WI-38"
  stimulation: "NONE"
  scinamicNum: "AW85"
  baseDir: "/fsx/home/crivera/BULK-TRANSCRIPTOMICS/Cell_line_Experiments/PROTEOMICS/AW85/Results_250522/"
  ReportNum: "1"
  Experimental_design_path: "/fsx/home/crivera/BULK-TRANSCRIPTOMICS/Cell_line_Experiments/PROTEOMICS/AW85/Data/Experimental_design.png"
  
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, error=TRUE, fig.align="left",  dev="png", fig.height=6, fig.width=9, message=F, warning=F)
knitr::opts_knit$set(progress = FALSE)

library(tidyverse)
library(DT)
library(biomaRt)
library(plotly)
library(EnhancedVolcano)
library(knitr)
#library(kableExtra)
library(glue)
library(devtools)
library(msigdbr)
library(ggthemes)
library(clusterProfiler)
library(enrichplot) # needed for term similarity calcs
library(DESeq2)
library(conflicted)
library(patchwork)
library(pheatmap)
library(metafolio)
#library(ggvenn)
#library(UpSetR)
library(ashr)
library(BiocParallel)
library(UpSetR)
library(eulerr)

# source("~/repos/DiamondAge/report_templates/R_markdown_templates/_common_R_code/utilities.R")
# source("~/repos/DiamondAge/report_templates/R_markdown_templates/_common_R_code/rnaseq_de.R") # Most of the functions are in this file

# Save parameters to a JSON file
library(jsonlite)
write_json(params, file.path(params$baseDir,"params_DEG.json"))

# directories

baseDir = params$baseDir
saveDir = file.path(params$baseDir, "REPORTS", "DEG_ENRICHMENT", paste(params$drug,"Report",  params$ReportNum, sep = '_'))
#dataDir = file.path(baseDir,  "QCoutput", "221028_EXP005_BCH002")


if(!dir.exists(saveDir)){
  dir.create(saveDir, recursive = TRUE)
}
save = TRUE

conflicts_prefer(
  dplyr::select,
  dplyr::select,
  dplyr::filter,
  dplyr::rename,
  dplyr::mutate,
  base::intersect
)

theme_set(theme_bw(base_size = 14))
cbPalette <- c("#999999", "#E69F00", "#56B4E9", "#009E73", "#F0E442", "#0072B2", "#D55E00", "#CC79A7")
```



## Experimental design


```{r Exp,echo=FALSE, warning = FALSE,message=FALSE, fig.cap="Experimental design", fig.height=20, fig.width=24}

cat(params$ExpDescription)


if(file.exists(params$Experimental_design_path)){
  
    #knitr::opts_chunk$set(fig_width=20, fig_height=15)
    knitr::include_graphics(params$Experimental_design_path)
}else{
    cat("No experimental design scheme available")
}
```



-------------------

# Description Of DE Results

The names of the differential expression results are structured as **treatment** vs **control**. The following results are generated:

## Volcano Plot

The volcano plots show us a summary view of the differential expression results. Each point on the plot represents one gene in the experiment. Spots are colored according to the following criteria:

- **Blue**: padj < `r params$padj_thr_gene` & abs(LogFC) < `r params$logFC_thrs_gene`
- **Red**: padj < `r params$padj_thr_gene` & abs(LogFC) > `r params$logFC_thrs_gene`
- **Green**: padj > `r params$padj_thr_gene` & abs(LogFC) > `r params$logFC_thrs_gene`

The y-axis position represents the -log p-value: a higher value indicates that the gene is more significant. 

The x-axis position shows the log2 fold change for the gene between treatment or group 1 and control or group 2. Genes on the right-hand side of the plot increase in expression with treatment. Genes on the left-hand side decrease in expression with treatment.

## Top Up/Downregulated Genes

Heatmaps showing the scaled expression values of the top 50 up or downregulated genes in all samples. Genes in these heatmaps have a padj < `r params$padj_thr_gene` and  abs(LogFC) > `r params$logFC_thrs_gene`

## List Of Genes

This table contains the DE results for all genes with padj < `r params$padj_thr_gene` and  abs(LogFC) > `r params$logFC_thrs_gene`. Click the "Download" button to view a version of the data in Excel. The columns are as follows:

- **symbol**: Gene symbol
- **ensembl_gene_id**: ENSEMBL gene ID
- **description**: Gene name
- **log2FC**: Log2 fold change
- **pvalue**: Wald test p-value
- **padj**: Benjamini-Hochberg corrected p-value

## Gene Set Enrichment Analysis GSEA

Since so many genes are differentially expressed, it is difficult to review the entire experiment for biological themes in the expression changes. Gene Set Enrichment Analysis is one of several pathway analysis methods that can give us a bird’s eye view of the data. We’ll test the gene expression data for significant movement of collections of genes in known biological pathways. GSEA was performed on the following measure: sign(Log2FC) * -log10(pvalue)

We will use the following gene sets in this analysis:  

+ [Hallmark gene sets from MSigDb](https://www.gsea-msigdb.org/gsea/msigdb/collections.jsp#H). These gene sets "summarize and represent specific well-defined biological states or processes and display coherent expression. These gene sets were generated by a computational methodology based on identifying overlaps between gene sets in other MSigDB collections and retaining genes that display coordinate expression."
+ [Kyoto Encylopedia of Genes and Genomes (KEGG)](https://www.gsea-msigdb.org/gsea/msigdb/collections.jsp#C2). These gene sets are used to understand "high-level functions and utilities of the biological system, such as the cell, the organism and the ecosystem, from molecular-level information, especially large-scale molecular datasets generated by genome sequencing and other high-throughput experimental technologies."
+ [Reactome](https://www.gsea-msigdb.org/gsea/msigdb/collections.jsp#C2). 
+ [Enrichr](https://maayanlab.cloud/Enrichr/).  A large number of from a multitude of experimental sources. See [here](https://maayanlab.cloud/Enrichr/#libraries) for details on libraries of genesets.

For more information on the interpretation of these results, please see the "Interpreting results" section here: http://software.broadinstitute.org/gsea/doc/GSEAUserGuideFrame.html

### Signficance and GeneRatios

These dotplot capture both the significance and the GeneRatio (i.e. (count of core enrichment genes)/(count of pathway genes)) 

### Visualization pathways

These plots show the normalized enrichment score (x axis) for the enriched pathways. The size of the dot corresponds is proportional to the size of the pathway.

### Genes within pathways

These plots show shared genes among the most significant pathways. 

### Tree:pathway cluster

There is redundancy in the gene sets with many sharing genes/themes. These treeplots capture how the different terms relate to each other. Pathways sharing many genes will be closer in the treeplot. 

### Top Up/Downregulated Pathways

Enrichment plots showing the expression of the genes from the most enriched gene sets. The y-axis indicates the expression of the pathway genes. The x-axis is the rank order of the genes from the differential expression analysis. When there is significant gene set enrichment we should see a large number of genes at the beginning or end of the ranked gene list. 

For upregulated pathways you will see many pathway genes are on the left side of the plot and downregulated pathways will have pathway genes on the right of the plot. 


### List Of All Gene Sets

This table includes all gene sets in the pathway database. The columns are as follows:

* **ID:** Name of the gene set
* **link:** A link to information about the gene sets from mSigDB  (This contains information about how the gene sets were created.)
* **pvalue:** Uncorrected p-value
* **padj:** The Benjamini-Hochberg adjusted p-value (Generally we use a p-value cutoff of p<0.05 for this type of analysis.)
* **ES:** Uncorrected enrichment score
* **NES:** The normalized enrichment score (This is the score used to determine whether a gene set is moving up or down the gene rankings under the tested conditions. A positive score means that the genes are relatively overexpressed under treatment relative to the baseline condition. A negative score means that they are relatively underexpressed.)
* **size:** Size of the pathway after removing genes not observed in the dataset
* **core_enrichment:** Subset of genes that contribute most to the ES
* **Target_Chemo_esp:** Hits from chemoproteomics within the specific cell line associated to the molecule
* **Target_Chemo_all:** Hits from ALL experiments in chemoproteomics associated to the molecule

# Differential gene expression and pathway enrichment



```{r ChildComp, eval=TRUE, echo=FALSE, message=FALSE, warning=FALSE, results="asis"}

Childpath = "/fsx/home/crivera/BULK-TRANSCRIPTOMICS/Transcriptomics_Pipeline/R/all_reports/deg_enrich_report"
#names(all_contrasts)

Df = data.frame(Gene = c("G1", "G2"), pvalue = c("0.2", "0.05"))

all_contrasts = list("WI-38_M2065_10_24_NONE_A_Vs_WI-38_DMSO_0_24_NONE_A"  = Df )

res <- lapply(names(all_contrasts), function(name) {
   knitr::knit_child(file.path(Childpath, "child_reports","Child_Test.Rmd"),
                    envir = environment(),
                    quiet = TRUE,
                    options = list(
                      cache = FALSE,
                      fig.height = 10,
                      fig.width = 10
                    )
   )
  })

cat(unlist(res), sep="\n")

```
