---
title: "<br><br> `r params$scinamicNum`: Differential gene expression and enrichment analysis of proteomics data for `r params$drug` treated samples in `r params$cell_line` with `r params$stimulation` stimulation"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  bookdown::html_document2:
    collapsed: true
    fig_width: 8
    highlight: haddock
    keep_md: false
    theme: cerulean
    toc: yes
    toc_float:
      collapsed: yes
params:
  drug: "Sunitinib_Dimethyl fumarate"
  cell_line: "THP1.1"
  stimulation: "oxLDL_R848_NONE"
  scinamicNum: "A-2025-0147-B"
  baseDir: "/fsx/home/crivera/BULK-TRANSCRIPTOMICS/Cell_line_Experiments/PROTEOMICS/ChemoBetter/A-2025-0147-B/"
  DirDataForPipeline: "/fsx/home/crivera/BULK-TRANSCRIPTOMICS/Transcriptomics_Pipeline/data/Data_for_pipeline"
  #Customgenesets_path: "/fsx/home/crivera/BULK-TRANSCRIPTOMICS/Transcriptomics_Pipeline/data/Data_for_pipeline/250303_Disease_genesets.xlsx"
  DirPipeline: "/fsx/home/crivera/BULK-TRANSCRIPTOMICS/Transcriptomics_Pipeline/R/all_reports/deg_enrich_report"
  #dataDEG: "/fsx/home/crivera/BULK-TRANSCRIPTOMICS/Cell_line_Experiments/PROTEOMICS/AW85/DEG/Results200522/all_contrasts.RDS"
  Contrast_path: "/fsx/home/crivera/BULK-TRANSCRIPTOMICS/Cell_line_Experiments/PROTEOMICS/ChemoBetter/A-2025-0147-B/CONTRAST_FILE_GEN/A-2025-0147-B_constrasts.csv"
  Chemo_path: "/fsx/home/crivera/BULK-TRANSCRIPTOMICS/Transcriptomics_Pipeline/data/Data_for_pipeline/Target_list_241210_w_InvitroTargets_knInh.RDS"
  Experimental_design_path: ""
  Cell_Dict_path: "/fsx/home/crivera/BULK-TRANSCRIPTOMICS/Cell_line_Experiments/PROTEOMICS/ChemoBetter/Data/CellLine_Dict_Chemo.csv"
  Organism: "Human"
  padj_thr_gene: 0.05
  logFC_thrs_gene: 0
  ReportNum: "2"
  Uniprot_map_db: "/fsx/home/crivera/Data_Bases/UNIPROT_GeneInfo/hgnc_uniprot_mapping.txt"
  Metadata_gr_path: "~/MULTI_OMICS/ChemoBetter_results/Proteomics/2025/A-2025-0147-B/A-2025-0147-B_contrast_metadata.csv"
  Contrasts_stats: "~/MULTI_OMICS/ChemoBetter_results/Proteomics/2025/A-2025-0147-B/A-2025-0147-B_protein_abundance_contrast_stats.csv"
  workstream: "Proteomics"
  
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, error=TRUE, fig.align="left",  dev="png", fig.height=6, fig.width=9, message=F, warning=F)
knitr::opts_knit$set(progress = FALSE)

library(tidyverse)
library(DT)
library(biomaRt)
library(plotly)
library(EnhancedVolcano)
library(knitr)
#library(kableExtra)
library(glue)
library(devtools)
library(msigdbr)
library(ggthemes)
library(clusterProfiler)
library(enrichplot) # needed for term similarity calcs
library(DESeq2)
library(conflicted)
library(patchwork)
library(pheatmap)

library(metafolio)
#library(ggvenn)
#library(UpSetR)
library(ashr)
library(BiocParallel)
library(UpSetR)
library(eulerr)

# source("~/repos/DiamondAge/report_templates/R_markdown_templates/_common_R_code/utilities.R")
# source("~/repos/DiamondAge/report_templates/R_markdown_templates/_common_R_code/rnaseq_de.R") # Most of the functions are in this file

# Save parameters to a JSON file
library(jsonlite)
write_json(params, file.path(params$baseDir,"params_DEG.json"))



#setwd(Output_file_path)

# Save metadata and count formatted data frames
#dir.create("CONTRAST_FILE_GEN")


# directories
baseDir = params$baseDir
dir.create(baseDir)
setwd(baseDir)

# Create REPORTS folder, when QC report is finished this should be created in the QC_REPORT rmd
dir.create("REPORTS")
setwd(file.path(baseDir,"REPORTS"))
dir.create("DEG_ENRICHMENT")

saveDir = file.path(params$baseDir, "REPORTS", "DEG_ENRICHMENT", paste("Report",  params$ReportNum, sep = '_'))
#dataDir = file.path(baseDir,  "QCoutput", "221028_EXP005_BCH002")


if(!dir.exists(saveDir)){
  dir.create(saveDir, recursive = TRUE)
}
save = TRUE

conflicts_prefer(
  dplyr::select,
  dplyr::select,
  dplyr::filter,
  dplyr::rename,
  dplyr::mutate,
  base::intersect
)

theme_set(theme_bw(base_size = 14))
cbPalette <- c("#999999", "#E69F00", "#56B4E9", "#009E73", "#F0E442", "#0072B2", "#D55E00", "#CC79A7")
```

```{r functions }
source(file.path(params$DirPipeline, "../cleaned_functions.R"))

```


```{r load_meta_data}
library(readxl)

# load genesets
if (params$Organism == 'Human') {
    print(paste("Organism selected", params$Organism, sep = " "))
    Kegg = readRDS(file.path(params$DirDataForPipeline, "KEGG_All_human_symbol_240702.RDS"))
    Hallmark = read.gmt(file.path(params$DirDataForPipeline, "h.all.v2023.2.Hs.symbols.gmt"))
    Reactome = read.gmt(file.path(params$DirDataForPipeline, "c2.cp.reactome.v2023.2.Hs.symbols.gmt")) 
    Pfam_Interpro = readRDS(file.path(params$DirDataForPipeline, "Pfam_Interpro_251030.RDS"))
    # get custom genesets
    if (file.exists(params$Customgenesets_path)) {
        # get the genesets
        sheet_names <- excel_sheets(params$Customgenesets_path)
        sheet_names <- sheet_names[!sheet_names %in% c("INSTRUCTIONS", "SUMMARY", "Sheet1")]
        all_sheets <- sheet_names %>%
            map(~read_excel(params$Customgenesets_path, sheet = .) %>% dplyr::select(1))
        names(all_sheets) <- sheet_names
        Customgenesets <- bind_rows(all_sheets, .id = "sheet_name")
        names(Customgenesets) <- c("term", "gene")
        # get the geneset sumamry table
        sheet_names <- "SUMMARY"
        cutomgenesetsummarytable <- read_excel(params$Customgenesets_path, sheet = "SUMMARY")
    } else {
        print("No custom genesets file found")
    }
    
} else if (params$Organism == 'Mouse') {
    print(paste("Organism selected", params$Organism, sep = " "))
    Kegg = read.gmt(file.pathhead(Cu(params$DirDataForPipeline,  "c2.cp.kegg.v6.2.symbols_mouse.gmt")))
    Hallmark = read.gmt(file.path(params$DirDataForPipeline, "mh.all.v2024.1.Mm.symbols.gmt"))
    Reactome = read.gmt(file.path(params$DirDataForPipeline, "m2.cp.reactome.v2024.1.Mm.symbols.gmt"))
}

# TPM expression matrix

#TPM_expr_path = file.path(params$baseDir,"IMPORT_DATA", "TPM.tsv")
Chemo_path = params$Chemo_path
Cell_Dict_path = params$Cell_Dict_path
Contrast_path = params$Contrast_path
```

```{r get_gene_annotation, eval = TRUE}
library(biomaRt)

# gene annotations
if(params$Organism == 'Human'){
    
    if(file.exists(file.path(params$DirDataForPipeline, "geneAnns_Human.RDS"))){
        geneAnns = readRDS(file.path(params$DirDataForPipeline, "geneAnns_Human.RDS"))
        colnames(geneAnns)[2] = "symbol"
        geneAnns_unique <- geneAnns %>% group_by(symbol) %>% slice_sample(n = 1)
        
    }else{
        organismDataset <- "hsapiens_gene_ensembl"
        mart <- useMart("ENSEMBL_MART_ENSEMBL", dataset=organismDataset)
        geneAnns = getBM(attributes = c("ensembl_gene_id", "external_gene_name", "description", "gene_biotype"), mart = mart)
        saveRDS(geneAnns, file = file.path(params$DirDataForPipeline, "geneAnns_Human.RDS"))
        colnames(geneAnns)[2] = "symbol"
        # Eliminate redundancy in this data frame for gene symbols present in multiple rows. This is important to keep consistent the lists in the overlaps for the venn diagrams.

        geneAnns_unique <- geneAnns %>% group_by(symbol) %>% slice_sample(n = 1)
        
    }
    
    
} else if (params$Organism == 'Mouse') {
    
    if (file.exists(file.path(params$DirDataForPipeline, "geneAnns_Mouse.RDS"))) {
        geneAnns = readRDS(file.path(params$DirDataForPipeline, "geneAnns_Mouse.RDS"))
        colnames(geneAnns)[2] = "symbol"
        geneAnns_unique <- geneAnns %>% group_by(symbol) %>% slice_sample(n = 1)
        
    }else{
        organismDataset <- "mmusculus_gene_ensembl"
        mart <- useMart("ENSEMBL_MART_ENSEMBL", dataset=organismDataset)
        geneAnns = getBM(attributes = c("ensembl_gene_id", "external_gene_name", "description", "gene_biotype"), mart = mart)
        saveRDS(geneAnns, file = file.path(params$DirDataForPipeline, "geneAnns_Mouse.RDS"))
        colnames(geneAnns)[2] = "symbol"
        # Eliminate redundancy in this data frame for gene symbols present in multiple rows. This is important to keep consistent the lists in the overlaps for the venn diagrams.
        geneAnns_unique <- geneAnns %>% group_by(symbol) %>% slice_sample(n = 1)
    }
}
```


## Experimental design


```{r Exp,echo=FALSE, warning = FALSE,message=FALSE, fig.cap="Experimental design", fig.height=20, fig.width=24}

cat(params$ExpDescription)


if(file.exists(params$Experimental_design_path)){
  
    #knitr::opts_chunk$set(fig_width=20, fig_height=15)
    knitr::include_graphics(params$Experimental_design_path)
}else{
    cat("No experimental design scheme available")
}
```



-------------------

# Description Of DE Results

The names of the differential expression results are structured as **treatment** vs **control**. The following results are generated:

## Volcano Plot

The volcano plots show us a summary view of the differential expression results. Each point on the plot represents one gene in the experiment. Spots are colored according to the following criteria:

- **Blue**: padj < `r params$padj_thr_gene` & abs(LogFC) < `r params$logFC_thrs_gene`
- **Red**: padj < `r params$padj_thr_gene` & abs(LogFC) > `r params$logFC_thrs_gene`
- **Green**: padj > `r params$padj_thr_gene` & abs(LogFC) > `r params$logFC_thrs_gene`

The y-axis position represents the -log p-value: a higher value indicates that the gene is more significant. 

The x-axis position shows the log2 fold change for the gene between treatment or group 1 and control or group 2. Genes on the right-hand side of the plot increase in expression with treatment. Genes on the left-hand side decrease in expression with treatment.

## Top Up/Downregulated Genes

Heatmaps showing the scaled expression values of the top 50 up or downregulated genes in all samples. Genes in these heatmaps have a padj < `r params$padj_thr_gene` and  abs(LogFC) > `r params$logFC_thrs_gene`

## List Of Genes

This table contains the DE results for all genes with padj < `r params$padj_thr_gene` and  abs(LogFC) > `r params$logFC_thrs_gene`. Click the "Download" button to view a version of the data in Excel. The columns are as follows:

- **symbol**: Gene symbol
- **ensembl_gene_id**: ENSEMBL gene ID
- **description**: Gene name
- **log2FC**: Log2 fold change
- **pvalue**: Wald test p-value
- **padj**: Benjamini-Hochberg corrected p-value

## Gene Set Enrichment Analysis GSEA

Since so many genes are differentially expressed, it is difficult to review the entire experiment for biological themes in the expression changes. Gene Set Enrichment Analysis is one of several pathway analysis methods that can give us a bird’s eye view of the data. We’ll test the gene expression data for significant movement of collections of genes in known biological pathways. GSEA was performed on the following measure: sign(Log2FC) * -log10(pvalue)

We will use the following gene sets in this analysis:  

+ [Hallmark gene sets from MSigDb](https://www.gsea-msigdb.org/gsea/msigdb/collections.jsp#H). These gene sets "summarize and represent specific well-defined biological states or processes and display coherent expression. These gene sets were generated by a computational methodology based on identifying overlaps between gene sets in other MSigDB collections and retaining genes that display coordinate expression."
+ [Kyoto Encylopedia of Genes and Genomes (KEGG)](https://www.gsea-msigdb.org/gsea/msigdb/collections.jsp#C2). These gene sets are used to understand "high-level functions and utilities of the biological system, such as the cell, the organism and the ecosystem, from molecular-level information, especially large-scale molecular datasets generated by genome sequencing and other high-throughput experimental technologies."
+ [Reactome](https://www.gsea-msigdb.org/gsea/msigdb/collections.jsp#C2). 
+ [Enrichr](https://maayanlab.cloud/Enrichr/).  A large number of from a multitude of experimental sources. See [here](https://maayanlab.cloud/Enrichr/#libraries) for details on libraries of genesets.

For more information on the interpretation of these results, please see the "Interpreting results" section here: http://software.broadinstitute.org/gsea/doc/GSEAUserGuideFrame.html

### Signficance and GeneRatios 

These dotplot in GSEA captures both the significance and the GeneRatio (i.e. (count of core enrichment genes)/(count of pathway genes)) 

### Visualization pathways

These plots show the normalized enrichment score (x axis) for the enriched pathways. The size of the dot corresponds is proportional to the size of the pathway.

### Genes within pathways

These plots show shared genes among the most significant pathways. 

### Tree:pathway cluster

There is redundancy in the gene sets with many sharing genes/themes. These treeplots capture how the different terms relate to each other. Pathways sharing many genes will be closer in the treeplot. 

### Top Up/Downregulated Pathways

Enrichment plots showing the expression of the genes from the most enriched gene sets. The y-axis indicates the expression of the pathway genes. The x-axis is the rank order of the genes from the differential expression analysis. When there is significant gene set enrichment we should see a large number of genes at the beginning or end of the ranked gene list. 

For upregulated pathways you will see many pathway genes are on the left side of the plot and downregulated pathways will have pathway genes on the right of the plot. 


### List Of All Gene Sets

This table includes all gene sets in the pathway database. The columns are as follows:

* **ID:** Name of the gene set
* **link:** A link to information about the gene sets from mSigDB  (This contains information about how the gene sets were created.)
* **pvalue:** Uncorrected p-value
* **padj:** The Benjamini-Hochberg adjusted p-value (Generally we use a p-value cutoff of p<0.05 for this type of analysis.)
* **ES:** Uncorrected enrichment score
* **NES:** The normalized enrichment score (This is the score used to determine whether a gene set is moving up or down the gene rankings under the tested conditions. A positive score means that the genes are relatively overexpressed under treatment relative to the baseline condition. A negative score means that they are relatively underexpressed.)
* **size:** Size of the pathway after removing genes not observed in the dataset
* **core_enrichment:** Subset of genes that contribute most to the ES
* **Target_Chemo_esp:** Hits from chemoproteomics within the specific cell line associated to the molecule
* **Target_Chemo_all:** Hits from ALL experiments in chemoproteomics associated to the molecule

# Differential gene expression and pathway enrichment

```{r comparisons,  eval=TRUE, echo=FALSE, message=FALSE, warning=FALSE, results="asis", fig.show='hide'}
library(openxlsx)

# Read uniprot mapping
uniprot_map <- readr::read_tsv(params$Uniprot_map_db)
colnames(uniprot_map) <- c("gene", "Uniprot.ID")
# Read contrast file with DEG
DEG_df_all = read.csv(file.path(params$Contrasts_stats))


# check for 
List_contrasts = read.csv(params$Contrast_path)

comparisons  = List_contrasts %>%  dplyr::filter(reportNum == params$ReportNum)
comparisons$namecontrast =  paste0(comparisons$treat,"_Vs_",comparisons$untreat)

# Make contrast names valid names in r
# replace_hyphens <- function(x) {
#   gsub("-", "_", x)
# }
# 
# comparisons <- data.frame(lapply(comparisons, replace_hyphens), stringsAsFactors = FALSE)

deg_frame = function(contrast_id, DEG_df){
  
    DEG_df_cont = DEG_df %>% dplyr::filter(Contrast_ID == contrast_id)
    DEG_df_cont$padj = p.adjust(DEG_df_cont$P.Value, method = "BH")
    DEG_df_cont$gene = uniprot_map$gene[match(DEG_df_cont$Uniprot_ID,uniprot_map$Uniprot.ID )]
    DEG_df_cont = DEG_df_cont %>% drop_na(gene)
    DEG_df_cont = DEG_df_cont %>% dplyr::select(gene, P.Value, log2FC, padj)
    colnames(DEG_df_cont) = c("symbol", "pvalue", "log2FC", "padj")
    return(DEG_df_cont)
}



if (file.exists(file.path(saveDir, "contrasts", "all_contrasts.RDS"))){
  all_contrasts <- readRDS(file.path(saveDir, "contrasts", "all_contrasts.RDS"))
  all_contrasts = all_contrasts[comparisons$namecontrast]
} else {
  
   all_contrasts = list()
    if(!dir.exists(file.path(saveDir, "contrasts"))){
       dir.create(file.path(saveDir, "contrasts"), recursive = TRUE)
          
        print("creating contrast list")
        for(i in 1:length(comparisons$Contrast_ID)){
             
            deg_cont = deg_frame(contrast_id = comparisons$Contrast_ID[i] , DEG_df_all)
            all_contrasts[[comparisons$namecontrast[i]]] = deg_cont
            
        }
    }
   saveRDS(all_contrasts, file.path(saveDir, "contrasts", "all_contrasts.RDS")) 
    
}

```



```{r ChildComp, eval=TRUE, echo=FALSE, message=FALSE, warning=FALSE, results="asis"}

Childpath = params$DirPipeline
#names(all_contrasts)

res <- lapply(names(all_contrasts), function(name) {
   knitr::knit_child(file.path(Childpath, "child_reports","Child_perComparison.Rmd"),
                    envir = environment(),
                    quiet = TRUE,
                    options = list(
                      cache = FALSE,
                      fig.height = 10,
                      fig.width = 10
                    )
   )
  })

cat(unlist(res), sep="\n")

```

# Common DE Genes
In this section a Venn diagram, UpSet plot, and tables of genes are used to visualize the overalap of genes that are signficiantly differentially expressed across multiple comparisons.

An UpSet plot shows the same information as a Venn diagram, but when there are large numbers of groups an UpSet plot is a more straightforward way of visualizing the data. The number of DE genes in each comparison is listed on the left-hand side of the plot. The dots show possible intersections between the comparisons, and the bar graph at the top shows the total number of intersecting genes for each possible combination. It is similar to a Venn diagram, where the bars corresponding to a single dot are showing the number of genes that are unique to that comparison, and the bars corresponding to a column containing two dots are showing the number of genes that overalap between those two comparisons.

## All Comparisons

```{r Comp, eval = TRUE}
library(VennDiagram)
library(eulerr)
library(UpSetR)

comps <- names(all_contrasts)
sig_genes2 <- function(res_tibble, direction = "up", p_threshold = 0.05, logfc_threshold = 1) {
    if (direction == "up") {
        res <- res_tibble %>%
            dplyr::filter(padj < p_threshold & log2FC >= logfc_threshold) %>%
            distinct(symbol, .keep_all = TRUE)
    } else if (direction == "down") {
        res <- res_tibble %>%
            dplyr::filter(padj < p_threshold & log2FC <= -logfc_threshold) %>%
            distinct(symbol, .keep_all = TRUE)
    } else if (direction == "both") {
        res <- res_tibble %>%
            dplyr::filter(padj < p_threshold & abs(log2FC) >= logfc_threshold) %>%
            distinct(symbol, .keep_all = TRUE)
    }
    return(res)
}
plot_venn <- function(venn){
    plot(euler(venn),
         quantities = list(type = c("counts", "percent"), fontsize=8, col = "black"),
         lty = 1:3,
         labels = list(fontsize = 8, col = "black"),
         shape = "ellipse",
         edges = list(col = "black"))
}

sig_up <- sapply(all_contrasts[comps], function(x){sig_genes2(x,direction = "up", p_threshold = params$padj_thr_gene, logfc_threshold = params$logFC_thrs_gene)}, simplify = F, USE.NAMES = T)
sig_down <- sapply(all_contrasts[comps], function(x){sig_genes2(x,direction = "down", p_threshold = params$padj_thr_gene, logfc_threshold = params$logFC_thrs_gene)}, simplify = F, USE.NAMES = T)
sig_all <- sapply(all_contrasts[comps], function(x){sig_genes2(x,direction = "both", p_threshold = params$padj_thr_gene, logfc_threshold = params$logFC_thrs_gene)}, simplify = F, USE.NAMES = T)

venn_list_up <- sapply(sig_up, function(x){
    x %>% dplyr::filter(!is.na(symbol)) %>% dplyr::distinct(symbol) %>% pull(symbol) 
}
)

venn_list_down <- sapply(sig_down, function(x){
    x %>% dplyr::filter(!is.na(symbol)) %>% dplyr::distinct(symbol) %>% pull(symbol) 
}
)

upset_data_up <- fromList(venn_list_up)
upset_data_down <- fromList(venn_list_down)
```


### Upregulated Genes {.tabset}

#### Venn Diagram

```{r VennUp, results="asis", eval=TRUE}
if(any(unlist(lapply(venn_list_up, function(x) length(x)>0)))){
    plot_venn(venn_list_up)
} else {
    cat("*No DE genes*")
}
```

#### UpSet Plot

```{r UpUp, results="asis", eval=TRUE, fig.width = 24}
if(any(unlist(lapply(venn_list_up, function(x) length(x)>0)))){
    upset(upset_data_up, text.scale = c(1, 1, 1, 1, 1, 2), nsets = 10, nintersects = 100)
} else {
    cat("*No DE genes*")
}
```

#### Lists Of Genes {.tabset .tabset-dropdown}

```{r, results="asis", eval=TRUE}
find_all_combinations_overlaps <- function(sets_list) {

    all_overlaps <- list()
    # Loop through combination sizes
    for (k in 2:length(sets_list)) {
        combo_indices <- combn(seq_along(sets_list), k)

        # Loop through each combination of indices
        for (j in 1:ncol(combo_indices)) {
            combo <- combo_indices[, j]
            set_name <- paste("Overlap", paste(names(sets_list)[combo], collapse = "_AND_"), sep = "_")
            overlap <- Reduce(base::intersect, sets_list[combo])
            if(length(overlap)> 0 ){
            all_overlaps[[set_name]] <- overlap
            }
        }
    }
    return(all_overlaps)
}
if(any(unlist(lapply(venn_list_up, function(x) length(x)>0)))){
    # Find all overlaps
     tables <- find_all_combinations_overlaps(venn_list_up)
} 

#eval_tables_over_up = ifelse(length(tables)>0, TRUE, FALSE)
```


```{r, results = "hide", eval=TRUE}
if(any(unlist(lapply(venn_list_up, function(x) length(x)>0))) & length(tables)>0){
  src_list8 <- lapply(names(tables), function(comp) {
    src8 <- c("##### {{comp}} {.unnumbered}",
              "```{r}",
              "x <- as.data.frame(tables[['{{comp}}']])",
              "colnames(x) <- 'symbol'",
              "x <- merge(x, geneAnns_unique, all.x = TRUE, all.y = FALSE, by = 'symbol')",
              "x  %>% downloadableDT()",
              "```",
              "")
    knit_expand(text = src8)
  })
  
  out8 <- knit_child(text = unlist(src_list8), options = list(cache = FALSE, fig.height=10, fig.width=10))
} else {
  out8 <- knit_child(text="*No DE genes*")
}

#`r out8`
```

`r out8`




### Downregulated Genes {.tabset}

#### Venn Diagram

```{r, results="asis", eval=TRUE}
if(any(unlist(lapply(venn_list_down, function(x) length(x)>0)))){
  plot_venn(venn_list_down)
} else {
  cat("*No DE genes*")
}
```

#### UpSet Plot

```{r, results="asis",eval=TRUE, fig.width = 24}
if(any(unlist(lapply(venn_list_down, function(x) length(x)>0)))){
  upset(upset_data_down, text.scale = c(1, 1, 1, 1, 1, 2), nsets = 10, nintersects = 100)
} else {
  cat("*No DE genes*")
}
```

#### Lists Of Genes {.tabset .tabset-dropdown}

```{r, eval=TRUE}
if(any(unlist(lapply(venn_list_down, function(x) length(x)>0)))){
  tables <- find_all_combinations_overlaps(venn_list_down)
}
```

```{r, results = "hide",eval=TRUE}

if(any(unlist(lapply(venn_list_down, function(x) length(x)>0))) & length(tables)>0){
  src_list9 <- lapply(names(tables), function(comp) {
    src9 <- c("##### {{comp}} {.unnumbered}",
              "```{r}",
              "x <- as.data.frame(tables[['{{comp}}']])",
              "colnames(x) <- 'symbol'",
              "x <- merge(x, geneAnns_unique, all.x = TRUE, all.y = FALSE, by = 'symbol')",
              "x  %>% downloadableDT()",
              "```",
              "")
    knit_expand(text = src9)
  })
  
  out9 <- knit_child(text = unlist(src_list9), options = list(cache = FALSE))
} else {
  out9 <- knit_child(text="*No DE genes*")
}

#Take it out of the r chink
#`r out9`
```
  
`r out9`




# Comparison of Pathway Enrichment

This heatmap shows a summary of the significant GSEA results for the Hallmark gene sets across the comparisons done above. Each cell in the heatmap represents the gene set enrichment score for the gene set in that differential expression comparison. Each row represents one gene set, labeled on the right. Each column represents one differential expression comparison, where the reference is second group in the column name (control), and the heatmap is showing the pathways being either up or downregulated in the treatment samples as compared to the control samples.


## All Comparisons GSEA{.tabset}

### Hallmark

```{r comphall, eval = TRUE, results = 'asis' , echo = FALSE}

#thr <- 3 # threshold
geneset = 'Hallmark'
gseares_list <- lapply(names(all_contrasts), function(name) {
   
   filename <- paste(geneset, name,".RDS" , sep = '_')
   res <- readRDS(file.path(saveDir,"contrasts",name, "gsea_res", geneset, filename ))
   #res <- readRDS(file.path(saveDir, "gsea_res", paste0(name, " keggs.RDS")))
   gseares_tb <- na.omit(res$gseares_all@result)
   gseares_tb <- gseares_tb[order(gseares_tb$ID),]
   
   return(gseares_tb)
   
})
pathway_list <- lapply(gseares_list, function(gseares){
  return(gseares$ID)
})
pathway_isect <- Reduce(base::intersect, pathway_list)

gseares_list <- lapply(gseares_list, function(gseares) {
   gseares  <- gseares[order(gseares$ID),] %>% dplyr::filter(ID %in% pathway_isect)
   return(gseares)
})


# NES_list <- lapply(gseares_list, function(gseares){
#   return(gseares$NES)
# })
 NES_sign_padj_list <- lapply(gseares_list, function(gseares){
   return(sign(gseares$NES)*(-log10(gseares$p.adjust)))
 })
 
 


NES_mat <- as.data.frame(matrix(unlist(NES_sign_padj_list), nrow=length(unlist(NES_sign_padj_list[1]))))
colnames(NES_mat) <- names(all_contrasts)
rownames(NES_mat) <- pathway_isect

forfiltering <- lapply(gseares_list, function(gseares){
  return(vapply(gseares$p.adjust, getsigmarkerV2, FUN.VALUE="astring"))
})
forfiltering_mat <- as.data.frame(matrix(unlist(forfiltering), nrow=length(unlist(forfiltering[1]))))
colnames(forfiltering_mat) <- names(all_contrasts)
rownames(forfiltering_mat) <- pathway_isect

rowstokeep <- apply(forfiltering_mat, 1, function(x) !all(x==""))
NES_mat <- NES_mat[rowstokeep,, drop = FALSE]
forfiltering_mat <- forfiltering_mat[rowstokeep,,drop = FALSE]

# NES_mat[NES_mat < -thr] <- -thr
# NES_mat[NES_mat > thr] <- thr

# row.names(NES_mat) <- pathway_lookup[match(row.names(NES_mat), pathway_lookup$ID),"pathway"]

myfigheight <- calculate_fig_height(NES_mat)
old_opts <- knitr::opts_chunk$get()
on.exit(knitr::opts_chunk$set(old_opts)) 
knitr::opts_chunk$set(fig.height = myfigheight)


dir.create(file.path(saveDir,"contrasts","ComparisonPathways"), recursive = TRUE)


```

```{r comp_hallm_plt, echo=FALSE, eval = TRUE, results='asis'}
library(pheatmap)
# IMPORTANT NOTE: if you use the MAIN_DEG_ENRICH_perdrug.R to render this file, and these heatmaps are not displaying. Please close the enviornment open it again. THEN IT WORKS!
geneset = 'Hallmark'

filenameMat <- paste(geneset,"Heatmap_comparison_Pways",".RDS", sep = '_' )
filepathMat <- file.path(saveDir,"contrasts","ComparisonPathways", filenameMat)
saveRDS(NES_mat, filepathMat)
filenameMatsig <- paste(geneset,"Heatmap_comparison_Pways_SignifDisplay",".RDS", sep = '_' )
filepathMatsig <- file.path(saveDir,"contrasts","ComparisonPathways", filenameMatsig)
saveRDS(forfiltering_mat, filepathMatsig)

filename <- paste(geneset,"Heatmap_comparison_Pways",".jpeg", sep = '_' )
filepath <- file.path(saveDir,"contrasts","ComparisonPathways", filename)

#dir.create(file.path(saveDir,"contrasts","ComparisonPathways"), recursive = TRUE)
my_colors <- colorRampPalette(c("springgreen4", "white", "orchid4"))(100)
thr = max(abs(min(NES_mat)), max(NES_mat))
if (nrow(NES_mat)>1) {
 hm <-  pheatmap::pheatmap(NES_mat,
           display_numbers=forfiltering_mat,
           breaks=seq(from=-thr, to=thr, length=101),
           cluster_col=T,
           cluster_rows = T,
           show_rownames = T,
           show_colnames = T,
           main="Comparison of enriched pathways: sign(NES)*-log10(padj)",
           color = my_colors)
 
 print(hm)
 ggsave(filename= filepath, plot=hm , width = 8,height = myfigheight, units = 'in',limitsize = FALSE)
 
}else if (nrow(NES_mat)==1){
  hm <- pheatmap::pheatmap(NES_mat,
           display_numbers=forfiltering_mat,
           breaks=seq(from=-thr, to=thr, length=101),
           cluster_col=F,
           cluster_rows = F,
           show_rownames = T,
           show_colnames = T,
           main="Comparison of enriched pathways: sign(NES)*-log10(padj)",
           color = my_colors)
  print(hm)
  ggsave(filename= filepath, plot=hm , width = 8,height = myfigheight, units = 'in',limitsize = FALSE)
}else  {
  cat("**", paste("No significantly enriched pathways"), "**\n")
}



```


The asterisks in the heatmap tell you about the p-values associated with that GSEA test as such:

```
*** p_adj < 0.005
** padj < 0.05
* padj < 0.2
```

### Kegg

```{r compkegg, eval = TRUE, results = 'asis' , echo = FALSE}

#thr <- 100 # threshold
geneset = 'Kegg'
gseares_list <- lapply(names(all_contrasts), function(name) {
   
   filename <- paste(geneset, name,".RDS" , sep = '_')
   res <- readRDS(file.path(saveDir,"contrasts",name, "gsea_res", geneset, filename ))
   #res <- readRDS(file.path(saveDir, "gsea_res", paste0(name, " keggs.RDS")))
   gseares_tb <- na.omit(res$gseares_all@result)
   gseares_tb <- gseares_tb[order(gseares_tb$ID),]
   
   return(gseares_tb)
   
})
pathway_list <- lapply(gseares_list, function(gseares){
  return(gseares$ID)
})
pathway_isect <- Reduce(base::intersect, pathway_list)

gseares_list <- lapply(gseares_list, function(gseares) {
   gseares  <- gseares[order(gseares$ID),] %>% dplyr::filter(ID %in% pathway_isect)
   return(gseares)
})


# NES_list <- lapply(gseares_list, function(gseares){
#   return(gseares$NES)
# })

NES_sign_padj_list <- lapply(gseares_list, function(gseares){
   return(sign(gseares$NES)*(-log10(gseares$p.adjust)))
 })
 

NES_mat <- as.data.frame(matrix(unlist(NES_sign_padj_list), nrow=length(unlist(NES_sign_padj_list[1]))))
colnames(NES_mat) <- names(all_contrasts)
rownames(NES_mat) <- pathway_isect

forfiltering <- lapply(gseares_list, function(gseares){
  return(vapply(gseares$p.adjust, getsigmarkerV2, FUN.VALUE="astring"))
})
forfiltering_mat <- as.data.frame(matrix(unlist(forfiltering), nrow=length(unlist(forfiltering[1]))))
colnames(forfiltering_mat) <- names(all_contrasts)
rownames(forfiltering_mat) <- pathway_isect

rowstokeep <- apply(forfiltering_mat, 1, function(x) !all(x==""))
NES_mat <- NES_mat[rowstokeep,, drop = FALSE]
forfiltering_mat <- forfiltering_mat[rowstokeep,, drop = FALSE]

# NES_mat[NES_mat < -thr] <- -thr
# NES_mat[NES_mat > thr] <- thr

# row.names(NES_mat) <- pathway_lookup[match(row.names(NES_mat), pathway_lookup$ID),"pathway"]

myfigheight <- calculate_fig_height(NES_mat)
old_opts <- knitr::opts_chunk$get()
on.exit(knitr::opts_chunk$set(old_opts)) 
knitr::opts_chunk$set(fig.height = myfigheight)





```

```{r comp_Kegg_plt, echo=FALSE, eval = TRUE, results='asis'}
library(pheatmap)

# IMPORTANT NOTE: if you use the MAIN_DEG_ENRICH_perdrug.R to render this file, and these heatmaps are not displaying. Please close the enviornment open it again. THEN IT WORKS!

geneset = 'Kegg'

filenameMat <- paste(geneset,"Heatmap_comparison_Pways",".RDS", sep = '_' )
filepathMat <- file.path(saveDir,"contrasts","ComparisonPathways", filenameMat)
saveRDS(NES_mat, filepathMat)
filenameMatsig <- paste(geneset,"Heatmap_comparison_Pways_SignifDisplay",".RDS", sep = '_' )
filepathMatsig <- file.path(saveDir,"contrasts","ComparisonPathways", filenameMatsig)
saveRDS(forfiltering_mat, filepathMatsig)

filename <- paste(geneset,"Heatmap_comparison_Pways",".jpeg", sep = '_' )
filepath <- file.path(saveDir,"contrasts","ComparisonPathways", filename)
dir.create(file.path(saveDir,"contrasts","ComparisonPathways"), recursive = TRUE)

my_colors <- colorRampPalette(c("springgreen4", "white", "orchid4"))(100)
thr = max(abs(min(NES_mat)), max(NES_mat))
if (nrow(NES_mat)>1) {
 hm <-  pheatmap::pheatmap(NES_mat,
           display_numbers=forfiltering_mat,
           breaks=seq(from=-thr, to=thr, length=101),
           cluster_col=T,
           cluster_rows = T,
           show_rownames = T,
           show_colnames = T,
           main="Comparison of enriched pathways: sign(NES)*-log10(padj)",
           color = my_colors)
 print(hm)
 ggsave(filename= filepath, plot=hm , width = 8,height = myfigheight, units = 'in',limitsize = FALSE)
 
}else if (nrow(NES_mat)==1){
  hm <- pheatmap::pheatmap(NES_mat,
           display_numbers=forfiltering_mat,
           breaks=seq(from=-thr, to=thr, length=101),
           cluster_col=F,
           cluster_rows = F,
           show_rownames = T,
           show_colnames = T,
           main="Comparison of enriched pathways: sign(NES)*-log10(padj)",
           color = my_colors)
  print(hm)
  ggsave(filename= filepath, plot=hm , width = 8,height = myfigheight, units = 'in',limitsize = FALSE)
}else  {
  cat("**", paste("No significantly enriched pathways"), "**\n")
}



```



The asterisks in the heatmap tell you about the p-values associated with that GSEA test as such:

```
*** padj < 0.005
** padj < 0.05
* padj < 0.2
```

### Reactome

```{r compReac, eval = TRUE, results = 'asis' , echo = FALSE}

#thr <- 100 # threshold
geneset = 'Reactome'
gseares_list <- lapply(names(all_contrasts), function(name) {
   
   filename <- paste(geneset, name,".RDS" , sep = '_')
   res <- readRDS(file.path(saveDir,"contrasts",name, "gsea_res", geneset, filename ))
   #res <- readRDS(file.path(saveDir, "gsea_res", paste0(name, " keggs.RDS")))
   gseares_tb <- na.omit(res$gseares_all@result)
   gseares_tb$ID <- sub("REACTOME_", "", gseares_tb$ID)
   #gseares_tb$ID2 = sapply(gseares_tb$ID, function(x){substr(x,1,50)})
   gseares_tb <- gseares_tb[order(gseares_tb$ID),]
   
   
   return(gseares_tb)
   
})
pathway_list <- lapply(gseares_list, function(gseares){
  return(gseares$ID)
})
pathway_isect <- Reduce(base::intersect, pathway_list)

gseares_list <- lapply(gseares_list, function(gseares) {
   gseares  <- gseares[order(gseares$ID),] %>% dplyr::filter(ID %in% pathway_isect)
   return(gseares)
})


# NES_list <- lapply(gseares_list, function(gseares){
#   return(gseares$NES)
# })
NES_sign_padj_list <- lapply(gseares_list, function(gseares){
   return(sign(gseares$NES)*(-log10(gseares$p.adjust)))
 })

NES_mat <- as.data.frame(matrix(unlist(NES_sign_padj_list), nrow=length(unlist(NES_sign_padj_list[1]))))
colnames(NES_mat) <- names(all_contrasts)
rownames(NES_mat) <- pathway_isect

forfiltering <- lapply(gseares_list, function(gseares){
  return(vapply(gseares$p.adjust, getsigmarkerV2, FUN.VALUE="astring"))
})
forfiltering_mat <- as.data.frame(matrix(unlist(forfiltering), nrow=length(unlist(forfiltering[1]))))
colnames(forfiltering_mat) <- names(all_contrasts)
rownames(forfiltering_mat) <- pathway_isect

rowstokeep <- apply(forfiltering_mat, 1, function(x) !all(x==""))
NES_mat <- NES_mat[rowstokeep,,drop = FALSE]
forfiltering_mat <- forfiltering_mat[rowstokeep,,drop = FALSE]

# NES_mat[NES_mat < -thr] <- -thr
# NES_mat[NES_mat > thr] <- thr

# row.names(NES_mat) <- pathway_lookup[match(row.names(NES_mat), pathway_lookup$ID),"pathway"]

if (nrow(NES_mat) < 500) {
myfigheight <- calculate_fig_height(NES_mat)
old_opts <- knitr::opts_chunk$get()
on.exit(knitr::opts_chunk$set(old_opts)) 
knitr::opts_chunk$set(fig.height = myfigheight, fig.width = 30)
} else{
    
    myfigheight <- calculate_fig_height(NES_mat)
}   
    



```


```{r comp_Reacto_plt, eval = TRUE, echo=FALSE,warning = FALSE,message=FALSE, results = "asis"}
library(pheatmap)
# IMPORTANT NOTE: if you use the MAIN_DEG_ENRICH_perdrug.R to render this file, and these heatmaps are not displaying. Please close the enviornment open it again. THEN IT WORKS!
geneset = 'Reactome'

filenameMat <- paste(geneset,"Heatmap_comparison_Pways",".RDS", sep = '_' )
filepathMat <- file.path(saveDir,"contrasts","ComparisonPathways", filenameMat)
saveRDS(NES_mat, filepathMat)
filenameMatsig <- paste(geneset,"Heatmap_comparison_Pways_SignifDisplay",".RDS", sep = '_' )
filepathMatsig <- file.path(saveDir,"contrasts","ComparisonPathways", filenameMatsig)
saveRDS(forfiltering_mat, filepathMatsig)


filename <- paste(geneset,"Heatmap_comparison_Pways",".pdf", sep = '_' )
filepath <- file.path(saveDir,"contrasts","ComparisonPathways", filename)
dir.create(file.path(saveDir,"contrasts","ComparisonPathways"), recursive = TRUE)


thr = max(abs(min(NES_mat)), max(NES_mat))
my_colors <- colorRampPalette(c("springgreen4", "white", "orchid4"))(100)
if (nrow(NES_mat)>1 & nrow(NES_mat) < 450) {
 hm <-  pheatmap::pheatmap(NES_mat,
           display_numbers=forfiltering_mat,
           breaks=seq(from=-thr, to=thr, length=101),
           cluster_col=T,
           cluster_rows = T,
           show_rownames = T,
           show_colnames = T,
           fontsize_row = 4,
           main="Comparison of enriched pathways: sign(NES)*-log10(padj)",
           color = my_colors)
 print(hm)
 ggsave(filename= filepath, plot=hm , width = 20,height = myfigheight, units = 'in',limitsize = FALSE)



}else if(nrow(NES_mat) >=  450){
    hm <-  pheatmap::pheatmap(NES_mat,
           display_numbers=forfiltering_mat,
           breaks=seq(from=-thr, to=thr, length=101),
           cluster_col=T,
           cluster_rows = T,
           show_rownames = T,
           show_colnames = T,
           fontsize_row = 5,
           fontsize_col = 10,
           silent = TRUE,
           main="Comparison of enriched pathways: sign(NES)*-log10(padj)",
           filename = filepath,
           width = 10,
           height = myfigheight,
           color = my_colors)
    
    split_path <- strsplit(filepath, "Results_\\d+/")[[1]][2]
    print(paste("Heatmap is too large. Please find the pdf version here: ", split_path))
    

}else if (nrow(NES_mat)==1){
  hm <- pheatmap::pheatmap(NES_mat,
           display_numbers=forfiltering_mat,
           breaks=seq(from=-thr, to=thr, length=101),
           cluster_col=F,
           cluster_rows = F,
           show_rownames = T,
           show_colnames = T,
           main="Comparison of enriched pathways: sign(NES)*-log10(padj)",
           color = my_colors)
  print(hm)
  ggsave(filename= filepath, plot=hm , width = 20,height = myfigheight, units = 'in',limitsize = FALSE)

}else  {
  cat("**", paste("No significantly enriched pathways"), "**\n")
}



```


### Pfam_InterPro

```{r compPfam, eval = TRUE, results = 'asis' , echo = FALSE}

#thr <- 100 # threshold
geneset = 'Pfam_Interpro'
gseares_list <- lapply(names(all_contrasts), function(name) {
   
   filename <- paste(geneset, name,".RDS" , sep = '_')
   res <- readRDS(file.path(saveDir,"contrasts",name, "gsea_res", geneset, filename ))
   #res <- readRDS(file.path(saveDir, "gsea_res", paste0(name, " keggs.RDS")))
   gseares_tb <- na.omit(res$gseares_all@result)
   gseares_tb <- gseares_tb[order(gseares_tb$ID),]
   
   return(gseares_tb)
   
})
pathway_list <- lapply(gseares_list, function(gseares){
  return(gseares$ID)
})
pathway_isect <- Reduce(base::intersect, pathway_list)

gseares_list <- lapply(gseares_list, function(gseares) {
   gseares  <- gseares[order(gseares$ID),] %>% dplyr::filter(ID %in% pathway_isect)
   return(gseares)
})


# NES_list <- lapply(gseares_list, function(gseares){
#   return(gseares$NES)
# })

NES_sign_padj_list <- lapply(gseares_list, function(gseares){
   return(sign(gseares$NES)*(-log10(gseares$p.adjust)))
 })

NES_mat <- as.data.frame(matrix(unlist(NES_sign_padj_list), nrow=length(unlist(NES_sign_padj_list[1]))))
colnames(NES_mat) <- names(all_contrasts)
rownames(NES_mat) <- pathway_isect

forfiltering <- lapply(gseares_list, function(gseares){
  return(vapply(gseares$p.adjust, getsigmarkerV2, FUN.VALUE="astring"))
})
forfiltering_mat <- as.data.frame(matrix(unlist(forfiltering), nrow=length(unlist(forfiltering[1]))))
colnames(forfiltering_mat) <- names(all_contrasts)
rownames(forfiltering_mat) <- pathway_isect

rowstokeep <- apply(forfiltering_mat, 1, function(x) !all(x==""))
NES_mat <- NES_mat[rowstokeep,, drop = FALSE]
forfiltering_mat <- forfiltering_mat[rowstokeep,, drop = FALSE]

# NES_mat[NES_mat < -thr] <- -thr
# NES_mat[NES_mat > thr] <- thr

# row.names(NES_mat) <- pathway_lookup[match(row.names(NES_mat), pathway_lookup$ID),"pathway"]

myfigheight <- calculate_fig_height(NES_mat)
old_opts <- knitr::opts_chunk$get()
on.exit(knitr::opts_chunk$set(old_opts)) 
knitr::opts_chunk$set(fig.height = myfigheight)





```

```{r comp_Pfam_plt, echo=FALSE, eval = TRUE, results='asis'}
library(pheatmap)

geneset = 'Pfam_Interpro'

filenameMat <- paste(geneset,"Heatmap_comparison_Pways",".RDS", sep = '_' )
filepathMat <- file.path(saveDir,"contrasts","ComparisonPathways", filenameMat)
saveRDS(NES_mat, filepathMat)
filenameMatsig <- paste(geneset,"Heatmap_comparison_Pways_SignifDisplay",".RDS", sep = '_' )
filepathMatsig <- file.path(saveDir,"contrasts","ComparisonPathways", filenameMatsig)
saveRDS(forfiltering_mat, filepathMatsig)

filename <- paste(geneset,"Heatmap_comparison_Pways",".jpeg", sep = '_' )
filepath <- file.path(saveDir,"contrasts","ComparisonPathways", filename)
dir.create(file.path(saveDir,"contrasts","ComparisonPathways"), recursive = TRUE)

my_colors <- colorRampPalette(c("springgreen4", "white", "orchid4"))(100)
thr = max(abs(min(NES_mat)), max(NES_mat))
if (nrow(NES_mat)>1) {
 hm <-  pheatmap::pheatmap(NES_mat,
           display_numbers=forfiltering_mat,
           breaks=seq(from=-thr, to=thr, length=101),
           cluster_col=T,
           cluster_rows = T,
           show_rownames = T,
           show_colnames = T,
           main="Comparison of enriched pathways: sign(NES)*-log10(padj)",
           color = my_colors)
 print(hm)
 ggsave(filename= filepath, plot=hm , width = 8,height = myfigheight, units = 'in',limitsize = FALSE)
 
}else if (nrow(NES_mat)==1){
  hm <- pheatmap::pheatmap(NES_mat,
           display_numbers=forfiltering_mat,
           breaks=seq(from=-thr, to=thr, length=101),
           cluster_col=F,
           cluster_rows = F,
           show_rownames = T,
           show_colnames = T,
           main="Comparison of enriched pathways: sign(NES)*-log10(padj)",
           color = my_colors)
  print(hm)
  ggsave(filename= filepath, plot=hm , width = 8,height = myfigheight, units = 'in',limitsize = FALSE)
}else  {
  cat("**", paste("No significantly enriched pathways"), "**\n")
}



```



The asterisks in the heatmap tell you about the p-values associated with that GSEA test as such:

```
*** padj < 0.005
** padj < 0.05
* padj < 0.2
```






```{r comp_LogF_plot, echo=FALSE, eval = FALSE, results='asis'}

library(pheatmap)
genesets = c('Reactome', 'Hallmark', 'Kegg')

for(geneset in genesets){
    
    dir.create(file.path(saveDir,"contrasts","ComparisonPathways", geneset), recursive = TRUE)
    
    
    
    filenameMat <- paste(geneset,"Heatmap_comparison_Pways",".RDS", sep = '_' )
    filepathMat <- file.path(saveDir,"contrasts","ComparisonPathways", filenameMat)
    NES_mat = readRDS(filepathMat)
    
    # Create matrices with all comparisons all genes
    
    LogFC_list = lapply(colnames(NES_mat), function(comp){
        
        Tblgen <- readRDS(file.path(saveDir,"contrasts",comp, "DEG_df.RDS"))
        Tblgen_LogFC = Tblgen %>% dplyr::select(symbol, log2FC)
        colnames(Tblgen_LogFC) = c("symbol", comp)
        return(Tblgen_LogFC)
        
    })
    LogFC_Mat = LogFC_list %>% purrr::reduce(full_join, by = "symbol")
    
    # Star will be assign to genes with padj < 0.2
    Signif_list = lapply(colnames(NES_mat), function(comp){
        
        Tblgen <- readRDS(file.path(saveDir,"contrasts",comp, "DEG_df.RDS"))
        Tblgen_signif = Tblgen %>% dplyr::select(symbol, padj)
        Tblgen_signif$padj[Tblgen_signif$padj< 0.2] = '*'
        Tblgen_signif$padj[Tblgen_signif$padj> 0.2] = ' '
        colnames(Tblgen_signif) = c("symbol", comp)
        return(Tblgen_signif)
        
    })
    Signif_Mat = Signif_list %>% purrr::reduce(full_join, by = "symbol")
    
    
    
    lapply(rownames(NES_mat), function(pway) {
        
        print(pway)
        # Take leading genes for each significant pathway
        Lead_gen = lapply(colnames(NES_mat),function(name){
            
            filename <- paste(geneset, name,".RDS" , sep = '_')
            res <- readRDS(file.path(saveDir,"contrasts",name, "gsea_res", geneset, filename ))
            SignPwayTable = as.data.frame(res$gseares_all) %>% dplyr::filter(p.adjust < 0.2)
            SignPwayTable$ID <- sub("REACTOME_", "", SignPwayTable$ID)
            
            if(pway %in% SignPwayTable$ID){
                
                Lead_genes = str_split(SignPwayTable$core_enrichment[which( SignPwayTable$ID == pway)], '/')[[1]]
                
            }else{
                
                Lead_genes = c()
            }
            
            return(Lead_genes) 
        })
        Lead_gen_union = unique(unlist(Lead_gen))
        if(length(Lead_gen_union) != 0){
            # Generate heatmap matrix with these leading genes
            LogFC_Mat_pway = LogFC_Mat[match(Lead_gen_union, LogFC_Mat$symbol), ]
            LogFC_Mat_pway = LogFC_Mat_pway %>% column_to_rownames(var="symbol")
            Signif_Mat_pway = Signif_Mat[match(Lead_gen_union,Signif_Mat$symbol), ]
            Signif_Mat_pway = Signif_Mat_pway %>% column_to_rownames(var="symbol")
            
            # plot heatmaps
            
            
            LogFC_Mat_pway[LogFC_Mat_pway< -1] = -1
            LogFC_Mat_pway[LogFC_Mat_pway> 1] = 1
            
            paletteLength <- 50
            myColor <- colorRampPalette(c("blue", "white", "red"))(paletteLength)
            myBreaks <- c(seq(min(LogFC_Mat_pway), 0, length.out=ceiling(paletteLength/2) + 1),
                          seq(max(LogFC_Mat_pway)/paletteLength,  max(LogFC_Mat_pway), length.out=floor(paletteLength/2)))
            
            
            if(nrow(LogFC_Mat_pway)>2){
                Plt = pheatmap(LogFC_Mat_pway,
                               color = myColor,
                               display_numbers = Signif_Mat_pway,
                               show_rownames = TRUE,
                               border_color = NA,
                               fontsize = 10,
                               breaks=myBreaks,
                               scale = "none",
                               cluster_cols = TRUE,
                               cluster_rows = TRUE,
                               fontsize_row = 8)
            }else if(nrow(LogFC_Mat_pway) <= 2){
                
                Plt = pheatmap(LogFC_Mat_pway,
                               color = myColor,
                               display_numbers = Signif_Mat_pway,
                               show_rownames = TRUE,
                               border_color = NA,
                               fontsize = 10,
                               breaks=myBreaks,
                               scale = "none",
                               cluster_cols = FALSE,
                               cluster_rows = FALSE,
                               fontsize_row = 8)
                
                
                
                
                
            }
            
            filePlt_name_pdf = paste(pway, ".pdf", sep = '')
            filePlt_name_jpeg = paste(pway, ".jpeg", sep = '')
            filepathPlt = file.path(saveDir,"contrasts","ComparisonPathways", geneset,filePlt_name_pdf)
            filepathPlt_jpeg = file.path(saveDir,"contrasts","ComparisonPathways", geneset,filePlt_name_jpeg)
            
            # 10 genes in 2 inches
            pdf(file = filepathPlt, width = 12, height = (length(Lead_gen_union) *2/10+5))
            print( Plt)
            dev.off()
            
            jpeg(file = filepathPlt_jpeg, width = 12, height = (length(Lead_gen_union) *2/10+5), units = 'in', res= 400)
            print( Plt)
            dev.off()
            
        }
        
        
        
    })
}
```





