## `r name` 

### Differential Expression {.tabset}
```{r results = 'asis' , echo = FALSE, fig.width=8, fig.height=8}
cat('\n')
cat("####", "Volcano Plot (Padj)")
cat('\n')
if(params$workstream == "Proteomics"){
plot_enhanced_volcano(all_contrasts[[name]], FCcut = params$logFC_thrs_gene, PadjThr = params$padj_thr_gene, yaxis = "padj")
}else if(params$workstream == "Pisa"){
plot_enhanced_volcano(all_contrasts[[name]], FCcut = params$logFC_thrs_gene, PadjThr = params$padj_thr_gene, yaxis = "padj")
}else if(params$workstream == "PAL"){
plot_enhanced_volcano_PAL(all_contrasts[[name]], FCcut = params$logFC_thrs_gene, PadjThr = params$padj_thr_gene, yaxis = "padj")
    
}    
cat('\n')             

cat('\n')
cat("####", "Volcano Plot (Pvalue)")
cat('\n')
if(params$workstream == "Proteomics"){
plot_enhanced_volcano(all_contrasts[[name]], FCcut = params$logFC_thrs_gene, PadjThr = params$padj_thr_gene, yaxis = "pvalue")
}else if(params$workstream == "Pisa"){
plot_enhanced_volcano(all_contrasts[[name]], FCcut = params$logFC_thrs_gene, PadjThr = params$padj_thr_gene, yaxis = "pvalue")
}else if(params$workstream == "PAL"){
plot_enhanced_volcano_PAL(all_contrasts[[name]], FCcut = params$logFC_thrs_gene, PadjThr = params$padj_thr_gene, yaxis ="pvalue")    
    
}    
cat('\n')      


# cat('\n')
# cat("####", "Top Up/Downregulated Genes {.tabset .tabset-pills}")
# cat('\n')
# 
# cat('\n')
# cat("#####", "Top Up-regulated Genes")
# cat('\n')
# Top_up_filename <- file.path(saveDir, "contrasts", name, "Top_up_DEGs.jpeg")
# if(file.exists(Top_up_filename)){
# cat('\n')
# writeLines(paste0("![](",Top_up_filename,")"))
# cat('\n\n')
# }else{
#   cat("No significant upregulated genes")
# }
# cat('\n')

# cat('\n')
# cat("#####", "Top Down-regulated Genes")
# cat('\n')
# Top_dn_filename <- file.path(saveDir, "contrasts", name, "Top_dn_DEGs.jpeg")
# if(file.exists(Top_dn_filename)){
# cat('\n')
# writeLines(paste0("![](",Top_dn_filename,")"))
# cat('\n\n')
# }else{
#   cat("No significant upregulated genes")
# }
# cat('\n\n')


cat('\n')
cat("####", "Table of DE genes")
cat('\n')

if(params$workstream == "Proteomics"){
  
display_de_genes4_prot(mytable = all_contrasts[[name]],geneAnns = geneAnns_unique, filter = TRUE, distinct = TRUE, padj_cutoff = params$padj_thr_gene, name)
}else if(params$workstream == "Pisa"){
    
#display_de_genes4_pisa(mytable = all_contrasts[[name]], geneAnns = geneAnns_unique, filter = TRUE, distinct = FALSE, pval_cutoff = 0.01, name)
display_de_genes4_prot(mytable = all_contrasts[[name]],geneAnns = geneAnns_unique, filter = TRUE, distinct = TRUE, padj_cutoff = params$padj_thr_gene, name)
        
}else if(params$workstream == "PAL"){
    
display_de_genes4_PAL(mytable = all_contrasts[[name]],geneAnns = geneAnns_unique, filter = TRUE, distinct = TRUE, padj_cutoff = params$padj_thr_gene, name)    
}

cat('\n')

    
```


### Pathway enrichment GSEA {.tabset}
```{r results = 'asis' ,echo = FALSE, fig.width=9, fig.height=8}
# Define the cell line and drug to use in this comparison by using the info in comparisons
Cell_line = comparisons$cell_line[which(comparisons$namecontrast == name)]
Drug = comparisons$drug[which(comparisons$namecontrast == name)]

cat('\n')
cat("####", "Hallmark {.tabset}")
cat('\n')


gene_expression_fold = all_contrasts[[name]]$log2FC
names(gene_expression_fold) = all_contrasts[[name]]$symbol


res_hall <- gsea_results_logpval_prot(res_tib = all_contrasts[[name]], 
                                 geneset = Hallmark, 
                                 name, 
                                 Chemo_path = params$Chemo_path, 
                                 Cellline = Cell_line , 
                                 Celline_Dict_Chemo_path = params$Cell_Dict_path, 
                                 drug = Drug, 
                                 Organism = params$Organism,
                                 Workstream = params$workstream)




cat('\n')
cat("#####", "Pathway visualization")
cat('\n')
filename <- paste("Hallmark", "Whole_Vis", name,'.html', sep = '_')
filepath <- file.path(saveDir,"contrasts",name, "gsea_res", "Hallmark", filename )

CompleteVisualPathwaysGsea_V2(res_hall$gsea_table, filepath)
cat('\n')


cat('\n')
cat("#####", "Signficant pathways GeneRatios")
cat('\n')
if(nrow(res_hall$gseares@result)>0 ){
dotplot(res_hall$gseares)
}else{
 cat("No significant pathways")   
    
}    
cat('\n')

# filename <- paste("Hallmark", "Dotplot", name,'.jpeg', sep = '_')
# filepath <- file.path(saveDir,"contrasts",name, "gsea_res", "Hallmark", filename )
# dotplot(res_hall$gseares)
# cat('\n')
# jpeg(file = filepath, width = 8, height = 8, units = "in", res = 300)
# dotplot(res_hall$gseares)
# dev.off()
# cat('\n')




cat('\n')
cat("#####", " Top pathways vs NES")
cat('\n')
filename <- paste("Hallmark", "DotplotV2", name,'.jpeg', sep = '_')
filepath <- file.path(saveDir,"contrasts",name, "gsea_res", "Hallmark", filename )

VisualPathways(res_hall$gsea_table, filepath)
cat('\n')

cat('\n')
cat("#####", "Genes within pathways")
cat('\n')
cnetplot(res_hall$gseares, cex_label_gene=0.3, cex_label_category = 0.5, showCategory = 8, foldChange = gene_expression_fold) + scale_color_gradient2(
    midpoint = 0,                    # Neutral point corresponds to no change
    low = "blue", high = "red",      # Low values (downregulated) are blue, high are red
    mid = "white",
    
  )
cat('\n')


cat('\n')
cat("#####", "Tree: pathway cluster ")
cat('\n')
if(nrow(res_hall$gsea_table) > 5){
sim <- pairwise_termsim(res_hall$gseares)
treeplot(sim, hclust_method = 'average')
}else{
    cat('\n')
    cat("**", paste("Not enough pathways to fit a tree"), "**\n")
    cat('\n')
}
cat('\n')


cat('\n')
cat("#####", "Top upregulated")
cat('\n')

plot_top_gsea(res_hall, top='up')
cat('\n')

cat('\n')
cat("#####", "Top Downregulated")
cat('\n')

plot_top_gsea(res_hall, top='down')
cat('\n')

cat('\n')
cat("#####", "Table of enriched pathways")
cat('\n')

downloadableDTExcel(res_hall$gsea_table %>% dplyr::select(ID, pathway,pval, padj, ES, NES, size, core_enrichment, link,Target_Chemo_esp, Target_Chemo_all), escape=FALSE) %>% formatSignif(columns = c('pval','padj', 'ES', 'NES'), digits = 3)
cat('\n')


cat('\n')
cat("####", "Kegg {.tabset}")
cat('\n')



res_kegg <- gsea_results_logpval_prot(all_contrasts[[name]], geneset = Kegg, name, Chemo_path = params$Chemo_path, Cellline = Cell_line , Celline_Dict_Chemo_path = Cell_line, drug = Drug, Organism = params$Organism, Workstream = params$workstream)


cat('\n')
cat("#####", "Pathway visualization")
cat('\n')
filename <- paste("Kegg", "Whole_Vis", name,'.html', sep = '_')
filepath <- file.path(saveDir,"contrasts",name, "gsea_res", "Kegg", filename )


CompleteVisualPathwaysGsea_V2(res_kegg $gsea_table, filepath)
cat('\n')




cat('\n')
cat("#####", "Significance and GeneRatios")
cat('\n')
if(nrow(res_kegg$gseares@result)>0 ){
dotplot(res_kegg$gseares)
}else{
 cat("No significant pathways")   
    
}    
cat('\n')

# filename <- paste("Hallmark", "Dotplot", name,'.jpeg', sep = '_')
# filepath <- file.path(saveDir,"contrasts",name, "gsea_res", "Hallmark", filename )
# dotplot(res_hall$gseares)
# cat('\n')
# jpeg(file = filepath, width = 8, height = 8, units = "in", res = 300)
# dotplot(res_hall$gseares)
# dev.off()
# cat('\n')

cat('\n')
cat("#####", "Significance and NES")
cat('\n')
filename <- paste("Kegg", "DotplotV2", name,'.jpeg', sep = '_')
filepath <- file.path(saveDir,"contrasts",name, "gsea_res", "Kegg", filename )

VisualPathways(res_kegg$gsea_table, filepath)
cat('\n')

cat('\n')
cat("#####", "Genes within pathways")
cat('\n')
cnetplot(res_kegg$gseares, cex_label_gene=0.3, cex_label_category = 0.5, showCategory = 8, foldChange = gene_expression_fold) + scale_color_gradient2(
    midpoint = 0,                    # Neutral point corresponds to no change
    low = "blue", high = "red",      # Low values (downregulated) are blue, high are red
    mid = "white",
)
cat('\n')

cat('\n')
cat("#####", "Tree: pathway cluster ")
cat('\n')
if(nrow(res_kegg$gsea_table) > 5){
sim <- pairwise_termsim(res_kegg$gseares)
treeplot(sim, hclust_method = 'average')
}else{
    cat('\n')
    cat("**", paste("Not enough pathways to fit a tree"), "**\n")
    cat('\n')
}
cat('\n')


cat('\n')
cat("#####", "Top upregulated")
cat('\n')

plot_top_gsea(res_kegg, top='up')
cat('\n')

cat('\n')
cat("#####", "Top Downregulated")
cat('\n')

plot_top_gsea(res_kegg, top='down')
cat('\n')

cat('\n')
cat("#####", "Table of enriched pathways")
cat('\n')

downloadableDTExcel(res_kegg$gsea_table %>% dplyr::select(ID, pathway,pval, padj, ES, NES, size, core_enrichment, link, Target_Chemo_esp, Target_Chemo_all), escape=FALSE) %>% formatSignif(columns = c('pval','padj', 'ES', 'NES'), digits = 3)
cat('\n')


cat('\n')
cat("####", "Reactome {.tabset}")
cat('\n')

res_React <- gsea_results_logpval_prot(all_contrasts[[name]], geneset = Reactome, name, Chemo_path = params$Chemo_path, Cellline = Cell_line , Celline_Dict_Chemo_path = params$Cell_Dict_path, drug = Drug,Organism = params$Organism, Workstream = params$workstream)

cat('\n')
cat("#####", "Pathway visualization")
cat('\n')
filename <- paste("Reactome", "Whole_Vis", name,'.html', sep = '_')
filepath <- file.path(saveDir,"contrasts",name, "gsea_res", "Reactome", filename )


CompleteVisualPathwaysGsea_V2(res_React$gsea_table, filepath)
cat('\n')




cat('\n')
cat("#####", "Significance and GeneRatios")
cat('\n')
if(nrow(res_React$gseares@result)>0 ){
dotplot(res_React$gseares)
}else{
 cat("No significant pathways")   
    
}    
cat('\n')

# filename <- paste("Hallmark", "Dotplot", name,'.jpeg', sep = '_')
# filepath <- file.path(saveDir,"contrasts",name, "gsea_res", "Hallmark", filename )
# dotplot(res_hall$gseares)
# cat('\n')
# jpeg(file = filepath, width = 8, height = 8, units = "in", res = 300)
# dotplot(res_hall$gseares)
# dev.off()
# cat('\n')

cat('\n')
cat("#####", "Significance and NES")
cat('\n')
filename <- paste("Reactome", "DotplotV2", name,'.jpeg', sep = '_')
filepath <- file.path(saveDir,"contrasts",name, "gsea_res", "Reactome", filename )

VisualPathways(res_React$gsea_table, filepath)
cat('\n')

cat('\n')
cat("#####", "Genes within pathways")
cat('\n')
cnetplot(res_React$gseares, cex_label_gene=0.3, cex_label_category = 0.5, showCategory = 8, foldChange = gene_expression_fold) + scale_color_gradient2(
    midpoint = 0,                    # Neutral point corresponds to no change
    low = "blue", high = "red",      # Low values (downregulated) are blue, high are red
    mid = "white",
    name = "NES" # Neutral values are white
  )
cat('\n')

cat('\n')
cat("#####", "Tree: pathway cluster ")
cat('\n')

if(nrow(res_React$gsea_table) > 5){
sim <- pairwise_termsim(res_React$gseares)
treeplot(sim, hclust_method = 'average', fontsize = 3)
}else{
    cat('\n')
    cat("**", paste("Not enough pathways to fit a tree"), "**\n")
    cat('\n')
}

cat('\n')


cat('\n')
cat("#####", "Top upregulated")
cat('\n')

plot_top_gsea(res_React, top='up')
cat('\n')

cat('\n')
cat("#####", "Top Downregulated")
cat('\n')

plot_top_gsea(res_React, top='down')
cat('\n')

cat('\n')
cat("#####", "Table of enriched pathways")
cat('\n')

downloadableDTExcel(res_React$gsea_table %>% dplyr::select(ID, pathway,pval, padj, ES, NES, size, core_enrichment, link, Target_Chemo_esp, Target_Chemo_all ), escape=FALSE) %>% formatSignif(columns = c('pval','padj', 'ES', 'NES'), digits = 3)
cat('\n')


cat('\n')
cat("####", "Pfam_InterPro {.tabset}")
cat('\n')

gene_expression_fold = all_contrasts[[name]]$log2FC
names(gene_expression_fold) = all_contrasts[[name]]$symbol

res_pfam <- gsea_results_logpval_prot(res_tib = all_contrasts[[name]], 
                                 geneset = Pfam_Interpro, 
                                 name, 
                                 Chemo_path = params$Chemo_path, 
                                 Cellline = Cell_line , 
                                 Celline_Dict_Chemo_path = params$Cell_Dict_path, 
                                 drug = Drug, 
                                 Organism = params$Organism,
                                 Workstream = params$workstream)

cat('\n')
cat("#####", "Pathway visualization")
cat('\n')
filename <- paste("Pfam_InterPro", "Whole_Vis", name,'.html', sep = '_')
filepath <- file.path(saveDir,"contrasts",name, "gsea_res", "Pfam_InterPro", filename )


CompleteVisualPathwaysGsea_V2(res_pfam$gsea_table, filepath)
cat('\n')



cat('\n')
cat("#####", "Signficance and GeneRatios")
cat('\n')
if(nrow(res_pfam$gseares@result)>0 ){
dotplot(res_pfam$gseares)
}else{
 cat("No significant pathways")   
    
}    
cat('\n')

# filename <- paste("Hallmark", "Dotplot", name,'.jpeg', sep = '_')
# filepath <- file.path(saveDir,"contrasts",name, "gsea_res", "Hallmark", filename )
# dotplot(res_hall$gseares)
# cat('\n')
# jpeg(file = filepath, width = 8, height = 8, units = "in", res = 300)
# dotplot(res_hall$gseares)
# dev.off()
# cat('\n')

cat('\n')
cat("#####", "Visualization pathways")
cat('\n')
filename <- paste("Pfam_InterPro", "DotplotV2", name,'.jpeg', sep = '_')
filepath <- file.path(saveDir,"contrasts",name, "gsea_res", "Pfam_Interpro", filename )

VisualPathways(res_pfam$gsea_table, filepath)
cat('\n')

cat('\n')
cat("#####", "Genes within pathways")
cat('\n')
cnetplot(res_pfam$gseares, cex_label_gene=0.3, cex_label_category = 0.5, showCategory = 8, foldChange = gene_expression_fold) + scale_color_gradient2(
    midpoint = 0,                    # Neutral point corresponds to no change
    low = "blue", high = "red",      # Low values (downregulated) are blue, high are red
    mid = "white",
    
  )
cat('\n')


cat('\n')
cat("#####", "Tree: pathway cluster ")
cat('\n')
if(nrow(res_pfam$gsea_table) > 5){
sim <- pairwise_termsim(res_pfam$gseares)
treeplot(sim, hclust_method = 'average')
}else{
    cat('\n')
    cat("**", paste("Not enough pathways to fit a tree"), "**\n")
    cat('\n')
}
cat('\n')


cat('\n')
cat("#####", "Top upregulated")
cat('\n')

plot_top_gsea(res_pfam, top='up')
cat('\n')

cat('\n')
cat("#####", "Top Downregulated")
cat('\n')

plot_top_gsea(res_pfam, top='down')
cat('\n')

cat('\n')
cat("#####", "Table of enriched pathways")
cat('\n')

downloadableDTExcel(res_pfam$gsea_table %>% dplyr::select(ID, pathway,pval, padj, ES, NES, size, core_enrichment, Target_Chemo_esp, Target_Chemo_all), escape=FALSE) %>% formatSignif(columns = c('pval','padj', 'ES', 'NES'), digits = 3)
cat('\n')






################################################################################################################################

# cat('\n')
# cat("####", "Custom genesets {.tabset}")
# cat('\n')
# 
# kable(cutomgenesetsummarytable)
# 
# gene_expression_fold = all_contrasts[[name]]$log2FC
# names(gene_expression_fold) = all_contrasts[[name]]$symbol
# 
# res_custom <- gsea_results_logpval_prot(res_tib = all_contrasts[[name]], geneset = Customgenesets, name, Chemo_path = params$Chemo_path, Cellline = Cell_line , Celline_Dict_Chemo_path = params$Cell_Dict_path, drug = Drug, Organism = params$Organism)
# 
# cat('\n')
# cat("#####", "Pathway visualization")
# cat('\n')
# filename <- paste("Customgenesets", "Whole_Vis", name,'.html', sep = '_')
# filepath <- file.path(saveDir,"contrasts",name, "gsea_res", "Customgenesets", filename )
# 
# CompleteVisualPathwaysGsea_V2(res_custom$gsea_table, filepath)
# cat('\n')
# 
# cat('\n')
# cat("#####", "Signficance and GeneRatios")
# cat('\n')
# if(nrow(res_custom$gseares@result)>0 ){
# dotplot(res_custom$gseares)
# }else{
#  cat("No significant pathways")
#     
# }    
# cat('\n')
# 
# # filename <- paste("Hallmark", "Dotplot", name,'.jpeg', sep = '_')
# # filepath <- file.path(saveDir,"contrasts",name, "gsea_res", "Hallmark", filename )
# # dotplot(res_hall$gseares)
# # cat('\n')
# # jpeg(file = filepath, width = 8, height = 8, units = "in", res = 300)
# # dotplot(res_hall$gseares)
# # dev.off()
# # cat('\n')
# 
# cat('\n')
# cat("#####", "Visualization pathways")
# cat('\n')
# filename <- paste("Customgenesets", "DotplotV2", name,'.jpeg', sep = '_')
# filepath <- file.path(saveDir,"contrasts",name, "gsea_res", "Customgenesets", filename )
# 
# VisualPathways(res_custom$gsea_table, filepath)
# cat('\n')
# 
# cat('\n')
# cat("#####", "Genes within pathways")
# cat('\n')
# cnetplot(res_custom$gseares, cex_label_gene=0.3, cex_label_category = 0.5, showCategory = 8, foldChange = gene_expression_fold) + scale_color_gradient2(
#     midpoint = 0,                    # Neutral point corresponds to no change
#     low = "blue", high = "red",      # Low values (downregulated) are blue, high are red
#     mid = "white",
#     
#   )
# cat('\n')
# 
# 
# cat('\n')
# cat("#####", "Tree: pathway cluster ")
# cat('\n')
# if(nrow(res_custom$gsea_table) > 5){
# sim <- pairwise_termsim(res_custom$gseares)
# treeplot(sim, hclust_method = 'average')
# }else{
#     cat('\n')
#     cat("**", paste("Not enough pathways to fit a tree"), "**\n")
#     cat('\n')
# }
# cat('\n')
# 
# 
# cat('\n')
# cat("#####", "Top upregulated")
# cat('\n')
# 
# plot_top_gsea(res_custom, top='up')
# cat('\n')
# 
# cat('\n')
# cat("#####", "Top Downregulated")
# cat('\n')
# 
# plot_top_gsea(res_custom, top='down')
# cat('\n')
# 
# cat('\n')
# cat("#####", "Table of enriched pathways")
# cat('\n')
# 
# downloadableDTExcel(res_custom$gsea_table %>% dplyr::select(ID, pathway,pval, padj, ES, NES, size, core_enrichment,Target_Chemo_esp, Target_Chemo_all), escape=FALSE) %>% formatSignif(columns = c('pval','padj', 'ES', 'NES'), digits = 3)
# cat('\n')


```

### Pathway enrichment Over-representation {.tabset}
```{r results = 'asis' ,eval = TRUE, echo = FALSE, fig.width=9, fig.height=8}
# Hallmark visualization

res_hall <- over_rep_results_logpval_prot(res_tib = all_contrasts[[name]], geneset = Hallmark, name, Chemo_path = params$Chemo_path, Cellline = Cell_line ,Celline_Dict_Chemo_path = params$Cell_Dict_path, drug = Drug,  PadjThr = params$padj_thr_gene, log2FCTHr = params$logFC_thrs_gene, Organism = params$Organism, Workstream  = params$workstream)
 
Eval_hall_over = FALSE
if(!is.null(res_hall$overrep)){
    if(nrow(res_hall$overrep_table)> 0){
      
        Eval_hall_over = TRUE
    }
}    

```

```{r results = 'asis' ,eval = Eval_hall_over, echo = FALSE, fig.width=9, fig.height=8}
cat('\n')
cat("####", "Hallmark {.tabset}")
cat('\n')
                             
    cat('\n')
    cat("#####", "Pathway visualization")
    cat('\n')
    filename <- paste("Hallmark", "Whole_Vis_over", name,'.html', sep = '_')
    filepath <- file.path(saveDir,"contrasts",name, "overrep_res", "Hallmark", filename )

    CompleteVisualPathwaysOver(res_hall$overrep_table, filepath)
    cat('\n')

    cat('\n')
    cat("#####", "Signficance and GeneRatios")
    cat('\n')
    dotplot(res_hall$overrep)
    cat('\n')
    
    # filename <- paste("Hallmark", "Dotplot", name,'.jpeg', sep = '_')
    # filepath <- file.path(saveDir,"contrasts",name, "gsea_res", "Hallmark", filename )
    # dotplot(res_hall$gseares)
    # cat('\n')
    # jpeg(file = filepath, width = 8, height = 8, units = "in", res = 300)
    # dotplot(res_hall$gseares)
    # dev.off()
    # cat('\n')
    
    
    cat('\n')
    cat("#####", "Genes within pathways")
    cat('\n')
    cnetplot(res_hall$overrep, cex_label_gene=0.3, cex_label_category = 0.5, showCategory = 8, foldChange = gene_expression_fold) + scale_color_gradient2(
    midpoint = 0,                    # Neutral point corresponds to no change
    low = "blue", high = "red",      # Low values (downregulated) are blue, high are red
    mid = "white",
    
  )
    cat('\n')
    
    
    cat('\n')
    cat("#####", "Tree: pathway cluster ")
    cat('\n')
    if(nrow(res_hall$overrep_table) > 5){
    sim <- pairwise_termsim(res_hall$overrep)
    treeplot(sim, hclust_method = 'average')
    }else{
        cat('\n')
        cat("**", paste("Not enough pathways to fit a tree"), "**\n")
        cat('\n')
    }
    cat('\n')
    
    
    cat('\n')
    cat("#####", "Table of enriched pathways")
    cat('\n')

    downloadableDTExcel(res_hall$overrep_table %>% dplyr::select(ID,GeneRatio, BgRatio, pvalue, p.adjust, geneID,Count,link, Target_Chemo_esp, Target_Chemo_all), escape=FALSE) %>% formatSignif(columns = c('pvalue','p.adjust'), digits = 3)
    cat('\n')
  
 


```



```{r results = 'asis' ,eval = TRUE, echo = FALSE, fig.width=9, fig.height=8}
# Kegg visualization
                               
res_kegg <- over_rep_results_logpval_prot(res_tib = all_contrasts[[name]], geneset = Kegg, name, Chemo_path = params$Chemo_path, Cellline = Cell_line ,Celline_Dict_Chemo_path = params$Cell_Dict_path, drug = Drug,  PadjThr = params$padj_thr_gene, log2FCTHr = params$logFC_thrs_gene, Organism = params$Organism, Workstream  = params$workstream)

Eval_kegg_over = FALSE
if(!is.null(res_kegg$overrep)){
    if(nrow(res_kegg$overrep_table)> 0){
      
        Eval_kegg_over = TRUE
    }
}    

```

```{r results = 'asis' ,eval = Eval_kegg_over, echo = FALSE, fig.width=9, fig.height=8}
cat('\n')
cat("####", "Kegg {.tabset}")
cat('\n')
                             
    
    cat('\n')
    cat("#####", "Pathway visualization")
    cat('\n')
    filename <- paste("Kegg", "Whole_Vis_over", name,'.html', sep = '_')
    filepath <- file.path(saveDir,"contrasts",name, "overrep_res", "Kegg", filename )

    CompleteVisualPathwaysOver(res_kegg$overrep_table, filepath)
    cat('\n')


    cat('\n')
    cat("#####", "Signficance and GeneRatios")
    cat('\n')
    dotplot(res_kegg$overrep)
    cat('\n')
    
    # filename <- paste("Hallmark", "Dotplot", name,'.jpeg', sep = '_')
    # filepath <- file.path(saveDir,"contrasts",name, "gsea_res", "Hallmark", filename )
    # dotplot(res_hall$gseares)
    # cat('\n')
    # jpeg(file = filepath, width = 8, height = 8, units = "in", res = 300)
    # dotplot(res_hall$gseares)
    # dev.off()
    # cat('\n')
    
    
    cat('\n')
    cat("#####", "Genes within pathways")
    cat('\n')
    cnetplot(res_kegg$overrep, cex_label_gene=0.3, cex_label_category = 0.5, showCategory = 8, foldChange = gene_expression_fold) + scale_color_gradient2(
    midpoint = 0,                    # Neutral point corresponds to no change
    low = "blue", high = "red",      # Low values (downregulated) are blue, high are red
    mid = "white",
    
  )
    cat('\n')
    
    
    cat('\n')
    cat("#####", "Tree: pathway cluster ")
    cat('\n')
    if(nrow(res_kegg$overrep_table) > 5){
    sim <- pairwise_termsim(res_kegg$overrep)
    treeplot(sim, hclust_method = 'average')
    }else{
        cat('\n')
        cat("**", paste("Not enough pathways to fit a tree"), "**\n")
        cat('\n')
    }
    cat('\n')
    
    
    cat('\n')
    cat("#####", "Table of enriched pathways")
    cat('\n')

    downloadableDTExcel(res_kegg$overrep_table %>% dplyr::select(ID,GeneRatio, BgRatio, pvalue, p.adjust, geneID,Count,link, Target_Chemo_esp, Target_Chemo_all), escape=FALSE) %>% formatSignif(columns = c('pvalue','p.adjust'), digits = 3)
    cat('\n')
  
 

```


```{r results = 'asis' ,eval = TRUE, echo = FALSE, fig.width=9, fig.height=8}
# Reactome visualization
                               
res_React <- over_rep_results_logpval_prot(res_tib = all_contrasts[[name]], geneset = Reactome, name, Chemo_path = params$Chemo_path, Cellline = Cell_line ,Celline_Dict_Chemo_path = params$Cell_Dict_path, drug = Drug,  PadjThr = params$padj_thr_gene, log2FCTHr = params$logFC_thrs_gene, Organism = params$Organism, Workstream  = params$workstream)

Eval_React_over = FALSE
if(!is.null(res_React$overrep)){
    if(nrow(res_React$overrep_table)> 0){
      
        Eval_React_over = TRUE
    }
}    

```

```{r results = 'asis' ,eval = Eval_React_over, echo = FALSE, fig.width=9, fig.height=8}
cat('\n')
cat("####", "Reactome {.tabset}")
cat('\n')
                             

    cat('\n')
    cat("#####", "Pathway visualization")
    cat('\n')
    filename <- paste("Reactome", "Whole_Vis_over", name,'.html', sep = '_')
    filepath <- file.path(saveDir,"contrasts",name, "overrep_res", "Reactome", filename )

    CompleteVisualPathwaysOver(res_React$overrep_table, filepath)
    cat('\n')

    cat('\n')
    cat("#####", "Signficance and GeneRatios")
    cat('\n')
    dotplot(res_React$overrep)
    cat('\n')
    
    # filename <- paste("Hallmark", "Dotplot", name,'.jpeg', sep = '_')
    # filepath <- file.path(saveDir,"contrasts",name, "gsea_res", "Hallmark", filename )
    # dotplot(res_hall$gseares)
    # cat('\n')
    # jpeg(file = filepath, width = 8, height = 8, units = "in", res = 300)
    # dotplot(res_hall$gseares)
    # dev.off()
    # cat('\n')
    
    
    cat('\n')
    cat("#####", "Genes within pathways")
    cat('\n')
    cnetplot(res_React$overrep, cex_label_gene=0.3, cex_label_category = 0.5, showCategory = 8, foldChange = gene_expression_fold) + scale_color_gradient2(
    midpoint = 0,                    # Neutral point corresponds to no change
    low = "blue", high = "red",      # Low values (downregulated) are blue, high are red
    mid = "white",
    
  )
    cat('\n')
    
    
    cat('\n')
    cat("#####", "Tree: pathway cluster ")
    cat('\n')
    if(nrow(res_React$overrep_table) > 5){
    sim <- pairwise_termsim(res_React$overrep_all)
    treeplot(sim, hclust_method = 'average')
    }else{
        cat('\n')
        cat("**", paste("Not enough pathways to fit a tree"), "**\n")
        cat('\n')
    }
    cat('\n')
    
    
    cat('\n')
    cat("#####", "Table of enriched pathways")
    cat('\n')

    downloadableDTExcel(res_React$overrep_table %>% dplyr::select(ID,GeneRatio, BgRatio, pvalue, p.adjust, geneID,link, Count,Target_Chemo_esp, Target_Chemo_all), escape=FALSE) %>% formatSignif(columns = c('pvalue', 'p.adjust'), digits = 3)
    cat('\n')
  
 

```


```{r results = 'asis' ,eval = TRUE, echo = FALSE, fig.width=9, fig.height=8}
# Pfam_Interpro visualization
                               
res_pfam <- over_rep_results_logpval_prot(res_tib = all_contrasts[[name]], geneset = Pfam_Interpro, name, Chemo_path = params$Chemo_path, Cellline = Cell_line ,Celline_Dict_Chemo_path = params$Cell_Dict_path, drug = Drug,  PadjThr = params$padj_thr_gene, log2FCTHr = params$logFC_thrs_gene, Organism = params$Organism, Workstream  = params$workstream)

Eval_Pfam_over = FALSE
if(!is.null(res_pfam$overrep)){
    if(nrow(res_pfam$overrep_table)> 0){
      
        Eval_Pfam_over = TRUE
    }
}    

```

```{r results = 'asis' ,eval = Eval_Pfam_over, echo = FALSE, fig.width=9, fig.height=8}
cat('\n')
cat("####", "Pfam InterPro {.tabset}")
cat('\n')
                             

    cat('\n')
    cat("#####", "Pathway visualization")
    cat('\n')
    filename <- paste("Pfam_Interpro", "Whole_Vis_over", name,'.html', sep = '_')
    filepath <- file.path(saveDir,"contrasts",name, "overrep_res", "Reactome", filename )

    CompleteVisualPathwaysOver(res_pfam$overrep_table, filepath)
    cat('\n')

    cat('\n')
    cat("#####", "Signficance and GeneRatios")
    cat('\n')
    dotplot(res_pfam$overrep)
    cat('\n')
    
    # filename <- paste("Hallmark", "Dotplot", name,'.jpeg', sep = '_')
    # filepath <- file.path(saveDir,"contrasts",name, "gsea_res", "Hallmark", filename )
    # dotplot(res_hall$gseares)
    # cat('\n')
    # jpeg(file = filepath, width = 8, height = 8, units = "in", res = 300)
    # dotplot(res_hall$gseares)
    # dev.off()
    # cat('\n')
    
    
    cat('\n')
    cat("#####", "Genes within pathways")
    cat('\n')
    cnetplot(res_pfam$overrep, cex_label_gene=0.3, cex_label_category = 0.5, showCategory = 8, foldChange = gene_expression_fold) + scale_color_gradient2(
    midpoint = 0,                    # Neutral point corresponds to no change
    low = "blue", high = "red",      # Low values (downregulated) are blue, high are red
    mid = "white",
    
  )
    cat('\n')
    
    
    cat('\n')
    cat("#####", "Tree: pathway cluster ")
    cat('\n')
    if(nrow(res_pfam$overrep_table) > 5){
    sim <- pairwise_termsim(res_pfam$overrep_all)
    treeplot(sim, hclust_method = 'average')
    }else{
        cat('\n')
        cat("**", paste("Not enough pathways to fit a tree"), "**\n")
        cat('\n')
    }
    cat('\n')
    
    
    cat('\n')
    cat("#####", "Table of enriched pathways")
    cat('\n')

    downloadableDTExcel(res_pfam$overrep_table %>% dplyr::select(ID,GeneRatio, BgRatio, pvalue, p.adjust, geneID, Count,Target_Chemo_esp, Target_Chemo_all), escape=FALSE) %>% formatSignif(columns = c('pvalue', 'p.adjust'), digits = 3)
    cat('\n')
  
 

```






```{r results = 'asis' ,eval = FALSE, echo = FALSE, fig.width=9, fig.height=8}
# Customgenesets visualization
                               
res_custom <- over_rep_results_logpval_prot(res_tib = all_contrasts[[name]], geneset = Customgenesets, name, Chemo_path = params$Chemo_path, Cellline = Cell_line ,Celline_Dict_Chemo_path = params$Cell_Dict_path, drug = Drug, PadjThr = params$padj_thr_gene, log2FCTHr = params$logFC_thrs_gene, Organism = params$Organism, Workstream  = params$workstream)

Eval_custom_over = FALSE
if(!is.null(res_custom$overrep)){
    if(nrow(res_custom$overrep_table)> 0){
      
        Eval_custom_over = TRUE
    }
}    

```

```{r results = 'asis' ,eval = FALSE, echo = FALSE, fig.width=9, fig.height=8}
cat('\n')
cat("####", "Custom genesets {.tabset}")
cat('\n')
kable(cutomgenesetsummarytable)                             


cat('\n')
cat("#####", "Signficance and GeneRatios")
cat('\n')
dotplot(res_custom$overrep)
cat('\n')

# filename <- paste("Hallmark", "Dotplot", name,'.jpeg', sep = '_')
    # filepath <- file.path(saveDir,"contrasts",name, "gsea_res", "Hallmark", filename )
    # dotplot(res_hall$gseares)
    # cat('\n')
    # jpeg(file = filepath, width = 8, height = 8, units = "in", res = 300)
    # dotplot(res_hall$gseares)
    # dev.off()
    # cat('\n')
    
    
    cat('\n')
    cat("#####", "Genes within pathways")
    cat('\n')
    cnetplot(res_custom$overrep, cex_label_gene=0.3, cex_label_category = 0.5, showCategory = 8, foldChange = gene_expression_fold) + scale_color_gradient2(
    midpoint = 0,                    # Neutral point corresponds to no change
    low = "blue", high = "red",      # Low values (downregulated) are blue, high are red
    mid = "white",
    
  )
    cat('\n')
    
    
    cat('\n')
    cat("#####", "Tree: pathway cluster ")
    cat('\n')
    if(nrow(res_custom$overrep_table) > 5){
    sim <- pairwise_termsim(res_custom$overrep_all)
    treeplot(sim, hclust_method = 'average')
    }else{
        cat('\n')
        cat("**", paste("Not enough pathways to fit a tree"), "**\n")
        cat('\n')
    }
    cat('\n')
    
    
    cat('\n')
    cat("#####", "Table of enriched pathways")
    cat('\n')

    downloadableDTExcel(res_custom$overrep_table %>% dplyr::select(ID,GeneRatio, BgRatio, pvalue, p.adjust, geneID,link, Count,Target_Chemo_esp, Target_Chemo_all), escape=FALSE) %>% formatSignif(columns = c('pvalue', 'p.adjust'), digits = 3)
    cat('\n')
  
 

```



### Enrichr

- running all enrichr genesets with their algorithm

```{r , results='hide'}
background <- all_contrasts[[name]] %>% dplyr::filter(!is.na(padj)) %>% pull(symbol)

all_db_results <- enrichr_results(
  res_tib = all_contrasts[[name]], 
  name = name,
  saveDir = saveDir,
  PadjThr = params$padj_thr_gene,
  log2FCTHr = params$logFC_thrs_gene,
  run_all = TRUE,
  background = background,
  Workstream  = params$workstream)

combined_results <- bind_rows(
  lapply(names(all_db_results), function(db_name) {
    df <- all_db_results[[db_name]]
    if(nrow(df) > 0) {
      df %>%
        mutate(Database = db_name) %>%
        dplyr::select(Database, everything())
    } else {
      NULL
    }
  }) %>% 
    Filter(Negate(is.null), .)
)

# recalculate padjust
combined_results <- combined_results %>% dplyr::select(-contains("Old."), Adjusted.P.value) %>% 
    mutate(Full_Adjusted.P.value = p.adjust(P.value, method = "BH")) %>%
    arrange(P.value) %>% 
    dplyr::select(Database, Term, P.value, Adjusted.P.value, everything()) %>% 
    # rename("Database_Rank"="Rank") %>% 
    dplyr::rename("Database_Adjusted.P.value"="Adjusted.P.value")

#linkpath is with respect to the place where the html is stored
filepath <- file.path(saveDir, "contrasts", name, "enrichr_res", paste0(name, "_all_enrichr_results.csv"))
rio::export(combined_results, file=filepath)
linkpath <- fs::path_rel(filepath, start=file.path(baseDir, "REPORTS"))
# (`r paste0("../DEG_ENRICHMENT/", basename(saveDir), "contrasts", name, "enrichr_res", paste0(name, "_all_enrichr_results.xlsx")))
```

Note that:

* Database adjusted pvalues (Database_Adjusted.P.value) are calculated for only the respective database's genesets. 
* Full adjusted pvalues (Full_Adjusted.P.value) are calculated for all genesets assayed.


[link to Enrichr results](`r linkpath`)
