---
title: "Chemoproteomics over-representation"
output: html_document
date: "2024-01-30"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Here we estimate whether the chemoproteomics target candidates are over-represented within the enriched pathways. Mainly whether we find them within the enriched pathways more often than what we would find them by chance in the total collection of Gene sets, for example KEGG or REACTOME.


```{r EnrichmentScheme,echo=FALSE, warning = FALSE,message=FALSE, fig.cap=""}


Path_Exp = "~/BULK-TRANSCRIPTOMICS/Transcriptomics_Pipeline/data/Data_for_pipeline/Enrichment_scheme.png"
knitr::opts_chunk$set(fig_width=12, fig_height=15) 
knitr::include_graphics(Path_Exp)

```


The following heatmaps show in blue the targets that are over-represented for a particular molecule. Only those with p-value < 0.05 are shown in blue. More specifically, log10(pvalue) is plotted. The cases where over-representation is not significant are shown in white with log10(pvalue) = 0. The star identifies for every molecule,  those genes that are 'hits' from chemoproteomics or other prior information.

```{r HeatmapChemoAll, echo=FALSE,warning = FALSE,message=FALSE, results = "asis", fig.width=10, fig.height=10}

library("readxl")
library('pheatmap')
library("dplyr")
library("stringr")

# Download Chemoproteomics targets
Target_list_path = "~/BULK-TRANSCRIPTOMICS/Transcriptomics_Pipeline/data/Data_for_pipeline/Target_list_Mouse_240131.RData"
load(Target_list_path)


FolderPath = "~/InVivoTranscriptomics/Results/Results_240129/PWAYS_INTEGRATION"
for(File in list.files(FolderPath)[grep("Chemo",list.files(FolderPath))]){
    
    cat('\n')
    cat("##", File)
    cat('\n')
    
    # KEGG
    cat("### KEGG")
    Chemo_Enrich_Kegg = read_excel(path = paste(FolderPath,File, sep = '/'), sheet = "Chemo_Enrich_Kegg")
    Chemo_Enrich_Kegg$Chemo_TargetTime = paste(Chemo_Enrich_Kegg$Chemo_Target,sapply(Chemo_Enrich_Kegg$CompCategory, function(x){str_split(x, '_')[[1]][1]}), sep = '_')
    annotation_row = Chemo_Enrich_Kegg %>% dplyr::select(CompCategory) %>% data.frame()
    rownames(annotation_row) = Chemo_Enrich_Kegg$Chemo_TargetTime
    matrix_kegg = Chemo_Enrich_Kegg[,c('Chemo_TargetTime', colnames(Chemo_Enrich_Kegg)[grep('P_val',colnames(Chemo_Enrich_Kegg))])] %>% as.data.frame()
    rownames(matrix_kegg) = matrix_kegg$Chemo_TargetTime
    matrix_kegg$Chemo_TargetTime = NULL
    matrix_kegg = as.matrix(matrix_kegg)
    matrix_kegg[matrix_kegg > 0.05] = 1
    colnames(matrix_kegg)  = sapply(colnames(matrix_kegg), function(x){str_split(x, '_')[[1]][1]})
    
    # labels for heatmap showing targets associated to molecules
    labels_kegg = matrix(' ', nrow = nrow(matrix_kegg), ncol = ncol(matrix_kegg))
    colnames(labels_kegg) = colnames(matrix_kegg)
    rownames(labels_kegg) = rownames(matrix_kegg)
    for(mol in colnames(labels_kegg)){
        
        Target_list_mol = Target_list %>% filter(drugs == mol)
        TarNames = sapply(rownames(matrix_kegg), function(x){str_split(x, '_')[[1]][1]})
        labels_kegg[TarNames %in% Target_list_mol$gene,mol] = "\u2731"
        
    }
    
    # Plot heatmap
    paletteLength <- 50
    myColor <- colorRampPalette(c( "navy", "white"))(paletteLength)
    myBreaks <- seq(min(log10(matrix_kegg)),0, length.out = paletteLength)
        
    P = pheatmap(log10(matrix_kegg), breaks=myBreaks, col = myColor,annotation_row=annotation_row, cluster_rows = FALSE, display_numbers = labels_kegg)
    print(P)
        
   cat('\n')
   
   cat("### REACTOME")
    Chemo_Enrich_React = read_excel(path = paste(FolderPath,File, sep = '/'), sheet = "Chemo_Enrich_React")
    Chemo_Enrich_React$Chemo_TargetTime = paste(Chemo_Enrich_React$Chemo_Target,sapply(Chemo_Enrich_React$CompCategory, function(x){str_split(x, '_')[[1]][1]}), sep = '_')
    annotation_row = Chemo_Enrich_React %>% dplyr::select(CompCategory) %>% data.frame()
    rownames(annotation_row) = Chemo_Enrich_React$Chemo_TargetTime
    matrix_React = Chemo_Enrich_React[,c('Chemo_TargetTime', colnames(Chemo_Enrich_React)[grep('P_val',colnames(Chemo_Enrich_React))])] %>% as.data.frame()
    rownames(matrix_React) = matrix_React$Chemo_TargetTime
    matrix_React$Chemo_TargetTime = NULL
    matrix_React = as.matrix(matrix_React)
    matrix_React[matrix_React > 0.05] = 1
    colnames(matrix_React)  = sapply(colnames(matrix_React), function(x){str_split(x, '_')[[1]][1]})
    
    # labels for heatmap showing targets associated to molecules
    labels_React = matrix(' ', nrow = nrow(matrix_React), ncol = ncol(matrix_React))
    colnames(labels_React) = colnames(matrix_React)
    rownames(labels_React) = rownames(matrix_React)
    for(mol in colnames(labels_React)){
        
        Target_list_mol = Target_list %>% filter(drugs == mol)
        TarNames = sapply(rownames(matrix_React), function(x){str_split(x, '_')[[1]][1]})
        labels_React[TarNames %in% Target_list_mol$gene,mol] = "\u2731"
        
    }
    # Plot heatmap
    paletteLength <- 50
    myColor <- colorRampPalette(c( "navy", "white"))(paletteLength)
    myBreaks <- seq(min(log10(matrix_React)),0, length.out = paletteLength)
        
    P = pheatmap(log10(matrix_React), breaks=myBreaks, col = myColor,annotation_row=annotation_row, cluster_rows = FALSE, display_numbers = labels_React)
    print(P)
        
   cat('\n')
    
    
}



```
