---
title: "<br><br> `r params$scinamicNum`: Differential gene expression and enrichment analysis of bulk-RNAseq data for `r params$drug` treated samples in `r params$cell_line` with `r params$stimulation` stimulation"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  bookdown::html_document2:
    collapsed: true
    fig_width: 8
    highlight: haddock
    keep_md: false
    theme: cerulean
    toc: yes
    toc_float:
      collapsed: yes
params:
  drug: "M255"
  cell_line: "THP-1"
  stimulation: "R848"
  scinamicNum: 'EXP004'
  baseDir: "/fsx/home/crivera/Novogene/RESULTS_FROM_DYNAMIC_PIPELINE/221020_EXP004_BCH002/240621_Results"
  DirDataForPipeline: "/fsx/home/crivera/BULK-TRANSCRIPTOMICS/Transcriptomics_Pipeline/data/Data_for_pipeline"
  DirPipeline: "/fsx/home/crivera/BULK-TRANSCRIPTOMICS/Transcriptomics_Pipeline/R"
  dataDir:  "/fsx/home/crivera/Novogene/RESULTS_FROM_PIPELINE/221020_EXP004_BCH002/240501_Results_THP1_R848/DESEQ_NORM"
  Contrast_path: "/fsx/home/crivera/Novogene/RESULTS_FROM_PIPELINE/221020_EXP004_BCH002/Data_For_Pipeline/List_contrasts.xlsx"
  
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, error=TRUE, fig.align="left",  dev="png", fig.height=6, fig.width=9, message=F, warning=F)
knitr::opts_knit$set(progress = FALSE)

library(tidyverse)
library(DT)
# library(biomaRt)
library(plotly)
library(EnhancedVolcano)
library(knitr)
#library(kableExtra)
library(glue)
library(devtools)
library(msigdbr)
library(ggthemes)
library(clusterProfiler)
library(enrichplot) # needed for term similarity calcs
library(DESeq2)
library(conflicted)
library(patchwork)
library(pheatmap)
library(metafolio)
#library(ggvenn)
#library(UpSetR)
library(ashr)

# source("~/repos/DiamondAge/report_templates/R_markdown_templates/_common_R_code/utilities.R")
# source("~/repos/DiamondAge/report_templates/R_markdown_templates/_common_R_code/rnaseq_de.R") # Most of the functions are in this file


# directories
Drug = params$drug
baseDir = params$baseDir
saveDir = file.path(baseDir, "DEG_ENRICHMENT", params$drug)
#dataDir = file.path(baseDir,  "QCoutput", "221028_EXP005_BCH002")


if(!dir.exists(saveDir)){
  dir.create(saveDir, recursive = TRUE)
}
save = TRUE

conflicts_prefer(
  dplyr::select,
  dplyr::select,
  dplyr::filter,
  dplyr::rename,
  dplyr::mutate,
  base::intersect
)

theme_set(theme_bw(base_size = 14))
cbPalette <- c("#999999", "#E69F00", "#56B4E9", "#009E73", "#F0E442", "#0072B2", "#D55E00", "#CC79A7")
```

```{r functions }
source(file.path(params$DirPipeline, "cleaned_functions.R"))
```


```{r load_meta_data}
library(readxl)
library(DESeq2)

Metadata <-read_xlsx(file.path(params$dataDir, "Norm_Data.xlsx"), sheet = 'Metadata')
#geneAnns <- readRDS(file.path(dataDir, "geneAnns.RDS"))
load(file.path(params$dataDir, "DESeq_Norm.RData"))
count_data = counts(deseqObj)
#keggs <- readRDS(file.path(dataDir, "keggs.RDS"))
#keggs_info <- readRDS(file.path(dataDir, "keggs_info.RDS"))
hallmarks = read.gmt(file.path(params$DirDataForPipeline, "h.all.v2023.2.Hs.symbols.gmt"))
#hallmarks <- read.gmt("/Users/johnhutchinson/repos/DiamondAge/report_templates/R_markdown_templates/_library/signatures/h.all.v6.1.symbols.gmt")
hallmark_t2g <- msigdbr(species = "Homo sapiens", category = "H") %>%  dplyr::select(gs_name, gene_symbol)
```


-------------------

# Description Of DE Results

The names of the differential expression results are structured as **treatment** vs **control**. The following results are generated:

## Volcano Plot

The volcano plots show us a summary view of the differential expression results. Each point on the plot represents one gene in the experiment. Spots are colored according to the following criteria:

- **Blue**: p-value < 0.05 & fold change < 1.5
- **Red**: p-value < 0.05 & fold change > 1.5
- **Green**: p-value > 0.05 & |fold change| < 1.5

The y-axis position represents the -log p-value: a higher value indicates that the gene is more significant. 

The x-axis position shows the log2 fold change for the gene between the treatment (timepoints) and control (Baseline) groups. Genes on the right-hand side of the plot increase in expression with treatment. Genes on the left-hand side decrease in expression with treatment.

## MA Plot
The MA plot shows the log2 fold change between experimental groups (M) on the y-axis against the log of the mean expression across all of the samples (A) on the x-axis for each gene (represented by dots). Spots are colored according to the following criteria:

- **Teal**: p-value < 0.05 & fold change <= 1.5
- **Red**: p-value < 0.05 & fold change >= 1.5
- **Grey**: p-value > 0.05

## Top Up/Downregulated Genes

Heatmaps showing the scaled expression values of the top 50 up or downregulated genes in all samples. Genes in these heatmaps have an FDR-adjusted p-value < 0.05. 

## List Of Genes

This table contains the DE results for all genes with a p-value < 0.05. Click the "Download" button to view a version of the data in Excel. The columns are as follows:

- **symbol**: Gene symbol
- **ensembl_gene_id**: ENSEMBL gene ID
- **description**: Gene name
- **log2FC**: Log2 fold change
- **pvalue**: Wald test p-value
- **padj**: Benjamini-Hochberg corrected p-value
- **statistic**: Wald test statistic
- **baseMean**: The mean of normalized counts of all samples, normalizing for sequencing depth (This helps to get a sense for the absolute level of expression for a given gene.)

## Gene Set Enrichment Analysis

Since so many genes are differentially expressed, it is difficult to review the entire experiment for biological themes in the expression changes. Gene Set Enrichment Analysis is one of several pathway analysis methods that can give us a bird’s eye view of the data. We’ll test the gene expression data for significant movement of collections of genes in known biological pathways.

We will use the following gene sets in this analysis:  

+ [Gene Ontologies](https:https://geneontology.org/). Gene ontologies (GO terms) are a standardized set of terms and concepts used to describe the function, biological process, and cellular location of gene products across different databases. Here we only use the Biological Process terms.
+ [Hallmark gene sets from MSigDb](https://www.gsea-msigdb.org/gsea/msigdb/collections.jsp#H). These gene sets "summarize and represent specific well-defined biological states or processes and display coherent expression. These gene sets were generated by a computational methodology based on identifying overlaps between gene sets in other MSigDB collections and retaining genes that display coordinate expression."
+ [Kyoto Encylopedia of Genes and Genomes (KEGG)](https://www.gsea-msigdb.org/gsea/msigdb/collections.jsp#C2). These gene sets are used to understand "high-level functions and utilities of the biological system, such as the cell, the organism and the ecosystem, from molecular-level information, especially large-scale molecular datasets generated by genome sequencing and other high-throughput experimental technologies."

For more information on the interpretation of these results, please see the "Interpreting results" section here: http://software.broadinstitute.org/gsea/doc/GSEAUserGuideFrame.html

### Signficance and GeneRatios

These dotplot capture both the significance and the GeneRatio (i.e. (count of core enrichment genes)/(count of pathway genes)) for log2FC ranked results for each GO term or KEGG pathway.

### Common Genes between terms

These heatmaps capture the common enriched genes in each gene set. Note that due to restrictions in the KEGG database, KEGG gene IDs are presented as EntrezIDs. 

### Term relationships

There is redundacny in the the GO and KEGG terms with many sharing genes/themes. These treeplots capture how the different terms relate to each other. Note that due to restrictions in the KEGG database, KEGG gene IDs are again shown as EntrezIDs. 

### Top Up/Downregulated Pathways

Enrichment plots showing the expression of the genes from the most enriched gene sets. The y-axis indicates the expression of the pathway genes. The x-axis is the rank order of the genes from the differential expression analysis. When there is significant gene set enrichment we should see a large number of genes at the beginning or end of the ranked gene list. 

For upregulated pathways you will see many pathway genes are on the left side of the plot and downregulated pathways will have pathway genes on the right of the plot. 


### List Of All Gene Sets

This table includes all gene sets in the pathway database. The columns are as follows:

* **pathway:** Name of the Hallmark gene set
* **link:** A link to information about the gene sets from mSigDB  (This contains information about how the gene sets were created.)
* **pvalue:** Uncorrected p-value
* **padj:** The Benjamini-Hochberg adjusted p-value (Generally we use a p-value cutoff of p<0.05 for this type of analysis.)
* **ES:** Uncorrected enrichment score
* **NES:** The normalized enrichment score (This is the score used to determine whether a gene set is moving up or down the gene rankings under the tested conditions. A positive score means that the genes are relatively overexpressed under treatment relative to the baseline condition. A negative score means that they are relatively underexpressed.)
* **size:** Size of the pathway after removing genes not observed in the dataset
* **core_enrichment:** Subset of genes that contribute most to the ES

# Differential gene expression and pathway enrichment

```{r comparisons,  results = 'asis'}
library(openxlsx)
source("~/BULK-TRANSCRIPTOMICS/Transcriptomics_Pipeline/R/DEG_FUNCTION.R")

# check for 
List_contrasts = read.xlsx(xlsxFile = params$Contrast_path)

#print("Only contrasts allowed after removing outliers will be calculated")
List_contrasts = List_contrasts %>% filter(treat %in% Metadata$CoarseCondition & untreat %in% Metadata$CoarseCondition)
comparisons <- List_contrasts %>%  filter(grepl(Drug, treat) | grepl(Drug, untreat))
comparisons$namecontrast =  paste0(comparisons$treat,"_vs_",comparisons$untreat)


if (file.exists(file.path(saveDir, "contrasts", "all_contrasts.RDS"))){
  all_contrasts <- readRDS(file.path(saveDir, "contrasts",  "all_contrasts.RDS"))
} else {
  print('Here')
  all_contrasts <- apply(comparisons,1, function(x){
    DEG_FUNCTION_DA(x,saveDir,Drug, Metadata, count_data, DEG_Method = "DESeq_Cons",MH_Method = 'BH', AdjustDeSeq =c("Plate.id"))
                    
  })
  names(all_contrasts) <- comparisons$namecontrast
  saveRDS(all_contrasts,file.path(saveDir, "contrasts",  "all_contrasts.RDS"))
}

```

```{r Norm, eval=FALSE}
# filter the metadata and vsd data to comparison samples
sample_meta <- sample_meta %>% filter(Treatment ==Drug | Treatment =="DMSO")
vsd <-readRDS(file.path(saveDir,  "vsd.RDS" )) %>% assay() %>% as.data.frame() %>% rownames_to_column("symbol")
vsd <- vsd %>% select(symbol, all_of(sample_meta$sample), contains("DMSO")) 
```

```{r dose, eval=FALSE}
# check to see if multiple dosages 
dosages <- sample_meta %>% filter(!is.na(conc_um)) %>% pull(conc_um) %>% unique()
multidose <- length(dosages)>1
```

```{r results="hide", eval = FALSE, fig.show='hide'}
mat_anno <- sample_meta %>% select(drug, stim, conc_um, rep)
anno_colors <- list(sample = setNames(gg_color_hue(length(unique(sample_meta$Sample_name))), unique(sample_meta$Sample_name)))

de_heatmaps_up <- lapply(names(all_contrasts), function(x){
  treat <- str_split(x, "_vs_", simplify = T)[,1]
  ctrl <- str_split(x, "_vs_", simplify = T)[,2]
  exp_dat <- vsd %>% select(symbol, matches(treat), matches(ctrl))
  top_genes <- all_contrasts[[x]] %>%
      filter(log2FC > 0, padj < 0.05) %>%
      top_n(50, abs(log2FC)) %>%
      pull(symbol)
  if(length(top_genes) == 0){
    return("No significant genes")
  }else{
    exp_dat_filtered <- exp_dat %>% filter(symbol %in% top_genes)
    exp_dat_filtered <- exp_dat_filtered %>% column_to_rownames(var = "symbol")
    exp_dat_filtered <- exp_dat_filtered %>% filter(rowSums(.) > 0)
    if(nrow(exp_dat_filtered)>1){
      require(dendsort)
      sort_hclust <- function(...) as.hclust(dendsort(as.dendrogram(...), isReverse = TRUE))
      cluster_rows <- sort_hclust(hclust(dist(exp_dat_filtered)))
      pheatmap(exp_dat_filtered, 
                         color = colorRampPalette(c("blue", "white", "red"))(200),
                         show_rownames = T,
                         annotation = mat_anno,
                         annotation_colors = anno_colors,
                         border_color = NA, 
                         fontsize = 10,
                         scale = "row",
                         cluster_cols = F,
                         cluster_rows = cluster_rows,
                         fontsize_row = 8)
    } else {
      pheatmap(exp_dat_filtered, 
                         color = colorRampPalette(c("blue", "white", "red"))(200),
                         show_rownames = T,
                         annotation = mat_anno,
                         annotation_colors = anno_colors,
                         border_color = NA, 
                         fontsize = 10,
                         scale = "row",
                         cluster_cols = F,
                         cluster_rows = F,
                         fontsize_row = 8)
    }
  }
})
names(de_heatmaps_up) <- names(all_contrasts)
dev.off()

de_heatmaps_down <- lapply(names(all_contrasts), function(x){
  treat <- str_split(x, "_vs_", simplify = T)[,1]
  ctrl <- str_split(x, "_vs_", simplify = T)[,2]
  exp_dat <- vsd %>% select(symbol, matches(treat), matches(ctrl))
  top_genes <- all_contrasts[[x]] %>%
      filter(log2FC < 0, padj < 0.05) %>%
      top_n(50, abs(log2FC)) %>%
      pull(symbol)
  if(length(top_genes) == 0){
    return("No significant genes")
  }else{
    exp_dat_filtered <- exp_dat %>% filter(symbol %in% top_genes)
    exp_dat_filtered <- exp_dat_filtered %>% column_to_rownames(var = "symbol")
    exp_dat_filtered <- exp_dat_filtered %>% filter(rowSums(.) > 0)
    if(nrow(exp_dat_filtered)>1){
      require(dendsort)
      sort_hclust <- function(...) as.hclust(dendsort(as.dendrogram(...), isReverse = TRUE))
      cluster_rows <- sort_hclust(hclust(dist(exp_dat_filtered)))
      pheatmap(exp_dat_filtered, 
                         color = colorRampPalette(c("blue", "white", "red"))(200),
                         show_rownames = T,
                         annotation = mat_anno,
                         annotation_colors = anno_colors,
                         border_color = NA, 
                         fontsize = 10,
                         scale = "row",
                         cluster_cols = F,
                         cluster_rows = cluster_rows,
                         fontsize_row = 8)
    } else {
      pheatmap(exp_dat_filtered, 
                         color = colorRampPalette(c("blue", "white", "red"))(200),
                         show_rownames = T,
                         annotation = mat_anno,
                         annotation_colors = anno_colors,
                         border_color = NA, 
                         fontsize = 10,
                         scale = "row",
                         cluster_cols = F,
                         cluster_rows = F,
                         fontsize_row = 8)
    }
  }
})
names(de_heatmaps_down) <- names(all_contrasts)
```




```{r ChildComp, eval=TRUE, echo=FALSE, message=FALSE, warning=FALSE, results="asis"}

Childpath = "/fsx/home/crivera/Novogene/RESULTS_FROM_DYNAMIC_PIPELINE/Pipeline_Dynamic"

res <- lapply(names(all_contrasts), function(name) {
   knitr::knit_child(file.path(Childpath, "Child_perComparison.Rmd"),
                    envir = environment(),
                    quiet = TRUE,
                    options = list(
                      cache = FALSE,
                      fig.height = 10,
                      fig.width = 10
                    )
   )
  })

cat(unlist(res), sep="\n")



```




```{r test knit_de_results, results="hide", eval = FALSE}
src_list7 <- lapply(names(all_contrasts), function(name) {
    src7 <- c("## {{name}}",
             "### Differential Expression {.tabset}",
             "#### Volcano Plot",
             "```{r}",
             "plot_enhanced_volcano(all_contrasts[['{{name}}']])",
             "```",
             "",
             "#### MA Plot",
             "```{r}",
             "plot_ma(all_contrasts[['{{name}}']])",
             "```",
             ""
             )
    knit_expand(text = src7)
})

out7 <- knit_child(text = unlist(src_list7), options = list(cache = FALSE, fig.height=10, fig.width=10))
```


```{r knit_de_results, results="hide",  eval = FALSE}
src_list7 <- lapply(names(all_contrasts), function(name) {
    src7 <- c("## {{name}}",
             "### Differential Expression {.tabset}",
             "#### Volcano Plot",
             "```{r}",
             "plot_enhanced_volcano(all_contrasts[['{{name}}']])",
             "```",
             "",
             "#### MA Plot",
             "```{r}",
             "plot_ma(all_contrasts[['{{name}}']])",
             "```",
             "",
             "#### Top Up/Downregulated Genes {.tabset .tabset-pills}",
             "##### Top Upregulated Genes",
             "```{r}",
             "de_heatmaps_up[['{{name}}']]",
             "```",
             "",
             "##### Top Downregulated Genes",
             "```{r}",
             "de_heatmaps_down[['{{name}}']]",
             "```",
             "",
             "#### Top DE Genes (by adjusted pvalue)",
             "```{r,results = 'asis'}",
             "display_de_genes3(all_contrasts[['{{name}}']], geneAnns, distinct = T, lfc_cutoff = 0)",
             "```",
             "",
             "### Gene Set Enrichment Analysis {.tabset}",
             "#### Gene Ontologies {.tabset}",
             "```{r}",
             "if(file.exists(file.path(saveDir, 'gsea_res', paste0('{{name}}', ' GO.RDS')))){",
             " res_go <- readRDS(file.path(saveDir, 'gsea_res', paste0('{{name}}', ' GO.RDS')))",
             "} else {",
             "res_go <- gsea_results_go_kegg(all_contrasts[['{{name}}']], name = '{{name}}',pval=1)",
             "}",
             "```",
             "",
             "##### Signficance and GeneRatios",
             "```{r}",
             "dotplot(res_go$gseares)",
             "```",
             "",
             "##### Common Genes between terms",
             "```{r}",
             "cnetplot(res_go$gseares, cex_label_gene=0.5)",
             "```",
             "",
             "##### Term relationships",
             "```{r}",
             "sim <- pairwise_termsim(res_go$gseares)",
             "treeplot(sim, hclust_method = 'average')",
             "```",
             "",
             "##### Top Upregulated",
             "```{r}",
             "plot_top_gsea(res_go, top='up')",
             "```",
             "",
             "##### Top Downregulated",
             "```{r}",
             "plot_top_gsea(res_go, top='down')",
             "```",
             "",
             "##### List Of All Gene Sets",
             "```{r}",
             "downloadableDT(res_go$gsea_table %>% select(ID, pathway, pvalue = pval, padj, ES, NES, size, core_enrichment, link), escape=FALSE) %>% formatSignif(columns = c('pvalue','padj', 'ES', 'NES'), digits = 3)",
             "```",
             "",
              "#### Hallmarks {.tabset}",
             "```{r}",
             "res_hall <- gsea_results2(all_contrasts[['{{name}}']], name = '{{name}}')",
             "```",
             "",
             "##### Signficance and GeneRatios",
             "```{r}",
             "dotplot(res_hall$gseares)",
             "```",
             "",
             "##### Common Genes between terms",
             "```{r}",
             "cnetplot(res_hall$gseares, cex_label_gene=0.5)",
             "```",
             "",
             "##### Term relationships",
             "```{r}",
             "sim <- pairwise_termsim(res_hall$gseares)",
             "treeplot(sim, hclust_method = 'average')",
             "```",
             "",
             "##### Top Upregulated",
             "```{r}",
             "plot_top_gsea(res_hall, top='up')",
             "```",
             "",
             "##### Top Downregulated",
             "```{r}",
             "plot_top_gsea(res_hall, top='down')",
             "```",
             "",
             "##### List Of All Gene Sets",
             "```{r}",
             "downloadableDT(res_hall$gsea_table %>% select(ID, pathway, pvalue = pval, padj, ES, NES, size, core_enrichment, link), escape=FALSE) %>% formatSignif(columns = c('pvalue','padj', 'ES', 'NES'), digits = 3)",
             "```",
             "",
             "#### KEGG {.tabset}",
             "```{r}",
             "res_kegg <- gsea_results2(all_contrasts[['{{name}}']], name = '{{name}}',geneset=keggs)",
             "```",
             "",
             "##### Signficance and GeneRatios",
             "```{r}",
             "dotplot(res_kegg$gseares)",
             "```",
             "",
             "##### Common Genes between terms",
             "```{r}",
             "cnetplot(res_kegg$gseares, cex_label_gene=0.5)",
             "```",
             "",
             "##### Term relationships",
             "```{r}",
             "sim <- pairwise_termsim(res_kegg$gseares)",
             "treeplot(sim, hclust_method = 'average')",
             "```",
             "",
             "##### Top Upregulated",
             "```{r}",
             "plot_top_gsea(res_kegg, top='up')",
             "```",
             "",
             "##### Top Downregulated",
             "```{r}",
             "plot_top_gsea(res_kegg, top='down')",
             "```",
             "",
             "##### List Of All Gene Sets",
             "```{r}",
             "downloadableDT(res_kegg$gsea_table %>% select(ID, pathway, pvalue = pval, padj, ES, NES, size, core_enrichment, link), escape=FALSE) %>% formatSignif(columns = c('pvalue','padj', 'ES', 'NES'), digits = 3)",
             "```",
             ""
             )
    knit_expand(text = src7)
})

out7 <- knit_child(text = unlist(src_list7), options = list(cache = FALSE, fig.height=10, fig.width=10))
```




