---
title: "<br><br> `r params$scinamicNums`: Integration across experiments containing the following coarse conditions `r params$CoarseCond`"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  bookdown::html_document2:
    collapsed: true
    fig_width: 8
    highlight: haddock
    keep_md: false
    theme: cerulean
    toc: yes
    toc_float:
      collapsed: yes
params:
  ConditionsComparisons_path: "/fsx/home/crivera/Novogene/RESULTS_FROM_PIPELINE/221101_EXP007_BCH003/Data_Files_Pipeline/Integration_Comparisons.xlsx"
  CoarseCond: "THP-1_LPS_M082"
  scinamicNums: "EXP007"
  baseDir : "/fsx/home/crivera/Novogene/RESULTS_FROM_PIPELINE/221101_EXP007_BCH003/240708_Results_THP1_LPS"
  DirDataForPipeline: "/fsx/home/crivera/BULK-TRANSCRIPTOMICS/Transcriptomics_Pipeline/data/Data_for_pipeline"
  DirPipeline: "/fsx/home/crivera/BULK-TRANSCRIPTOMICS/Transcriptomics_Pipeline/R"                    
  Chemo_path: "/fsx/home/crivera/BULK-TRANSCRIPTOMICS/Transcriptomics_Pipeline/data/Data_for_pipeline/Target_list_240728_w_InvitroTargets.RDS"                              
---
 

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, error=TRUE, fig.align="left",  dev="png", fig.height=6, fig.width=9, message=F, warning=F)
#knitr::opts_knit$set(progress = FALSE)

library(tidyverse)
library(DT)
library(biomaRt)
library(plotly)
library(knitr)
#library(kableExtra)
library(glue)
library(devtools)
library(msigdbr)
library(ggthemes)
library(clusterProfiler)
library(enrichplot) # needed for term similarity calcs
library(conflicted)
library(patchwork)
library(pheatmap)
library(metafolio)
library(ashr)
library(BiocParallel)

# source("~/repos/DiamondAge/report_templates/R_markdown_templates/_common_R_code/utilities.R")
# source("~/repos/DiamondAge/report_templates/R_markdown_templates/_common_R_code/rnaseq_de.R") # Most of the functions are in this file

Integration_Folder = file.path(params$baseDir, "INTEGRATION")
if(!dir.exists(Integration_Folder)){
  dir.create(Integration_Folder, recursive = TRUE)
}


conflicts_prefer(
  dplyr::select,
  dplyr::select,
  dplyr::filter,
  dplyr::rename,
  dplyr::mutate,
  base::intersect
)

theme_set(theme_bw(base_size = 14))
cbPalette <- c("#999999", "#E69F00", "#56B4E9", "#009E73", "#F0E442", "#0072B2", "#D55E00", "#CC79A7")
```

```{r functions }
source(file.path(params$DirPipeline, "cleaned_functions.R"))
```


```{r load_meta_data}
library(readxl)
library(DESeq2)


ConComp_tabl <-read_xlsx(params$ConditionsComparisons_path)

# This needs to be accomodated when mouse
Kegg = readRDS(file.path(params$DirDataForPipeline, "KEGG_All_human_symbol_240702.RDS"))
Hallmark = read.gmt(file.path(params$DirDataForPipeline, "h.all.v2023.2.Hs.symbols.gmt"))
Reactome = read.gmt(file.path(params$DirDataForPipeline, "c2.cp.reactome.v2023.2.Hs.symbols.gmt"))

genesets = c('Hallmark', 'Kegg', 'Reactome')

# Download expression of genes
Target_list = readRDS(params$Chemo_path)
TPM_expr_path = file.path(params$baseDir,"QC_PRENORMALIZATION", "TPM_count_expr.xlsx")
if(file.exists(TPM_expr_path)){

                TPM_expr = readRDS(TPM_expr_path)
                Target_list = Target_list %>% dplyr::filter(gene %in% TPM_expr$gene_name)
                Target_list$tpm_median = TPM_expr$median_tpm[match(Target_list$gene, TPM_expr$gene_name)]
}

```




```{r ComparisonsToDisplay,  eval=TRUE, echo=FALSE, message=FALSE, warning=FALSE, results="asis"}
library(openxlsx)

GseaTablesDisplay = list()
GseaTablesDisplay_all = list()


for( i in 1:nrow(ConComp_tabl)){
    
    file_path = ConComp_tabl$PathToGseaTable[i]
    file_name = str_split(ConComp_tabl$PathToGseaTable[i], '/')[[1]][length(str_split(ConComp_tabl$PathToGseaTable[i], '/')[[1]])][[1]]
    DisplayName = paste(c(ConComp_tabl$Cell_line[1],str_split(file_name, '_')[[1]]),collapse = '_')
        
    
    if(file.exists(file_path)){
        
       Gsea_temp = readRDS(file_path)
       
       GseaTablesDisplay[[DisplayName]] = Gsea_temp$gsea_table
       GseaTablesDisplay_all[[DisplayName]] = data.frame(Gsea_temp$gseares_all)
       
    }
    
}





```



```{r OverRepresentation,  eval=TRUE, echo=FALSE, message=FALSE, warning=FALSE, results="asis"}
library(openxlsx)

Chemo_overRepresentation = function(Df, Colname = 'Target_Chemo_all', Geneset, Chemo_Tar_geneset){
    
    # Takes a Df from pathway enrichment and all targets from chemoproteomics and outputs a data frame with the over-representation p-value
    
    Targets = unique(str_split(paste(Df[[Colname]], collapse = ', '), ', ')[[1]])
    Targets = Targets[Targets != ""]
    
    Stat_tar = lapply(Targets, function(tar){
         
         
         Tar_in_Pways = c()
         for(i in 1:nrow(Df)){
             
             Tar_in_Pway_t = tar %in% str_split(Df[[Colname]][i], ', ')[[1]]
             Tar_in_Pways = c( Tar_in_Pways, Tar_in_Pway_t )
              
         }
         
         x = sum(Tar_in_Pways) # P(X<= x)
         m = nrow(Chemo_Tar_geneset[[tar]]) # Number of pathways containing the target
         n = length(unique(Geneset$term)) - m # Number of pathways not containing the target
         k = nrow(Df) # Number of Pathways enriched
         # x-1 cause I want the right tail from X >= x
         pvalue =  1 - phyper(x-1,m,n,k,lower.tail = TRUE )
         Ratio_enrich = paste(as.character(x),"/",as.character(k))
         Ratio_geneset = paste(as.character(m), "/", as.character(length(unique(Geneset$term))))
         Stats_info = c("pvalue" = pvalue, "Ratio_enrich" = Ratio_enrich, "Ratio_geneset" = Ratio_geneset)
         
         return(Stats_info)
     })
     
    names(Stat_tar) = Targets
    Df_Chemo = as.data.frame(t(as.data.frame(Stat_tar)))
    Df_Chemo$padj = p.adjust(as.numeric(Df_Chemo$pvalue), method = 'BH')
    Df_Chemo$gene = rownames(Df_Chemo)
    
    
    return(Df_Chemo)
    
}


Integration_Folder_Chemo = file.path(params$baseDir, "INTEGRATION", "CHEMOPROTEOMICS")
if(!dir.exists(Integration_Folder_Chemo)){
  dir.create(Integration_Folder_Chemo, recursive = TRUE)
}


# Generate files to find gene sets that contain a particular target within selected gene sets

#Target_list = readRDS(params$Chemo_path)

Unique_Target_list = unique(Target_list$gene)

# KEGG list

# if(ORGANISM == 'Mouse'){
# 
#         GeneSet_Desc$to = sapply(GeneSet_Desc$to, function(x){str_split(x,' - Mus')[[1]][1]})
# 
# }
Chemo_Kegg_tar_path = file.path(Integration_Folder_Chemo,"Chemo_Tar_Kegg.RDS" )
if(!file.exists(Chemo_Kegg_tar_path)){
 Chemo_Tar_Kegg = list()
 for(Tar in Unique_Target_list){

        #Target_list_sel = Target_list %>% dplyr::filter(gene == Tar)
        GeneSetWithTar = Kegg %>% dplyr::filter(gene == Tar)
        #GeneSetWithTar$Desc = GeneSet_Desc$to[match(GeneSetWithTar$term, GeneSet_Desc$from)]
        Chemo_Tar_Kegg[[Tar]] = GeneSetWithTar

}
 saveRDS(Chemo_Tar_Kegg, file = Chemo_Kegg_tar_path )
}else{
    
    Chemo_Tar_Kegg = readRDS(Chemo_Kegg_tar_path)
}

# REACTOME list

Chemo_Reactome_tar_path = file.path(Integration_Folder_Chemo,"Chemo_Tar_Reactome.RDS" )
if(!file.exists(Chemo_Reactome_tar_path)){
 Chemo_Tar_Reactome = list()
 for(Tar in Unique_Target_list){

        #Target_list_sel = Target_list %>% dplyr::filter(gene == Tar)
        GeneSetWithTar = Reactome %>% dplyr::filter(gene == Tar)
        #GeneSetWithTar$Desc = GeneSet_Desc$to[match(GeneSetWithTar$term, GeneSet_Desc$from)]
        Chemo_Tar_Reactome[[Tar]] = GeneSetWithTar

}
 saveRDS(Chemo_Tar_Reactome, file = Chemo_Reactome_tar_path )
}else{
    
    Chemo_Tar_Reactome = readRDS(Chemo_Reactome_tar_path)
}



# Hallmark list

Chemo_Hallmark_tar_path = file.path(Integration_Folder_Chemo,"Chemo_Tar_Hallmark.RDS" )
if(!file.exists(Chemo_Hallmark_tar_path)){
 Chemo_Tar_Hallmark = list()
 for(Tar in Unique_Target_list){

        
        GeneSetWithTar = Hallmark %>% dplyr::filter(gene == Tar)
        Chemo_Tar_Hallmark[[Tar]] = GeneSetWithTar

}
 saveRDS(Chemo_Tar_Hallmark, file = Chemo_Hallmark_tar_path )
}else{
    
    Chemo_Tar_Hallmark = readRDS(Chemo_Hallmark_tar_path)
}


# Generate chemoproteomic for pathway enrichment

Colnames = c('Target_Chemo_all', 'Target_Chemo_esp')

for(colname in Colnames){

 Df_Chemo_hits = list()
 for(geneset in genesets){
    
     
    if(geneset == 'Kegg'){
        
        Geneset = Kegg
        Chemo_Tar_geneset = Chemo_Tar_Kegg
        
    }else if (geneset == 'Hallmark'){
        
        Geneset = Hallmark
        Chemo_Tar_geneset = Chemo_Tar_Hallmark
    }else if(geneset == 'Reactome'){
        
        Geneset = Reactome
        Chemo_Tar_geneset = Chemo_Tar_Reactome
        
    }
    
    
    
    
    GseaTablesDisplay_sel = GseaTablesDisplay[grep(geneset, names(GseaTablesDisplay))]
    
    for(j in 1:length(GseaTablesDisplay_sel)){
        
        Name = paste(str_split(names(GseaTablesDisplay_sel)[j], '_')[[1]][1:length(str_split(names(GseaTablesDisplay_sel)[j], '_')[[1]])-1], collapse = '_')
        
        # Check whether there is available data, otherwise don't proceed
        
        if(nrow(GseaTablesDisplay_sel[[j]]) > 0){
            
            if(unique(GseaTablesDisplay_sel[[j]][[colname]])[1] != 'No available data'){
        
                  Df_Chemo_hits_t = Chemo_overRepresentation(Df = GseaTablesDisplay_sel[[j]], Colname = colname, Geneset, Chemo_Tar_geneset)
                  # Check whether there is available data, otherwise don't proceed
                
                
                  if(nrow(Df_Chemo_hits_t)>0){ 
                    Df_Chemo_hits_t$geneset = geneset
                    
                  }
                
                  Df_Chemo_hits[[Name]] = Df_Chemo_hits_t
           }
        }
    
    }
    
 }

 Df_Chemo_hits_path = file.path(Integration_Folder_Chemo,paste("Chemo_hits", "Colname" ,colname, ".RDS", sep = '_'))
 if(length(Df_Chemo_hits)>0){
 saveRDS(Df_Chemo_hits, file = Df_Chemo_hits_path)
 }
}





```


# Over-representation of chemoproteomic targets 

Here we estimate whether the chemoproteomics target candidates are over-represented within the enriched pathways. Mainly whether we find them within the enriched pathways more often than what we would find them by chance in the total gene set collection, for example KEGG or REACTOME.


```{r EnrichmentScheme,echo=FALSE, warning = FALSE,message=FALSE, fig.cap=""}


Path_Exp = file.path(params$DirDataForPipeline, "Enrichment_scheme.png")
knitr::opts_chunk$set(fig_width=12, fig_height=15) 
knitr::include_graphics(Path_Exp)

```


The heatmaps show in blue the targets that are over-represented for a particular comparison. Only those targets expressed in the cell line/organism of the given comparison are shown. More specifically, -log10(padj) is plotted. The star identifies the level of significance of the padj value:

```
*** p-adj < 0.005
** p-adj < 0.05
* p-adj < 0.2

```




## Using all chemoproteomics targets associated to the molecule {.tabset}




```{r, echo=FALSE, results='asis', fig.show='hide'}
library(pheatmap)


genesets = c('Hallmark', 'Kegg', 'Reactome')

colname = 'Target_Chemo_all'
    
Df_Chemo_hits_path = file.path(Integration_Folder_Chemo,paste("Chemo_hits", "Colname" ,colname, ".RDS", sep = '_'))

if(file.exists(Df_Chemo_hits_path)){
    
      Df_Chemo_hits = readRDS(Df_Chemo_hits_path)
      Heatmap_matrices = list()
      for(geneset in genesets){
          
         Df_Chemo_hits_sel = Df_Chemo_hits[grep(geneset, names(Df_Chemo_hits))]
         Df_Chemo_hits_sel_filt = list()
         for(k in 1:length(Df_Chemo_hits_sel)){
             
             Df = Df_Chemo_hits_sel[[k]]
             Dfn = Df %>% dplyr::select(gene, padj)
             colnames(Dfn) = c('gene', names(Df_Chemo_hits_sel)[k])
             Df_Chemo_hits_sel_filt[[k]] = Dfn
         }
         
                               
         Df_Chemo_M = purrr::reduce(Df_Chemo_hits_sel_filt, full_join, by = 'gene' )
         Df_Chemo_M[is.na(Df_Chemo_M)] = 1
         Df_Chemo_M = Df_Chemo_M %>% column_to_rownames('gene')
         Df_Chemo_M_filt = Df_Chemo_M[rowSums(Df_Chemo_M < 0.2) !=0,]
         
         Df_Chemo_M_sign = matrix("", ncol = ncol(Df_Chemo_M_filt), nrow = nrow(Df_Chemo_M_filt)) 
         Df_Chemo_M_sign[Df_Chemo_M_filt <0.2 & Df_Chemo_M_filt > 0.05] = '*'
         Df_Chemo_M_sign[Df_Chemo_M_filt <= 0.05 & Df_Chemo_M_filt > 0.005] = '**'
         Df_Chemo_M_sign[Df_Chemo_M_filt <=0.005] = '***'
         colnames(Df_Chemo_M_sign) = colnames(Df_Chemo_M_filt)
         rownames(Df_Chemo_M_sign) = rownames(Df_Chemo_M_filt)
         Df_Chemo_M_log = -log10(Df_Chemo_M_filt)
         MaxNum = max(Df_Chemo_M_log[Df_Chemo_M_log != Inf])
         Df_Chemo_M_log[Df_Chemo_M_log == Inf] = MaxNum +10
         
         Heatmap_matrices[[geneset]] = list('Matrix' = Df_Chemo_M_log, Sign_display = Df_Chemo_M_sign)
         
         
         
      
      }    
        
        res <- lapply(names(Heatmap_matrices), function(name) {
   knitr::knit_child(file.path(params$DirPipeline, "Child_Chemoproteomics_heatmap.Rmd"),
                    envir = environment(),
                    quiet = TRUE,
                    options = list(
                      cache = FALSE
                    )
   )
  })

         cat(unlist(res), sep="\n")
         
}else{
    
    cat("No data available")
   
    
}

```

## Using chemoproteomics targets only associated to the specific cellline/tissue {.tabset}

```{r, echo=FALSE, results='asis', fig.show='hide'}
library(pheatmap)

genesets = c('Hallmark', 'Kegg', 'Reactome')

colname = 'Target_Chemo_esp'
    
Df_Chemo_hits_path = file.path(Integration_Folder_Chemo,paste("Chemo_hits", "Colname" ,colname, ".RDS", sep = '_'))

if(file.exists(Df_Chemo_hits_path)){
    
      Df_Chemo_hits = readRDS(Df_Chemo_hits_path)
      Heatmap_matrices = list()
      for(geneset in genesets){
          
         Df_Chemo_hits_sel = Df_Chemo_hits[grep(geneset, names(Df_Chemo_hits))]
         Df_Chemo_hits_sel_filt = list()
         for(k in 1:length(Df_Chemo_hits_sel)){
             
             Df = Df_Chemo_hits_sel[[k]]
             Dfn = Df %>% dplyr::select(gene, padj)
             colnames(Dfn) = c('gene', names(Df_Chemo_hits_sel)[k])
             Df_Chemo_hits_sel_filt[[k]] = Dfn
         }
         
                               
         Df_Chemo_M = purrr::reduce(Df_Chemo_hits_sel_filt, full_join, by = 'gene' )
         Df_Chemo_M[is.na(Df_Chemo_M)] = 1
         Df_Chemo_M = Df_Chemo_M %>% column_to_rownames('gene')
         Df_Chemo_M_filt = Df_Chemo_M[rowSums(Df_Chemo_M < 0.2) !=0,]
         
         Df_Chemo_M_sign = matrix("", ncol = ncol(Df_Chemo_M_filt), nrow = nrow(Df_Chemo_M_filt)) 
         Df_Chemo_M_sign[Df_Chemo_M_filt <0.2 & Df_Chemo_M_filt > 0.05] = '*'
         Df_Chemo_M_sign[Df_Chemo_M_filt <= 0.05 & Df_Chemo_M_filt > 0.005] = '**'
         Df_Chemo_M_sign[Df_Chemo_M_filt <=0.005] = '***'
         
         colnames(Df_Chemo_M_sign) = colnames(Df_Chemo_M_filt)
         rownames(Df_Chemo_M_sign) = rownames(Df_Chemo_M_filt)
         Df_Chemo_M_log = -log10(Df_Chemo_M_filt)
         MaxNum = max(Df_Chemo_M_log[Df_Chemo_M_log != Inf])
         Df_Chemo_M_log[Df_Chemo_M_log == Inf] = MaxNum +10
         
         Heatmap_matrices[[geneset]] = list('Matrix' = Df_Chemo_M_log, Sign_display = Df_Chemo_M_sign)
         

      
      }    
        
        res <- lapply(names(Heatmap_matrices), function(name) {
   knitr::knit_child(file.path(params$DirPipeline, "Child_Chemoproteomics_heatmap.Rmd"),
                    envir = environment(),
                    quiet = TRUE,
                    options = list(
                      cache = FALSE
                    )
   )
  })

         cat(unlist(res), sep="\n")
         
}else{
    
    cat("No data available")
    
    
}






```


# Concordance chemoproteomics and transcriptomics

```{r Concordance,  eval=TRUE, echo=FALSE, message=FALSE, warning=FALSE, results="asis"}
library(openxlsx)

# Enrichment of all chemoproteomic targets for a given molecule

Mols = unique(ConComp_tabl$Treatment)
Celllines = unique(ConComp_tabl$Cell_line)
genesets = list('Hallmark' = Hallmark, 'Kegg' = Kegg, 'Reactome' = Reactome)


# Enrichment of chemoproteomics

for(mol in Mols){

  Enrichment_chemo_path = file.path(Integration_Folder_Chemo,paste('Chemo_Enrichment_All',mol, ".RDS",sep = '_'))
  if(file.exists(Enrichment_chemo_path)){    
    
    enrichedChemo = readRDS(Enrichment_chemo_path)
  }else{
        enrichedChemo = list()
     
        Target_list_mol = Target_list %>% dplyr::filter(drugs == mol) %>% pull(gene)
    
        for(geneset in names(genesets)){
    
             try(res_enrich <- enricher(Target_list_mol, TERM2GENE = genesets[[geneset]], pvalueCutoff = 1) )
             enrichedChemo_t = res_enrich@result
             enrichedChemo[[paste("Chemo", mol,geneset,sep = '_')]] = enrichedChemo_t
     
        }    
        saveRDS(enrichedChemo, file = Enrichment_chemo_path)
  }
}    
    
```

```{r Concordance_matrices,  eval=TRUE, echo=FALSE, message=FALSE, warning=FALSE, results="asis"}
library(openxlsx)

Heatmap_Conconrd_mats = list()

for(geneset in names(genesets)){
    
    # Prepare matrix from TX enrichment  
    GseaTablesDisplay_all_sel = GseaTablesDisplay_all[grep(geneset, names(GseaTablesDisplay_all))]
    Matrix_padj = lapply(GseaTablesDisplay_all_sel, function(x){x %>% dplyr::select(ID,p.adjust)})
    Matrix_padj_mod = list()
    # Rename the columns of data frames within the lists
    for(k in 1:length(Matrix_padj)){
             
             Df = Matrix_padj[[k]]
             name_t = paste(str_split(names(Matrix_padj)[k], '_')[[1]][1:(length(str_split(names(Matrix_padj)[k], '_')[[1]])-1)], collapse = '_')
             colnames(Df) = c('ID', name_t)
             Matrix_padj_mod[[k]] = Df
    }
         
                               
    
    # Prepare matrix from Chemoproteomics enrichment  
    enrichedChemo_sel = enrichedChemo[grep(geneset, names(enrichedChemo))]
    Matrix_Chemo_pathways = lapply(enrichedChemo_sel, function(x){x %>% dplyr::select(ID,p.adjust)})
    Matrix_Chemo_pathways_mod = list()
    
    for(l in 1:length(Matrix_Chemo_pathways)){
             
             Df = Matrix_Chemo_pathways[[l]]
             colnames(Df) = c('ID', names(Matrix_Chemo_pathways)[l])
             Matrix_Chemo_pathways_mod[[l]] = Df
    }
    # Join Chemotproteomics and TX enriched pathways     
    
    Matrix_padj_all = c(Matrix_Chemo_pathways_mod,Matrix_padj_mod )
    Matrix_padj_all_Join = purrr::reduce(Matrix_padj_all, full_join, by = 'ID' )
    Matrix_padj_all_Join[is.na(Matrix_padj_all_Join)] = 1
    Matrix_padj_all_Join = Matrix_padj_all_Join %>% column_to_rownames('ID')
    Matrix_padj_all_Join_filt = Matrix_padj_all_Join[rowSums(Matrix_padj_all_Join < 0.2) !=0,]
    
    # Matrix with significance stars
    Matrix_padj_all_sign = matrix("", ncol = ncol(Matrix_padj_all_Join_filt ), nrow = nrow( Matrix_padj_all_Join_filt)) 
    Matrix_padj_all_sign[Matrix_padj_all_Join_filt <0.2 & Matrix_padj_all_Join_filt > 0.05] = '*'
    Matrix_padj_all_sign[Matrix_padj_all_Join_filt <= 0.05 & Matrix_padj_all_Join_filt > 0.005] = '**'
    Matrix_padj_all_sign[Matrix_padj_all_Join_filt <= 0.005 ] = '***'
    colnames(Matrix_padj_all_sign) = colnames(Matrix_padj_all_Join_filt)
    rownames(Matrix_padj_all_sign) = rownames(Matrix_padj_all_Join_filt)
    Matrix_padj_all_Join_log = -log10(Matrix_padj_all_Join_filt)
    Heatmap_Conconrd_mats[[geneset]] = list('Matrix' = Matrix_padj_all_Join_log, "Matrix_signif" = Matrix_padj_all_sign)
    
}    

 

```


## Using all chemoproteomics targets associated to the molecule {.tabset}
```{r, echo=FALSE, results='asis', fig.show='hide', eval = TRUE}
library(pheatmap)

genesets = c('Hallmark', 'Kegg', 'Reactome')


res_concord <- lapply(names(Heatmap_Conconrd_mats), function(name) {
knitr::knit_child(file.path(params$DirPipeline, "Child_Chemoproteomics_Concord_heatmap.Rmd"),
                envir = environment(),
                quiet = TRUE,
                options = list(
                  cache = FALSE
                )
)
})

         
cat(unlist(res_concord), sep="\n")


```



