---
title: "TRANSCRIPTOMICS ANALYSIS: `r params$Cellline`"
date: "`r Sys.Date()`"
output:
 html_document:
    toc: true
    toc_depth: 4
    keep_md: true
    toc_float: true
params:
  Dir_Output: "/fsx/home/crivera/BULK-TRANSCRIPTOMICS/Cell_line_Experiments/A_2024_0058/240405_Results_HBEC5i" 
  DirDataForPipeline: "/fsx/home/crivera/BULK-TRANSCRIPTOMICS/Transcriptomics_Pipeline/data/Data_for_pipeline" 
  outliers_path: ""
  Cellline: "HBEC-5i"
  QCNORM: "PRE_QCNORM"
  DEG_url_path: "/fsx/home/crivera/BULK-TRANSCRIPTOMICS/Cell_line_Experiments/A_2024_0058/Data/DEG_url.xlsx"
  Check_Stim_Gene_path: "/fsx/home/crivera/BULK-TRANSCRIPTOMICS/Cell_line_Experiments/A_2024_0058/Data/Check_Stim_Genes.xlsx"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Experimental design
# QC-prenormalization{.tabset}

The following QC plots were made before any type of normalization. They use the count matrix from the "unique_counts" file.

```{r QC_PRENORM,echo=FALSE, warning = FALSE,message=FALSE,  results = "asis"}


# #Path_Dir = "/fsx/home/crivera/Novogene/usftp21.novogene.com_Exp5/Results_Ramos/Summary_Plots_Nfcore"
Path_Dir = params$Dir_Output
cat('\n')
cat("##","By treatment")
cat('\n')

PreNorm_file = "QC_Prenorm_LogGenesVsLogReads.png"
Path_PreNorm = paste(Path_Dir,'QC_PRENORMALIZATION',PreNorm_file, sep = "/")
knitr::opts_chunk$set(fig_width=15, fig_height=7)
knitr::include_graphics(Path_PreNorm)
cat('\n')

cat('\n')
cat("##","By replicate")
cat('\n')

PreNorm_file = "QC_Prenorm_LogGenesVsLogReads_V2.png"
Path_PreNorm = paste(Path_Dir,'QC_PRENORMALIZATION',PreNorm_file, sep = "/")
knitr::opts_chunk$set(fig_width=15, fig_height=7)
knitr::include_graphics(Path_PreNorm)
cat('\n')

cat('\n')
cat("##","By RQN")
cat('\n')

PreNorm_file = "QC_Prenorm_LogGenesVsLogReads_V3.png"
Path_PreNorm = paste(Path_Dir,'QC_PRENORMALIZATION',PreNorm_file, sep = "/")
knitr::opts_chunk$set(fig_width=15, fig_height=7)
knitr::include_graphics(Path_PreNorm)
cat('\n')

cat('\n')
cat("##","By treatment (original scale)")
cat('\n')

PreNorm_file = "QC_Prenorm_GenesVsReads.png"
Path_PreNorm = paste(Path_Dir,'QC_PRENORMALIZATION',PreNorm_file, sep = "/")
knitr::opts_chunk$set(fig_width=15, fig_height=7)
knitr::include_graphics(Path_PreNorm)
cat('\n')


```

# {-}

# Outliers from QC-prenormalization

```{r OUtliers, eval = TRUE, echo=FALSE,warning = FALSE,message=FALSE, results = "asis", fig.width=8, fig.height=6}

    
    library(knitr)
    library(ggplot2)
    library(ggpubr)
    library(rstatix)
    library(tidyverse)
    library(readxl)
    

    Path_Dir = params$Dir_Output
    Out_file = "Outliers.xlsx"
    Out_path = paste(Path_Dir,'QC_PRENORMALIZATION',Out_file, sep = "/")
    
    cat("\n")
    outliers_cust = read_excel(Out_path, col_names = TRUE)
    kable(outliers_cust, caption = "Outliers table")
    cat("\n")
    
   
```

# PCA: 

```{r PCA_Coment,echo=FALSE, warning = FALSE,message=FALSE, results = "asis"}
cat("\n")
cat("The following PCAs use the normalized matrix from", params$QCNORM, " folder")
cat("\n")
```



## PCA: All samples{.tabset}


```{r PCA_POSTNORM_ALLSAMPLES,echo=FALSE, warning = FALSE,message=FALSE, results = "asis"}


Path_Dir = params$Dir_Output
# Download Metadata
if(params$QCNORM == "PRE_QCNORM"){ 
    
    Data_file_name = "DESeq_Norm.RData" 
    Folder_Norm = 'DESEQ_NORM'
    Path_Data_file = paste(Path_Dir,'DESEQ_NORM',Data_file_name, sep = "/")
    load(Path_Data_file)
}else if(params$QCNORM == "DESEQ_NORM_QCNORM"){
    
    Data_file_name = "DESeq_Norm.RData" 
    Folder_Norm = 'DESEQ_NORM_QCNORM'
    Path_Data_file = paste(Path_Dir,'DESEQ_NORM_QCNORM',Data_file_name, sep = "/")
    load(Path_Data_file)
    
    
}


cat('\n')
cat("###","By treatment")
cat('\n')

PCA_file1 = "PCA_All_Treatment.jpeg"
Path_PCA1 = paste(Path_Dir,Folder_Norm ,'PCA_PLOTS',PCA_file1, sep = "/")
knitr::opts_chunk$set(fig_width=12, fig_height=15)
cat('\n')
knitr::include_graphics(Path_PCA1)
cat('\n')

cat('\n')
cat("###","By stimulation")
cat('\n')

PCA_file2 = "PCA_All_Stim.jpeg"
Path_PCA2 = paste(Path_Dir,Folder_Norm,'PCA_PLOTS',PCA_file2, sep = "/")
knitr::opts_chunk$set(fig_width=12, fig_height=15)
cat('\n')
knitr::include_graphics(Path_PCA2)
cat('\n')

cat('\n')
cat("###","By RQN")
cat('\n')

PCA_file3 = "PCA_All_RQN.jpeg"
Path_PCA3 = paste(Path_Dir,Folder_Norm ,'PCA_PLOTS',PCA_file3, sep = "/")
knitr::opts_chunk$set(fig_width=12, fig_height=15)
cat('\n')
knitr::include_graphics(Path_PCA3)
cat('\n')

cat('\n')
cat("###","By outliers")
cat('\n')


PCA_file4 = "PCA_All_Outliers.jpeg"
Path_PCA4 = paste(Path_Dir,Folder_Norm ,'PCA_PLOTS',PCA_file4, sep = "/")
knitr::opts_chunk$set(fig_width=12, fig_height=15)
cat('\n')
knitr::include_graphics(Path_PCA4)
cat('\n')



```

## {-}

## PCA: Per time point{.tabset}

```{r PCA_POSTNORM_PERTIME,echo=FALSE, warning = FALSE,message=FALSE, results = "asis"}

Path_Dir = params$Dir_Output
# Download Metadata
if(params$QCNORM == "PRE_QCNORM"){ 
    
    Data_file_name = "DESeq_Norm.RData" 
    Folder_Norm = 'DESEQ_NORM'
    Path_Data_file = paste(Path_Dir,'DESEQ_NORM',Data_file_name, sep = "/")
    load(Path_Data_file)
}else if(params$QCNORM == "DESEQ_NORM_QCNORM"){
    
    Data_file_name = "DESeq_Norm.RData" 
    Folder_Norm = 'DESEQ_NORM_QCNORM'
    Path_Data_file = paste(Path_Dir,'DESEQ_NORM_QCNORM',Data_file_name, sep = "/")
    load(Path_Data_file)
    
    
}


# By time point
Times = unique(Metadata$timeColl)
Time = "4"
for(Time in Times){

    cat('\n')
    cat("###",Time)
    cat('\n')
    
    cat('\n')
    cat("####", "{.tabset}")
    cat('\n')  
            
    cat('\n')
    cat("#####","By treatment")
    cat('\n')
    
    PCA_file1 = paste("PCATime", Time, "Treatment",".jpeg", sep = '_')
    Path_PCA1 = paste(Path_Dir,Folder_Norm ,'PCA_PLOTS',PCA_file1, sep = "/")
    cat('\n')
    writeLines(paste0("![](",Path_PCA1,")"))
    cat('\n')
    
    cat('\n')
    cat("#####","By stimulation")
    cat('\n')

    PCA_file2 = paste("PCATime", Time, "Stim",".jpeg", sep = '_')
    Path_PCA2 = paste(Path_Dir,Folder_Norm ,'PCA_PLOTS',PCA_file2, sep = "/")
    cat('\n')
    writeLines(paste0("![](",Path_PCA2,")"))
    cat('\n')

    cat('\n')
    cat("#####","By RQN")
    cat('\n')

    PCA_file3 = paste("PCATime", Time, "RQN",".jpeg", sep = '_')
    Path_PCA3 = paste(Path_Dir,Folder_Norm ,'PCA_PLOTS',PCA_file3, sep = "/")
    cat('\n')
    writeLines(paste0("![](",Path_PCA3,")"))
    cat('\n')
    

    cat('\n')
    cat("#####","By outliers")
    cat('\n')

    PCA_file4 = paste("PCATime", Time, "Outliers",".jpeg", sep = '_')
    Path_PCA4 = paste(Path_Dir,Folder_Norm ,'PCA_PLOTS',PCA_file4, sep = "/")
    cat('\n')
    writeLines(paste0("![](",Path_PCA4,")"))
    cat('\n')
    

    

            
}

```

## {-}

## PCA: Per time point, per treatment{.tabset}

```{r PCA_POSTNORM_PERTIME_PERTREAT,echo=FALSE, warning = FALSE,message=FALSE, results = "asis"}

Path_Dir = params$Dir_Output
# Download Metadata
if(params$QCNORM == "PRE_QCNORM"){ 
    
    Data_file_name = "DESeq_Norm.RData" 
    Folder_Norm = 'DESEQ_NORM'
    Path_Data_file = paste(Path_Dir,'DESEQ_NORM',Data_file_name, sep = "/")
    load(Path_Data_file)
}else if(params$QCNORM == "DESEQ_NORM_QCNORM"){
    
    Data_file_name = "DESeq_Norm.RData" 
    Folder_Norm = 'DESEQ_NORM_QCNORM'
    Path_Data_file = paste(Path_Dir,'DESEQ_NORM_QCNORM',Data_file_name, sep = "/")
    load(Path_Data_file)
    
    
}


# By time point
Times = unique(Metadata$timeColl)
Time = "4"
for(Time in Times){

    cat('\n')
    cat("###",Time)
    cat('\n')
    
    Metadata_Time = Metadata %>% filter(timeColl == Time)
    Mols = unique(Metadata_Time$Treatment)
    
    cat('\n')
    cat("####", "{.tabset}")
    cat('\n')  
    
    for(Mol in Mols){
    
        cat('\n')
        cat("#####", Mol)
        cat('\n')  
                
        cat('\n')
        cat("######", "{.tabset}")
        cat('\n')  
        
        
        cat('\n')
        cat("#######","By treatment")
        cat('\n')
        
        PCA_file1 = paste("PCATimeMol", Time,Mol, "Conc",".jpeg", sep = '_')
        Path_PCA1 = paste(Path_Dir,Folder_Norm ,'PCA_PLOTS',PCA_file1, sep = "/")
        cat('\n')
        writeLines(paste0("![](",Path_PCA1,")"))
        cat('\n')
        
        cat('\n')
        cat("#######","By stimulation")
        cat('\n')
    
        PCA_file2 = paste("PCATimeMol", Time,Mol, "Stim",".jpeg", sep = '_')
        Path_PCA2 = paste(Path_Dir,Folder_Norm ,'PCA_PLOTS',PCA_file2, sep = "/")
        cat('\n')
        writeLines(paste0("![](",Path_PCA2,")"))
        cat('\n')
    
        cat('\n')
        cat("#######","By RQN")
        cat('\n')
    
        PCA_file3 = paste("PCATimeMol", Time,Mol, "RQN",".jpeg", sep = '_')
        Path_PCA3 = paste(Path_Dir,Folder_Norm ,'PCA_PLOTS',PCA_file3, sep = "/")
        cat('\n')
        writeLines(paste0("![](",Path_PCA3,")"))
        cat('\n')
        
    
        cat('\n')
        cat("#######","By outliers")
        cat('\n')
    
        PCA_file4 = paste("PCATimeMol", Time,Mol, "Outliers",".jpeg", sep = '_')
        Path_PCA4 = paste(Path_Dir,Folder_Norm ,'PCA_PLOTS',PCA_file4, sep = "/")
        cat('\n')
        writeLines(paste0("![](",Path_PCA4,")"))
        cat('\n')
        
    }
    

            
}

```

## {-}

# QC-Correlation plots

## QC-Correlation plots: All samples{.tabset}

```{r QC_CORRPLOTS,echo=FALSE, warning = FALSE,message=FALSE,  results = "asis",  fig.width=8, fig.height= 2}


Path_Dir = params$Dir_Output
# Download Metadata
if(params$QCNORM == "PRE_QCNORM"){ 
    
    Data_file_name = "DESeq_Norm.RData" 
    Folder_Norm = 'DESEQ_NORM'
    Path_Data_file = paste(Path_Dir,'DESEQ_NORM',Data_file_name, sep = "/")
    load(Path_Data_file)
}else if(params$QCNORM == "DESEQ_NORM_QCNORM"){
    
    Data_file_name = "DESeq_Norm.RData" 
    Folder_Norm = 'DESEQ_NORM_QCNORM'
    Path_Data_file = paste(Path_Dir,'DESEQ_NORM_QCNORM',Data_file_name, sep = "/")
    load(Path_Data_file)
    
    
}


cat('\n')
cat("###","Spearman")
cat('\n')

Corr_file1 = "CorrSp_All.jpeg"
Path_Corr1 = paste(Path_Dir,Folder_Norm ,'PCA_PLOTS',Corr_file1, sep = "/")
knitr::opts_chunk$set(fig_width=12, fig_height=15)
cat('\n')
knitr::include_graphics(Path_Corr1)
cat('\n')

cat('\n')
cat("###","Pearson")
cat('\n')

Corr_file2 = "CorrPr_All.jpeg"
Path_Corr2 = paste(Path_Dir,Folder_Norm ,'PCA_PLOTS',Corr_file2, sep = "/")
knitr::opts_chunk$set(fig_width=12, fig_height=15)
cat('\n')
knitr::include_graphics(Path_Corr2)
cat('\n')

cat('\n')
cat("###","Scatter plots")
cat('\n')

cat("The first three samples in this scatter plot have been selected randomly and the last three belong to the outlier sample set proposed in the QC-prenormalization section")

Corr_file3 = "PairSp_RandSam.jpeg"
Path_Corr3 = paste(Path_Dir,Folder_Norm ,'PCA_PLOTS',Corr_file3, sep = "/")
knitr::opts_chunk$set(fig_width=12, fig_height=15)
cat('\n')
knitr::include_graphics(Path_Corr3)
cat('\n')



```

## {-}

## QC-Correlation plots: per time point{.tabset}

```{r QC_CORRPLOTS_TIME,echo=FALSE, warning = FALSE,message=FALSE,  results = "asis",  fig.width=8, fig.height= 2}


Path_Dir = params$Dir_Output
# Download Metadata
if(params$QCNORM == "PRE_QCNORM"){ 
    
    Data_file_name = "DESeq_Norm.RData" 
    Folder_Norm = 'DESEQ_NORM'
    Path_Data_file = paste(Path_Dir,'DESEQ_NORM',Data_file_name, sep = "/")
    load(Path_Data_file)
}else if(params$QCNORM == "DESEQ_NORM_QCNORM"){
    
    Data_file_name = "DESeq_Norm.RData" 
    Folder_Norm = 'DESEQ_NORM_QCNORM'
    Path_Data_file = paste(Path_Dir,'DESEQ_NORM_QCNORM',Data_file_name, sep = "/")
    load(Path_Data_file)
    
    
}

# By time point
Times = unique(Metadata$timeColl)

for(Time in Times){

    cat('\n')
    cat("###",Time)
    cat('\n')
    
    cat('\n')
    cat("####", "{.tabset}")
    cat('\n')  
            
    cat('\n')
    cat("#####","Spearman")
    cat('\n')
    
    CorrT_file1 = paste("CorrSpTime", Time,".jpeg", sep = '_')
    Path_CorrT1 = paste(Path_Dir,Folder_Norm ,'PCA_PLOTS',CorrT_file1, sep = "/")
    cat('\n')
    writeLines(paste0("![](",Path_CorrT1,")"))
    cat('\n')
    
    cat('\n')
    cat("#####","Pearson")
    cat('\n')

    CorrT_file2 = paste("CorrPrTime", Time,".jpeg", sep = '_')
    Path_CorrT2 = paste(Path_Dir,Folder_Norm ,'PCA_PLOTS',CorrT_file2, sep = "/")
    cat('\n')
    writeLines(paste0("![](",Path_CorrT2,")"))
    cat('\n')

    

            
}


```

## {-}


# QC-Correlation within replicates

In the following plot each dot represents the Spearman correlation between replicates for every condition in the data set.

```{r QC_CORR,echo=FALSE, warning = FALSE,message=FALSE,  results = "asis",  fig.width=8, fig.height= 2}


# #Path_Dir = "/fsx/home/crivera/Novogene/usftp21.novogene.com_Exp5/Results_Ramos/Summary_Plots_Nfcore"
Path_Dir = params$Dir_Output
Corr_file1 = "Correlation_within_replicates.png"
Path_Corr1 = paste(Path_Dir,'QC_POSTNORMALIZATION',Corr_file1, sep = "/")
knitr::opts_chunk$set(fig_width=15, fig_height=7)
knitr::include_graphics(Path_Corr1)


```





# DEG per time per dose: gene plots {.tabset}


```{r DEGLink, eval = TRUE,echo=FALSE,warning = FALSE,message=FALSE, results = "asis", fig.width=8, fig.height=6}

    
    library(knitr)
    library(glue)
    cat('This section finds results from comparisons made per time point, per dose, between a given condition and its respective control')  
    cat('\n')
    cat("Please find summary table containing differentially expressed genes for every selected comparison in the following link. Filter for padj < 0.2
")
    cat('\n')
    if(file.exists(params$DEG_url_path )){
       
        DEG_urls = read_excel(params$DEG_url_path, col_names = TRUE, sheet = params$Cellline)
        DEG_per_comp = DEG_urls %>% filter(url_name == 'DEG_per_comp')
        DEG_per_comp = DEG_per_comp$url
        cat("\n")
        DEG_link_name = "DEG all comparisons"
        
        output <- glue("[{DEG_link_name}]({DEG_per_comp})")
        knitr::knit_print(output)
   }else{
       
    print("Path to DEG url does not exist")
   }
   
   
```



```{r GenesPerTimePerDose, eval = TRUE,echo=FALSE,warning = FALSE,message=FALSE, results = "asis", fig.width=8, fig.height=6}

    
    library(knitr)
    library(ggplot2)
    library(ggpubr)
    library(rstatix)
    library(tidyverse)
    library(ggpubr)
    library(openxlsx)
    library(org.Hs.eg.db)
    library(DESeq2)
    library(BiocParallel)
    library(parallel)
    library(pheatmap)


    cat("The following heatmaps display the most significant (40 at most) DEG for each comparison (padj < 0.2). We use the normalized matrix from", params$QCNORM, " folder. The displayed values have been z-scored for each gene, so that differences between conditions can be visually identified by eye.")
    
    cat("\n")
    
    # Function to add description and gene plots of regulated genes in a pathway
    Gene_Expr_plot_dose = function(NormMatrix,Metadata_Cond, GeneList){

        
        NormMatrix_filt = as.data.frame(NormMatrix[GeneList,])
        NormMatrix_filt$Gene = rownames(NormMatrix_filt)
        NormMatrix_Long = NormMatrix_filt %>% pivot_longer(!Gene, names_to = "Sample_name", values_to = "Norm_Expr") %>% as.data.frame()
        NormMatrix_Long$Gene = factor(NormMatrix_Long$Gene)
        NormMatrix_Long$dose = Metadata_Cond$dose[match(NormMatrix_Long$Sample_name, Metadata_Cond$Sample_name)]
        NormMatrix_Long$Stim =Metadata_Cond$Stimulant_used[match(NormMatrix_Long$Sample_name, Metadata_Cond$Sample_name)]
        #NormMatrix_Long$Sample_name = NULL

        # Add very little noise to avoid T-test to complain
        #NormMatrix_Long$Norm_Expr = NormMatrix_Long$Norm_Expr + rnorm(nrow(NormMatrix_Long),mean = 0,sd = 1e-7)

        # Generate pvalues.  step.increase = 0.06 seems to control of the pvalue test in the y axis.
        #stat.test <- NormMatrix_Long %>% group_by(Gene, time) %>% t_test(Norm_Expr ~ Treatment, ref.group = ControlName)%>%add_significance()
        #stat.test <- stat.test %>% add_xy_position(x = "time", dodge = 0.5, step.increase = 0.06)
        #%>% rstatix::t_test(Norm_Expr ~ Treatment, ref.group = "Vehicle")
        # Plot
        bxp <- ggboxplot(NormMatrix_Long, x = "dose", y = "Norm_Expr", palette = "jco",
                         facet.by = "Gene", scales = "free", add = "dotplot")
            #stat_pvalue_manual(stat.test, label = "p.signif", size = 3)+
            #scale_y_continuous(expand = expansion(mult = c(0.01, 0.2)))

        # png(filename=paste('Genes', NameRefUniq, '.png',sep = '_'), width = 1200, height = 800, res= 100)
        # print(bxp)
        # dev.off()

        # Add gene data frame with description

        # Gene_info_temp = Df_mol_filt %>% filter(entrez %in% gids) %>% dplyr::select("log2FoldChange", "pvalue", "padj", "genes", "entrez")
        # 
        # # Gene description data frame
        # Description = c()
        # for(gene in Gene_info_temp$genes){
        # 
        #     for(i in 1:nrow(GeneDescription)){
        # 
        #         if(gene %in% GeneDescription$Gene.Names_mod[i][[1]]){
        #             Description[gene] = GeneDescription$LongDesc[i]
        # 
        #             break
        #         }
        # 
        #     }
        # }
        # 
        # Gene_info_temp$Description = Description[match(Gene_info_temp$genes, names(Description))]
        # DiffGenesPwaysDf = list()
        # DiffGenesPwaysDf[[paste('Genes', NameRefUniq,sep = '_')]] = Gene_info_temp
        # DiffGenesPwaysDf[['Names']] = paste('Genes', NameRefUniq,sep = '_')

        return(bxp)



    }
    Path_Dir = params$Dir_Output
    if(params$QCNORM == "PRE_QCNORM"){ 
    
    Data_file_name = "DESeq_Norm.RData" 
    Folder_Norm = 'DESEQ_NORM'
    Path_Data_file = paste(Path_Dir,'DESEQ_NORM',Data_file_name, sep = "/")
    load(Path_Data_file)
}else if(params$QCNORM == "DESEQ_NORM_QCNORM"){
    
    Data_file_name = "DESeq_Norm.RData" 
    Folder_Norm = 'DESEQ_NORM_QCNORM'
    Path_Data_file = paste(Path_Dir,'DESEQ_NORM_QCNORM',Data_file_name, sep = "/")
    load(Path_Data_file)
    
    
}
    # Import data
    # Path_Dir = params$Dir_Output
    # Data_file_name = "DESeq_Norm.RData" 
    # Path_Data_file = paste(Path_Dir,'DESEQ_NORM_QCNORM',Data_file_name, sep = "/")
    # load(Path_Data_file)
    # 
    # Out_file = "Outliers.xlsx"
    # Out_path = paste(Path_Dir,'QC_PRENORMALIZATION',Out_file, sep = "/")
    # outliers_cust = read.xlsx(Out_path, colNames = FALSE)

   
    # Split per time point
    
    # DESeq normalization
    #Create coarse Condition feature and useful Metadata
    ControlRef = 'DMSO'
    
    MOLEC = unique(Metadata$Treatment)
    #MOLEC = MOLEC[!MOLEC %in% c('DMSO', 'NONE')]
    
    for(mol in MOLEC){
        
        Data_file_name2 = paste("DEG", mol, ".RData", sep = '_')
        Path_Data_file2 = paste(Path_Dir,'DEG_FUNCTION',mol, Data_file_name2, sep = "/")
        load(Path_Data_file2)
        
        MapDf = data.frame(NamesDiff = names(DiffGenes))
        MapDf$Mol = sapply(MapDf$NamesDiff, function(x){str_split(x, '_')[[1]][1]})
        MapDf$Dose = sapply(MapDf$NamesDiff, function(x){str_split(x, '_')[[1]][2]})
        MapDf$Time = sapply(MapDf$NamesDiff, function(x){str_split(x, '_')[[1]][3]})
        MapDf$Stim = sapply(MapDf$NamesDiff, function(x){str_split(x, '_')[[1]][4]})
        
        
        cat('\n')
        cat("##",mol)
        cat('\n')  
        
        cat('\n')
        cat("###", "{.tabset}")
        cat('\n')  
        
        for(time in unique(MapDf$Time)){
            
            
            cat('\n')
            cat("####", time)
            cat('\n')  
            
            MapDf_time = MapDf %>% filter(Time == time)
            
            DiffGenes_time = DiffGenes[MapDf_time$NamesDiff]
            
            cat('\n')
            cat("#####", "{.tabset}")
            cat('\n')  
            
            
            for(stim in unique(MapDf_time$Stim)){
                
                cat('\n')
                cat("######", stim)
                cat('\n')  
                
                MapDf_time_stim = MapDf_time %>% filter(Stim == stim)
                DiffGenes_time_stim = DiffGenes_time[MapDf_time_stim$NamesDiff]
                
                cat('\n')
                cat("#######", "{.tabset}")
                cat('\n') 
                
                MapDf_time_stim = MapDf_time_stim[order(as.numeric(MapDf_time_stim$Dose)),]
                
                for(dose in unique(MapDf_time_stim$Dose)){
                    
                    cat('\n')
                    cat("########", dose)
                    cat('\n')  
                    
                    MapDf_time_stim_dose = MapDf_time_stim %>% filter(Dose == dose)
                    DiffGenes_time_stim_dose = DiffGenes_time_stim[MapDf_time_stim_dose$NamesDiff][[1]] %>% filter(padj < 0.2)
                    DiffGenes_time_stim_dose = DiffGenes_time_stim_dose[order(DiffGenes_time_stim_dose$padj, decreasing = FALSE),]
                    
                    if(nrow(DiffGenes_time_stim_dose) >= 1){
                       
                        # Select samples
                        if(mol %in% c('DMSO', 'NONE')){
                            
                            Metadata_comp = Metadata %>% filter(Treatment == mol & timeColl == time & Stimulant_used %in% c(stim, 'NONE') & Treatment_conc_uM == dose)
                            Metadata_comp = Metadata_comp[order(Metadata_comp$Stimulant_used), ]
                            annotation_col = Metadata_comp %>% dplyr::select(Stimulant_used)
                            rownames(annotation_col) = Metadata_comp$Sample_name
                            
                        }else{    
                            Metadata_comp = Metadata %>% filter(Treatment %in% c(mol, ControlRef) & timeColl == time & Stimulant_used == stim & Treatment_conc_uM %in% c(dose, '0'))
                            Metadata_comp = Metadata_comp[order(Metadata_comp$Treatment_conc_uM), ]
                            annotation_col = Metadata_comp %>% dplyr::select(Treatment)
                            rownames(annotation_col) = Metadata_comp$Sample_name
                        }
                            
                        
                        NormCounts_comp = NormCounts[match(DiffGenes_time_stim_dose$genes, rownames(NormCounts)), match(Metadata_comp$Sample_name, colnames(NormCounts)),drop=FALSE]
                        NormCounts_comp = NormCounts_comp[1:min(40,nrow(DiffGenes_time_stim_dose)),, drop=FALSE]
                        # Calculate z score of this matrix to be able to plot the heatmap
                        NormCounts_comp_zscore = t(sapply(as.data.frame(t(NormCounts_comp)), function(x) {(x-mean(x))/sd(x)}))
                        colnames(NormCounts_comp_zscore) = colnames(NormCounts_comp)
                        
        
                
                        P = pheatmap(as.matrix(NormCounts_comp_zscore), cluster_cols=FALSE, cluster_rows=FALSE, annotation_col = annotation_col, fontsize_row = 6, fontsize_col = 8, angle_col = 270)
                
                        print(P)
                
                        cat('\n')
                        rm(NormCounts_comp_zscore, annotation_col, Metadata_comp, NormCounts_comp)
                    }else{
                        cat('\n')
                        cat("No DEG for this condition")
                        cat('\n')
                    }
                }
                
                
                
            }
            
            
        }
        
        
        
        
        
        
    }
    
    
    
   
```

# {-}




# DEG per time point per dose: Summary{.tabset}


```{r GeneSummary, eval = TRUE, echo=FALSE,warning = FALSE,message=FALSE, results = "asis", fig.width=8, fig.height=6}

    
    library(knitr)
    library(ggplot2)
    library(ggpubr)
    library(rstatix)
    library(tidyverse)
    
    cat('\n')
    cat("Summary per time point, per dose, showing number of DEG (at padj < 0.2) for each comparison")
    cat('\n')
    
    Path_Dir = params$Dir_Output
    DEGSum_file1 = "Summary_Plot_DEG.RData"
    Path_DEGSum = paste(Path_Dir,'PWAYS_INTEGRATION',DEGSum_file1, sep = "/")
    load(Path_DEGSum)
    
    DEG_summ$dose = factor(DEG_summ$dose, levels = c('0','1','2.5', '6.25', '15.6' ))
    
    Mols = unique(DEG_summ$Mol)
    
    for(mol in Mols){
        
        cat('\n')
        cat("##",mol)
        cat('\n')  
        
        DEG_summ_mol = DEG_summ %>% filter(Mol == mol)
        print(nrow(DEG_summ_mol))
        
        P = ggplot(DEG_summ_mol, aes (x = time, y = n_diff, fill = dose)) +
                   geom_bar(stat="identity", position=position_dodge())+facet_wrap(~stim, ncol =1)
        
        print(P)   
        cat('\n')  
   }
    
   
```


# {-}

# Revise expected gene behavior from stimulations{.tabset}


```{r CheckStim, eval = TRUE, echo=FALSE,warning = FALSE,message=FALSE, results = "asis", fig.width=8, fig.height=6}

    
    library(knitr)
    library(ggplot2)
    library(ggpubr)
    library(rstatix)
    library(tidyverse)
    library(readxl)
    
   cat("The following heatmaps display a customized set of genes that should be regulated by a particular stimulation. We used the normalized matrix from", params$QCNORM, " folder. The display values have been z-scored for each gene, so that differences between conditions can be visually identified by eye.")
    
    cat("\n")

    # Download genes to check
    if(file.exists(params$Check_Stim_Gene_path)){
        Check_Genes = read_excel(params$Check_Stim_Gene_path, col_names = FALSE, sheet = params$Cellline)
        Check_Genes = Check_Genes[[1]]
        
        # Download normalized data frame
        if(params$QCNORM == "PRE_QCNORM"){ 
        
        Data_file_name = "DESeq_Norm.RData" 
        Folder_Norm = 'DESEQ_NORM'
        Path_Data_file = paste(Path_Dir,'DESEQ_NORM',Data_file_name, sep = "/")
        load(Path_Data_file)
        }else if(params$QCNORM == "DESEQ_NORM_QCNORM"){
        
        Data_file_name = "DESeq_Norm.RData" 
        Folder_Norm = 'DESEQ_NORM_QCNORM'
        Path_Data_file = paste(Path_Dir,'DESEQ_NORM_QCNORM',Data_file_name, sep = "/")
        load(Path_Data_file)
        
        
        }
        
        Controls = c('DMSO', 'NONE')
        
        Times = unique(Metadata$timeColl)
        
        for(Time in Times){
            
            Metadata_Time = Metadata %>% filter(timeColl == Time)
            Stims = unique(Metadata$Stimulant_used)
            
            cat('\n')
            cat("##", Time)
            cat('\n') 
            
            cat('\n')
            cat("###", "{.tabset}")
            cat('\n')  
            
            for(mol in Controls){
                
                
                cat('\n')
                cat("####", mol)
                cat('\n') 
                
                Metadata_Time_mol = Metadata_Time %>% filter(Treatment == mol)
                Metadata_Time_mol = Metadata_Time_mol[order( Metadata_Time_mol$Stimulant_used),]
                Check_Genes_fil = Check_Genes[Check_Genes %in% rownames(NormCounts)]
                NormCounts_Time_mol = NormCounts[match(Check_Genes_fil, rownames(NormCounts)),match(Metadata_Time_mol$Sample_name, colnames(NormCounts))]
                
                # Plot heatmap
                
                annotation_col = Metadata_Time_mol %>% dplyr::select(Stimulant_used)
                rownames(annotation_col) = Metadata_Time_mol$Sample_name
                
                NormCounts_Time_mol_zscore = t(sapply(as.data.frame(t(NormCounts_Time_mol)), function(x) {(x-mean(x))/sd(x)}))
                colnames(NormCounts_Time_mol_zscore) = colnames(NormCounts_Time_mol)
                
                P = pheatmap(as.matrix(NormCounts_Time_mol_zscore), cluster_cols=FALSE, cluster_rows=FALSE, annotation_col = annotation_col, fontsize_row = 6, fontsize_col = 8, angle_col = 270)
                
                print(P)
                cat('\n')
            }
            
            
        }
        

    }else{
        
        cat("Path to customize list of genes does not exists")
    }
   
```


# {-}




# GSEA on comparisons per time per dose {.tabset}


```{r GSEAPerTimePerDose, eval = TRUE,echo=FALSE,warning = FALSE,message=FALSE, results = "asis", fig.width=8, fig.height=6}

    
    library(knitr)
    library(ggplot2)
    library(ggpubr)
    library(rstatix)
    library(tidyverse)
    library(ggpubr)
    library(openxlsx)
    library(org.Hs.eg.db)
    library(DESeq2)
    library(BiocParallel)
    library(parallel)
    library(pheatmap)
    library(fgsea)
    
    cat("\n")
    cat(" We use GSEA enrichment on the quantity: sign(LogFold)x(-log10(pvalue)). We display the head of the enriched data frame generated using padj < 0.2")
    cat("\n")
    # Function for finding gsea enrich pathways 
    Enrich_gsea = function(gene_list, Gmt_file, pvalue) {
            set.seed(54321)
            library(dplyr)
            library(fgsea)
            
            
            if  ( !all( order(gene_list, decreasing = TRUE) == 1:length(gene_list)) ){
            warning("We had to sort genes")
            gene_list = sort(gene_list, decreasing = TRUE)
            }
            myGS = fgsea::gmtPathways(Gmt_file)

            gsea_Res <- fgsea::fgsea(pathways = myGS,
                                   stats = gene_list,
                                   minSize=10, ## minimum size of gene set 
                                   maxSize=400, ## maximum size of gene set 
                                   nperm=10000) %>% 
                          as.data.frame() %>% 
                          dplyr::filter(padj < !! pvalue) %>% 
                          arrange(desc(NES))
            message(paste("Number of enriched pathways =", nrow(gsea_Res)))
            
            # Collapse pathways 
            concise_pathways = collapsePathways(data.table::as.data.table(gsea_Res),
                                              pathways = myGS,
                                              stats = gene_list)
            gsea_Res = gsea_Res[gsea_Res$pathway %in% concise_pathways$mainPathways, ]
            message(paste("Number of enriched pathways after collapse =", nrow(gsea_Res)))
            
            gsea_Res$Enrichment = ifelse(gsea_Res$NES > 0, "Up regulated", "Down regulated")
            filtRes = rbind(head(gsea_Res, n = 10),
                          tail(gsea_Res, n = 10 ))
            
            total_up = sum(gsea_Res$Enrichment == "Up regulated")
            total_down = sum(gsea_Res$Enrichment == "Down regulated")
            header = paste0("Top 10: Up=", total_up,", Down=",    total_down, ")")
            
            colos = setNames(c("firebrick2", "dodgerblue2"),
                         c("Up regulated", "Down regulated"))
            
            g1= ggplot(filtRes, aes(reorder(pathway, NES), NES)) +
            geom_point( aes(fill = Enrichment, size = size), shape=21) +
            scale_fill_manual(values = colos ) +
            scale_size_continuous(range = c(2,10)) +
            geom_hline(yintercept = 0) +
            coord_flip() +
            labs(x="Pathway", y="Normalized Enrichment Score",
               title=header)
            
            output = list("Results" = gsea_Res, "Plot" = g1)
            return(output)
}
    
    # Import data
    Path_Dir_pipe = params$DirDataForPipeline
    Path_Dir = params$Dir_Output
    Data_file_name = "h.all.v2023.2.Hs.symbols.gmt" 
    Path_gmt = paste(Path_Dir_pipe,Data_file_name, sep = "/")
    
    
    # GSEA per Time per dose
    
    ControlRef = 'DMSO'
    
    MOLEC = unique(Metadata$Treatment)
    #MOLEC = MOLEC[!MOLEC %in% c('DMSO', 'NONE')]
    
    for(mol in MOLEC){
        Data_file_name2 = paste("DEG", mol, ".RData", sep = '_')
        Path_Data_file2 = paste(Path_Dir,'DEG_FUNCTION',mol, Data_file_name2, sep = "/")
        load(Path_Data_file2)
        
        MapDf = data.frame(NamesDiff = names(DiffGenes))
        MapDf$Mol = sapply(MapDf$NamesDiff, function(x){str_split(x, '_')[[1]][1]})
        MapDf$Dose = sapply(MapDf$NamesDiff, function(x){str_split(x, '_')[[1]][2]})
        MapDf$Time = sapply(MapDf$NamesDiff, function(x){str_split(x, '_')[[1]][3]})
        MapDf$Stim = sapply(MapDf$NamesDiff, function(x){str_split(x, '_')[[1]][4]})
        
        
        cat('\n')
        cat("##",mol)
        cat('\n')  
        
        cat('\n')
        cat("###", "{.tabset}")
        cat('\n')  
        
        for(time in unique(MapDf$Time)){
            
            
            cat('\n')
            cat("####", time)
            cat('\n')  
            
            MapDf_time = MapDf %>% filter(Time == time)
            
            DiffGenes_time = DiffGenes[MapDf_time$NamesDiff]
            
            cat('\n')
            cat("#####", "{.tabset}")
            cat('\n')  
            
            
            for(stim in unique(MapDf_time$Stim)){
                
                cat('\n')
                cat("######", stim)
                cat('\n')  
                
                MapDf_time_stim = MapDf_time %>% filter(Stim == stim)
                DiffGenes_time_stim = DiffGenes_time[MapDf_time_stim$NamesDiff]
                
                cat('\n')
                cat("#######","Concentration", "{.tabset}")
                cat('\n') 
                
                MapDf_time_stim = MapDf_time_stim[order(as.numeric(MapDf_time_stim$Dose)),]
                
                for(dose in unique(MapDf_time_stim$Dose)){
                    
                    cat('\n')
                    cat("########", dose)
                    cat('\n')  
                    
                    MapDf_time_stim_dose = MapDf_time_stim %>% filter(Dose == dose)
                    DiffGenes_time_stim_dose = DiffGenes_time_stim[MapDf_time_stim_dose$NamesDiff][[1]] 
                    DiffGenes_time_stim_dose$gsea_in = sign(DiffGenes_time_stim_dose$log2FoldChange) * (-log10(DiffGenes_time_stim_dose$pvalue))
                    DiffGenes_time_stim_dose = DiffGenes_time_stim_dose[order(DiffGenes_time_stim_dose$gsea_in, decreasing = TRUE),]
                    
                    gene_list  = DiffGenes_time_stim_dose$gsea_in
                    names(gene_list) = rownames(DiffGenes_time_stim_dose)
                    Gmt_file = Path_gmt
                    pval = 0.2
                    
                    Hall_gsea = Enrich_gsea(gene_list, Gmt_file, pval)
                   
                    Res_gsea = Hall_gsea$Results
                    if(nrow( Res_gsea ) > 0){
                        
                        cat('\n')  
                        print(kable(head(Res_gsea %>% dplyr::select(pathway,pval,padj,ES,NES))))
                        cat('\n')  
                        
                        cat('\n')  
                        print(Hall_gsea$Plot)
                        cat('\n')  
                        
                        
                    }else{
                        
                        cat('\n')  
                        cat("No enrich pathways from gsea")
                        cat('\n')  
                    }
                    
                    
                    
                    
                }
                
                
                
            }
            
            
        }
        
        
        
        
        
        
    }
    
    
    
   
```

# {-}



# DEG per time point, dose responding {.tabset}

For a given molecule under a particular stimulation at a given time point, we find genes that are responding to treatment concentration: Gene ~ dose

```{r DEGLinkDose, eval = TRUE,echo=FALSE,warning = FALSE,message=FALSE, results = "asis", fig.width=8, fig.height=6}

    
    library(knitr)
    library(glue)
    cat("\n")
    cat("Please find summary tables containing dose responding genes for every time point and stimulation. Please filter for padj < 0.2 to find the significant genes.
")
    cat("\n")
    if(file.exists(DEG_url_path )){
       
        DEG_urls = read_excel(params$DEG_url_path, col_names = TRUE, sheet = params$Cellline)
        DEG_per_comp = DEG_urls %>% filter(url_name == 'DEG_dose')
        DEG_per_comp = DEG_per_comp$url
        cat("\n")
        DEG_link_name = "DEG dose responding"
        
        output <- glue("[{DEG_link_name}]({DEG_per_comp})")
        knitr::knit_print(output)
    }else{
       
       print("Path to DEG url does not exist")
    }
   
   
```

```{r Genedose, eval = TRUE ,echo=FALSE,warning = FALSE,message=FALSE, results = "asis", fig.width=8, fig.height=6}

    
    library(knitr)
    library(ggplot2)
    library(ggpubr)
    library(rstatix)
    library(tidyverse)
    library(ggpubr)
    library(openxlsx)
    library(org.Hs.eg.db)
    library(DESeq2)
    library(BiocParallel)
    library(parallel)
    library("readxl")


    cat("\n")
    cat("The following dot plots show dose responding genes (first 25 at most) due to treatment for every time point and every stimulation")
    cat("\n")
    # Function to add description and gene plots of regulated genes in a pathway
    Gene_Expr_plot_dose = function(NormMatrix,Metadata_Cond, GeneList){

        
        NormMatrix_filt = as.data.frame(NormMatrix[GeneList,])
        NormMatrix_filt$Gene = rownames(NormMatrix_filt)
        NormMatrix_Long = NormMatrix_filt %>% pivot_longer(!Gene, names_to = "Sample_name", values_to = "Norm_Expr") %>% as.data.frame()
        NormMatrix_Long$Gene = factor(NormMatrix_Long$Gene)
        NormMatrix_Long$dose = Metadata_Cond$dose[match(NormMatrix_Long$Sample_name, Metadata_Cond$Sample_name)]
        NormMatrix_Long$Stim =Metadata_Cond$Stimulant_used[match(NormMatrix_Long$Sample_name, Metadata_Cond$Sample_name)]
        #NormMatrix_Long$Sample_name = NULL

        # Add very little noise to avoid T-test to complain
        #NormMatrix_Long$Norm_Expr = NormMatrix_Long$Norm_Expr + rnorm(nrow(NormMatrix_Long),mean = 0,sd = 1e-7)

        # Generate pvalues.  step.increase = 0.06 seems to control of the pvalue test in the y axis.
        #stat.test <- NormMatrix_Long %>% group_by(Gene, time) %>% t_test(Norm_Expr ~ Treatment, ref.group = ControlName)%>%add_significance()
        #stat.test <- stat.test %>% add_xy_position(x = "time", dodge = 0.5, step.increase = 0.06)
        #%>% rstatix::t_test(Norm_Expr ~ Treatment, ref.group = "Vehicle")
        # Plot
        bxp <- ggboxplot(NormMatrix_Long, x = "dose", y = "Norm_Expr", palette = "jco",
                         facet.by = "Gene", scales = "free", add = "dotplot")
            #stat_pvalue_manual(stat.test, label = "p.signif", size = 3)+
            #scale_y_continuous(expand = expansion(mult = c(0.01, 0.2)))

        # png(filename=paste('Genes', NameRefUniq, '.png',sep = '_'), width = 1200, height = 800, res= 100)
        # print(bxp)
        # dev.off()

        # Add gene data frame with description

        # Gene_info_temp = Df_mol_filt %>% filter(entrez %in% gids) %>% dplyr::select("log2FoldChange", "pvalue", "padj", "genes", "entrez")
        # 
        # # Gene description data frame
        # Description = c()
        # for(gene in Gene_info_temp$genes){
        # 
        #     for(i in 1:nrow(GeneDescription)){
        # 
        #         if(gene %in% GeneDescription$Gene.Names_mod[i][[1]]){
        #             Description[gene] = GeneDescription$LongDesc[i]
        # 
        #             break
        #         }
        # 
        #     }
        # }
        # 
        # Gene_info_temp$Description = Description[match(Gene_info_temp$genes, names(Description))]
        # DiffGenesPwaysDf = list()
        # DiffGenesPwaysDf[[paste('Genes', NameRefUniq,sep = '_')]] = Gene_info_temp
        # DiffGenesPwaysDf[['Names']] = paste('Genes', NameRefUniq,sep = '_')

        return(bxp)



    }

    
    # Import data
    Path_Dir = params$Dir_Output
    Data_file_name = "Prefilter_Data.xlsx" 
    Path_Data_file = paste(Path_Dir,'PRE_FILTERING',Data_file_name, sep = "/")
    
    Count = read.xlsx(xlsxFile = Path_Data_file, sheet = "Count", rowNames= TRUE)
    Metadata = read.xlsx(xlsxFile = Path_Data_file, sheet = "Metadata")

    # Read customize outliers
    if(file.exists(params$outliers_path)){

        outliers_cust <- read.csv(outliers_path, header = FALSE)
        outliers_cust = outliers_cust[[1]]
    }else{

        cat("\n")
        cat("Path to costumized outliers does not exist or is null")
        cat("\n")
        outliers_cust = c()
    }

    
    
    GENE_ENSEM = TRUE
    ORGANISM = 'Human'
    # Convert from ensemble to symbol
    if(GENE_ENSEM == TRUE){
        if(ORGANISM == 'Human'){
        # Convert from Ensemble to rownames
        geneSymbol <- mapIds(org.Hs.eg.db,keys=rownames(Count),column="SYMBOL",keytype="ENSEMBL",multiVals="first")
        Count$genesymbol = geneSymbol[match(rownames(Count), names(geneSymbol))]
        Count = Count[!is.na(Count$genesymbol),]

        Count <- aggregate(. ~ genesymbol, data = Count, FUN = sum)
        rownames(Count) = Count$genesymbol
        Count$genesymbol = NULL
      }
    }

   
    # Split per time point
    
    # DESeq normalization
    #Create coarse Condition feature and useful Metadata
    ControlRef = 'DMSO'
    CoarseCond_ForDose = c('Treatment', 'timeColl', 'Stimulant_used')
    Metadata$Coarse_ForDose = Metadata[[CoarseCond_ForDose[1]]]

    for(j in 2:length(CoarseCond_ForDose)){
        Metadata$Coarse_ForDose = paste(Metadata[["Coarse_ForDose"]],Metadata[[CoarseCond_ForDose[j]]], sep = "_")
    }
    
    
    CondUnique = unique(Metadata$Coarse_ForDose)
    
    Diff_Genes_dose = list()
    DEG_Sum_Dose = data.frame(Mol = as.character(), Time = as.character(), Stim = as.character(), n_diff= numeric())
    for(Cond in CondUnique){
        
        
        
        mol = str_split(Cond, '_')[[1]][1]
        time = str_split(Cond, '_')[[1]][2]
        stim = str_split(Cond, '_')[[1]][3]
        #print(Cond)
         
        if( !mol %in% c(ControlRef, 'NONE', 'M10541')){
           
            cat('\n')
            cat("##",Cond)
            cat('\n')  
            
            ControlCond = paste(ControlRef, time,stim,sep = '_')
            Metadata_cond = Metadata %>% filter(Coarse_ForDose %in% c(Cond, ControlCond))
            Count_cond = Count[, match(Metadata_cond$Sample_name, colnames(Count))]
            Metadata_cond$dose = as.numeric(Metadata_cond$Treatment_conc_uM)
            #Metadata_cond$dose = rafactor(Metadata_cond$Treatment_conc_uM, levels = c('0','1','2.5', '6.25', '15.6' ))
            # Deseq fit
            dds <- DESeqDataSetFromMatrix(countData = Count_cond, colData = Metadata_cond, design = ~ dose)
            deseqObj = DESeq(dds,
                         parallel = TRUE,
                         fitType = "parametric",
                         BPPARAM=MulticoreParam(detectCores() - 2))
            NormCounts_cond = getVarianceStabilizedData(deseqObj)
            res_dose = results(deseqObj, name = 'dose' )
            Model_dose = as.data.frame(res_dose)
            Model_dose$Gene = rownames(Model_dose)
            Diff_Genes_dose[[Cond]] = Model_dose
            Model_dose_sig = Model_dose %>% filter(padj < 0.2)
           
            
            
            #print(nrow(Model_dose_sig))
            
            DEG_Sum_Dose = DEG_Sum_Dose %>% add_row(Mol = mol, Time = time, Stim = stim, n_diff= nrow(Model_dose_sig))
            
            # Plot dose respnding genes
            if(nrow(Model_dose_sig)>1){
                
                Model_dose_sig =  Model_dose_sig[order(Model_dose_sig$padj, decreasing = FALSE),]
                GeneList = rownames(Model_dose_sig)[1:min(25,nrow(Model_dose_sig))]
                bxp = Gene_Expr_plot_dose(NormMatrix = NormCounts_cond,Metadata_Cond = Metadata_cond, GeneList)
                cat('\n')  
                print(bxp)
                cat('\n')  
            }else{
                print("Number of genes responding to dose is less than 2")
                cat('\n')  
            }
            
            
            
        }
        
    }
    
    Output_dose = "DEG_Dose.RData"
    Path_Output = paste(Path_Dir,'DEG_FUNCTION_DOSE',Output_dose, sep = "/")
    save(Diff_Genes_dose,DEG_Sum_Dose,  file = Path_Output)
    
    Path_Output2 = paste(Path_Dir,'DEG_FUNCTION_DOSE',"Diff_Genes_dose.xlsx", sep = "/")
    write.xlsx(Diff_Genes_dose, file = Path_Output2)
    
    
    
    
   
```

# {-}


# DEG per time point, dose responding: Summary{.tabset}


```{r GeneSummarydosePlot, eval = TRUE,echo=FALSE,warning = FALSE,message=FALSE, results = "asis", fig.width=8, fig.height=6}

    
    library(knitr)
    library(ggplot2)
    library(ggpubr)
    library(rstatix)
    library(tidyverse)

    cat("\n")
    cat("Summary showing number of dose responding genes per time point, per stimulation")
    cat("\n")
    
    Path_Data_file = paste(Path_Dir,'DEG_FUNCTION_DOSE','DEG_Dose.RData', sep = "/")
    
    load(Path_Data_file)
    Mols = unique(DEG_Sum_Dose$Mol)
    
    for(mol in Mols){
        
        cat('\n')
        cat("##",mol)
        cat('\n')  
        
        DEG_Sum_Dose_mol = DEG_Sum_Dose %>% filter(Mol == mol)
        print(nrow(DEG_Sum_Dose_mol))
        
        P = ggplot(DEG_Sum_Dose_mol, aes (x = Time, y = n_diff, fill = Time)) +
                   geom_bar(stat="identity", position=position_dodge())+facet_wrap(~Stim, ncol =2)
        
        print(P)   
        cat('\n')  
   }
    
   
    
    
    
   
```

# {-}




