---
title: "Transcriptomics analysis"
date: "2024-01-31"
output:
 html_document:
    toc: true
    toc_depth: 4
    keep_md: true
    toc_float: true
params:
  Dir_Output: "~/InVivoTranscriptomics/Results/Results_240129"  
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## PCA 

PCA of all samples in the experiment. Please check single treatment plus controls PCA plots within the folder DESEQ_NORM_QCNORM.

```{r PCA_POSTNORM_ALLSAMPLES,echo=FALSE, warning = FALSE,message=FALSE}
#Path_Dir = "/fsx/home/crivera/Novogene/usftp21.novogene.com_Exp5/Results_Ramos/Summary_Plots_Nfcore"
Path_Dir = params$Dir_Output
PCA_file1 = "PCA_allSamples1Vs2.png"
Path_PCA1 = paste(Path_Dir,'DESEQ_NORM_QCNORM','PCA_PLOTS',PCA_file1, sep = "/")
knitr::opts_chunk$set(fig_width=12, fig_height=15) 
knitr::include_graphics(Path_PCA1)
PCA_file2 = "PCA_allSamples1Vs3.png"
Path_PCA2 = paste(Path_Dir,'DESEQ_NORM_QCNORM','PCA_PLOTS',PCA_file2, sep = "/")
knitr::opts_chunk$set(fig_width=12, fig_height=15) 
knitr::include_graphics(Path_PCA2)

```


## DEG

Please find summary table containing differentially expressed genes for every selected comparison in the following link:

## ENRICHED PATHWAYS

Using DEG (abs(log2Fold) >1 and padj < 0.2) we find the over-represented pathways for each comparison. The filter REVERSE = TRUE determines whether only those DEG being regulated in the direction of healthy control are used for pathway enrichment. In other words, REVERSE = TRUE estimates the enrichment only with DEG from treatment vs DMSO that are also significant and change in the same  direction in the comparison healthy-control vs DMSO. We hope that this filter would allow us detect off-target effects at least up to a certain point. 

### SUMMARY TABLES

<br>
<a href= https://fvl55.sharepoint.com/:x:/s/Empress/EVwPcebhZ7pDp5Ae2YN3_iMBA6s7gUWJyGdz4LTkWlibTg?e=M6Vjgq> REVERSE_FALSE_KEGG </a>

<br>
<a href="file:///WORKDIR/InVivoTranscriptomics/Results/Results_240129/PWAYS_INTEGRATION/Chemo_target_enriched_PWAY_REVERSE_FALSE_Allmol.xlsx">link </a>


<br>
<a href= https://fvl55.sharepoint.com/:x:/s/Empress/EVwPcebhZ7pDp5Ae2YN3_iMBA6s7gUWJyGdz4LTkWlibTg?e=M6Vjgq> REVERSE_TRUE_KEGG </a>

<br>
<a href= https://fvl55.sharepoint.com/:x:/s/Empress/EVwPcebhZ7pDp5Ae2YN3_iMBA6s7gUWJyGdz4LTkWlibTg?e=M6Vjgq> REVERSE_TRUE_REACTOME </a>




```{r PATHWAYS,echo=FALSE,warning = FALSE,message=FALSE, results = "asis", fig.width=10, fig.height=10}
Path_Dir = params$Dir_Output
FolderName = "PWAY_ENRICHMENT"
FilterFold = list.files(paste(Path_Dir,FolderName, sep = "/"))

for(Fold in FilterFold){
    
    cat('\n')
    cat("###", Fold)
    cat('\n')
    Mols = list.files(paste(Path_Dir,FolderName,Fold, sep = "/"))

    for(mol in Mols){

        cat('\n')
        cat("####", mol)
        cat('\n')
        
         CompFiles = list.files(paste(Path_Dir,FolderName,Fold,mol, sep = "/"))
         CompFolder = CompFiles[grep(mol, CompFiles)]
         
         for(Comp in CompFolder){
             
             cat('\n')
             cat("####", Comp)
             cat('\n')
             
         }
         
         
    }

    
}
cat('\n')


```









